### 2016-05-21 Draft_BH_shells.tex
First upload
Summary of calculations so far.

\documentclass[aps,showpacs,twocolumn,floats,prd,superscriptaddress,nofootinbib]{revtex4-1} 
\usepackage{graphicx,amsmath,amssymb,amstext}
\usepackage{amssymb,amsbsy,amsfonts,amsthm,color}
\usepackage{epsfig}
%\usepackage{showkeys}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{sidecap}
\usepackage{floatrow}
\graphicspath{{Figures/}}

\begin{document}

\title{On the limitations of using quantum mechanics in a fixed background of a Schwarzschild black hole}

\author{Daniel Baker}
\email{dbaker@cita.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{University of Toronto, Department of Physics, 60 St George St, Toronto, ON M5S 3H8, Canada.}

\author{Darsh Kodwani}
\email{dkodwani@physics.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{University of Toronto, Department of Physics, 60 St George St, Toronto, ON M5S 3H8, Canada.}

\author{Ue-Li Pen}
\email{pen@cita.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{Canadian Institute for Advanced Research, CIFAR program in Gravitation and Cosmology.}
\affiliation{Dunlap Institute for Astronomy \& Astrophysics, University of Toronto, AB 120-50 St. George Street, Toronto, ON M5S 3H4, Canada.}
\affiliation{Perimeter Institute of Theoretical Physics, 31 Caroline Street North, Waterloo, ON N2L 2Y5, Canada.}

\author{I-Sheng Yang}

\email{isheng.yang@gmail.com}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{Perimeter Institute of Theoretical Physics, 31 Caroline Street North, Waterloo, ON N2L 2Y5, Canada.}

\begin{abstract}
Abstract
\end{abstract}

\maketitle

\onecolumngrid

\section{Introduction}

Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things. In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically. There are points where this assumption breaks down and we can see a clear example of this in terms of the interference pattern of a double slit experiment(DESCRIBE THE SITUATION INVOLVING THE DOUBLE SPLIT EXPERIMENT HERE). In this paper we analyse when this description of quantum mechanics in a classical background breaks down in the presence of a BH.

\section{Calculation}

\subsection{Proper time}

\subsubsection{Background spacetime}

First we consider the motion of Hawking photons coming from a Schwarzschild metric of the form

\begin{equation}
	ds^2 = - \left( 1 - \frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2.
\end{equation}

Consider two Hawking photons coming from a fixed distance, $r_{e}$, just above a Schwarzschild black hole separated by a coordinate time interval $\bar{\delta t}_A$ and a corresponding proper time $\bar{\delta \tau}_A$ as shown in figure \ref{fig:1}. The two photons propagate through to the observer at $r_0$ following geodesics. We could potentially solve for the geodesics of the photons to find out the coordinate time of arrival of each photon, however in the absence of additional gravitational fields the coordinate time interval between the photons will not change\footnote{This will prove to be extremely helpful when we look at the calculation in the presence of shells.}, i.e $\bar{\delta t}_A = \bar{\delta t}_0$, and that is the quantity we need in order to compute the proper time $\bar{\delta \tau}_0$ observed by the observer at $r_0$,

\begin{eqnarray}
	\bar{\delta \tau}_0 & = & \left( 1- \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_0	\nonumber	\\
	& = & \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_A \approx \bar{\delta t}_{A} 
\end{eqnarray}

where in the last step we have assumed $r_0$ is very large.

\subsubsection{Introducing perturbations: Double shells}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.6]{Propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
\label{fig:1}
\end{center}
\end{figure}

In this section we consider the top part of figure \ref{fig:1}. To distinguish the results from the previous section without shell we will not have an overbar in any of the quantities described in this scenario. The same initial conditions for the two Hawking photons are assumed. Using the argument described in the previous section we expect the coordinate time intervals between $r_A$ and $r_1$ to be equal, $\delta t_A = \delta t_1$. Analogously for the coordinate time interval between $r_2$ and $r_0$, $\delta t_2 = \delta t_0$. The new region is between $r_2$ and $r_1$ where the metric is different; it is defined by a mass $M - \Delta M$. The coordinate time interval at $r_1$ will also have a representation in the $II$ metric. Quantities evaluated in the $II$ metric will be denoted by a hat on top. By imposing the physical condition that there cannot be any discontinuities in spacetime we know that the proper times in both the metrics must be the same at $r_1$, $\delta \tau_1 = \delta \hat{\tau}_1$ and this gives a relation between the coordinate time intervals

\begin{equation}
	\delta t_1 = \left( \frac{1 - \frac{ 2(\Delta M -M)}{r_1})}{1 - \frac{ 2M}{r_1}}  \right)^\frac{1}{2} \delta \hat{t}_1.	\label{shell1}
\end{equation}

Applying the same condition to the proper times at $r_2$ gives the analogous relation between the coordinate time intervals at $r_2$,

\begin{equation}
	\delta t_2 = \left( \frac{1 - \frac{ 2(\Delta M -M)}{r_2})}{1 - \frac{ 2M}{r_2}}  \right)^\frac{1}{2} \delta \hat{t}_2. 	\label{shell2}
\end{equation}

Since $\delta \hat{t}_1$ and $\delta \hat{t}_2$ are both evaluated in the same metric they must be equal and therefore we can combine Eq (\ref{shell1}) and Eq (\ref{shell2}) to give a relation between $\delta t_1$ and $\delta t_2$,

\begin{eqnarray}
	\delta t_{1} & = & \left( \frac{ \left( 1 - \frac{2 M - \Delta M}{r_{1}} \right) \left( \frac{1 - 2M}{r_{2}} \right)}{\left( 1 - \frac{2M}{r_{1}} \right)  \left( 1 - \frac{2(M - \Delta M)}{r_{2}} \right)} \right)^\frac{1}{2} \delta t_{2}	\nonumber	\\
	& = & \left( \frac{2M - r_2}{2M - r_1} \right)^\frac{1}{2} \left( \frac{ 2(\Delta M - M) + r_1}{2(\Delta M - M) + r_2} \right)^\frac{1}{2} \delta {t}_{2}.
\end{eqnarray}

We see that $\delta t_1 = \delta t_2$ in the limit that $r_1 = r_2$ as then the shells will cancel out their masses and we are left with just metric $I$. By continuing these trajectories forward to the observer at $r_0$ we know that $\delta t_0 = \delta t_2 \approx \delta \tau_0$.

%\begin{SCfigure}
% \centering
%\includegraphics[height= 7 cm]{Propertime.pdf}	\label{fig:1}
%  \caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively. The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
%\end{SCfigure}

%\twocolumngrid

Without shells we saw that the proper time interval $\bar{\delta \tau}_0 \approx \delta t_A$, thus the difference in the proper time intervals with the shells is

\begin{equation}
	\delta \tau_0 - \bar{\delta \tau_0} = \delta t_A \left( \left( \frac{2M - r_2}{2M - r_1} \right)^\frac{1}{2} \left( \frac{ 2(\Delta M - M) + r_1}{2(\Delta M - M) + r_2} \right)^\frac{1}{2} - 1 \right). 	\label{PTD}
\end{equation}
As a check we see that when $r_1 = r_2$, $\delta \tau_0 = \bar{\delta \tau}_0$ as expected.

We can explore this relation further by going to a region close to the horizon. If we choose $r_1 = 2M + \epsilon_1$ and $r_2 = 2M + \epsilon_2$ where $\epsilon_{1,2} <<1$, the expression in Eq (\ref{PTD}) reduces to

\begin{equation}
	\delta \tau_0 - \bar{\delta \tau_0} = \left( \left( \frac{\epsilon_2}{\epsilon_1} \left( \frac{2\Delta M + \epsilon_1}{2 \Delta M + \epsilon_2}\right) \right)^\frac{1}{2} - 1 \right) 
\end{equation}

\subsection{Frequency of Hawking photons}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.6]{frequency.pdf}
\caption{This diagram follows the same notation as figure \ref{fig:1} except we are looking at one photon represented by the orange line. The frequency at each relevant point is denoted on the diagram. The quantities in the metric $I$ on the left of the shells are denoted with overbars. Quantities in metric $II$ are denoted without any overbars or hats. Quantities in metric $I$ to the right are denoted with hats on top.}
\label{fig:2}
\end{center}
\end{figure}

\subsubsection{Background spacetime}
We can do an analogous calculation to see this effect. Instead of looking at the proper time interval between photons we can consider the shift in frequency of single Hawking photon in the same two scenarios as were described in the previous section. We can write the photon four vector at distance $r$ as

\begin{equation}
	\bar{k}^\mu (\bar{\omega}_\infty, \bar{r}) = \bar{\omega}_\infty \left( \left( 1 - \frac{2M}{\bar{r}_A} \right)^{-1}, \sqrt{ 1 - \frac{\bar{b}^2}{\bar{r}_A^2} \left( 1 - \frac{2M}{\bar{r}_A} \right)}, \frac{\bar{b}}{\bar{r}_A^2}, 0 \right),
\end{equation}
where $\bar{\omega}_\infty$ is the frequency observed by a stationary observer at infinity and $b$ is the impact parameter of the photon. The general four velocity, $\bar{u}^\mu(\bar{r})$ of a stationary object in this geometry is

\begin{equation}
	\bar{u}^\mu(\bar{r}) = \left( \left( 1 - \frac{2M}{\bar{r}} \right)^{-\frac{1}{2}}, 0, 0, 0 \right).
\end{equation}

In the case where there are no shells, $\bar{\omega}_\infty$ is exactly the frequency observed by the observer at $\bar{r}_0$ in the limit that $\bar{r}_0 \rightrrow \infty$. In general, the frequency observed at $\bar{r}_0$, $\bar{\omega}_0$, will be redshifted

\begin{eqnarray}
	\bar{\omega}_0 & = & \bar{k}^\mu(\bar{\omega}_\infty, \bar{r}_0) \bar{u}^\nu(\bar{r}_0) \bar{g}_{\mu \nu}(\bar{r}_0) 	\nonumber	\\
	& = & - \bar{\omega}_\infty \left( 1 - \frac{2M}{\bar{r}_0} \right)^{-\frac{1}{2} }
\end{eqnarray}

of course in the limit $\bar{r}_0 \rightarrow \infty$ we get $\bar{\omega}_0 = -\bar{\omega}_\infty$.

\subsubsection{Introducing perturbations: Double shells}

The frequency measured at $r_1$ in metric $I$, $\bar{\omega}_1$ is

\begin{equation}
	\bar{\omega}_1 = - \bar{\omega}_\infty \left (1 - \frac{2M}{\bar{r}_1} \right)^{-\frac{1}{2}}.
\end{equation}

In metric $II$ the observed frequency $\omega_1$ is

\begin{eqnarray}
	\omega_1 & = & g_{\mu \nu}(r_1) k^\mu(\omega_\infty, r_1) u^\nu(r_1)	\nonumber	\\
	& = & - \omega_\infty \left( 1 - \frac{2(M- \Delta M)}{r_1} \right)^{-\frac{1}{2}}.
\end{eqnarray}

Since $\omega_1$ is a physical quantity we expect it to be the same in both in metrics, $\omega_1 = \bar{\omega}_1$ and also we expect $r_1 = \bar{r}_1, r_2 = \bar{r}_2$ (since the radius of the shell corresponds to a physical sphere of radius of $r$). This gives a relation between $\omega_\infty$ and $\bar{\omega}_\infty$

\begin{equation}
	\bar{\omega}_\infty = \omega_\infty \left( 1 - \frac{2 \Delta M}{2(\Delta M  - M)+ r_1} \right)^\frac{1}{2}.	\label{13}
\end{equation}

At $r_2$ we can again equate the observed frequencies in both metrics. In this case we define the frequency observed at infinity in metric $I$ on the right side of $r_2$ as $\hat{\omega}_\infty$, i.e the photon vector in metric $I$ for $r > r_2$ is $\hat{k}$ (But we expect the four velocity of the shell to be $\bar{u}_2$). From $k^\mu(\omega_2, r_2) u^\nu(r_2) g_{\mu \nu}(r_2) = \hat{k}^\mu(\bar{r}_2) \bar{u}^\nu(\bar{r}_2) \bar{g}_{\mu \nu} (\bar{r}_2)$ we have

\begin{equation}
	\hat{\omega}_\infty = \omega_\infty \left( 1 - \frac{2 \Delta M}{2(M-\Delta M) + r_2} \right)^\frac{1}{2}.	\label{14}
\end{equation}

By combining Eq (\ref{13}) and (\ref{14}) we get

\begin{equation}
	\hat{\omega}_\infty = \bar{\omega}_\infty \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
\end{equation}

The observed frequency at $r_0$, $\hat{\omega}_0$, is

\begin{eqnarray}
	\hat{\omega}_0 & = & u^\mu(r_0) k^\nu(\hat{\omega}_\infty, r_0) g_{\mu \nu}(r_0) 	\nonumber	\\
	& = & - \bar{\omega}_\infty \left( 1 - \frac{2M}{r_0} \right)^{-\frac{1}{2}}  \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
\end{eqnarray}

In the limit that $r_0 \rightarrow \infty$,

\begin{equation}
	\hat{\omega}_0 = - \bar{\omega}_\infty \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
\end{equation}

Looking at dynamics close to the horizon,

\begin{eqnarray}
	r_1 & = & 2M + \epsilon_1	\nonumber	\\
	r_2 & = & 2M + \epsilon_2
\end{eqnarray}

we get

\begin{equation}
	\hat{\omega}_0 = - \bar{\omega}_\infty \left( \frac{\epsilon_2}{\epsilon_1} \left( \frac{2 \Delta M + \epsilon_1}{2 \Delta M + \epsilon_2} \right) \right)^\frac{1}{2}
\end{equation}

\bibliography{all_active}

\end{document}

### 2016-05-21 Draft_BH_shells.tex
Add files via upload

@@
 
-Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things.
+%Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things.
 In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically.

### 2016-06-27 First_draft_BHs.tex

\documentclass[aps,showpacs,onecolumn,floats,prd,superscriptaddress,nofootinbib]{revtex4} 
\usepackage{graphicx,amsmath,amssymb,amstext}
\usepackage{amssymb,amsbsy,amsfonts,amsthm,color}

\usepackage{epsfig}
%\usepackage{showkeys}
\usepackage{graphicx}
\usepackage{subfigure}

\graphicspath{{Figures/}}

\begin{document}

\title{On the limitations of using quantum mechanics in a fixed background of a Schwarzschild black hole}

\author{Daniel Baker}
\email{dbaker@cita.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{University of Toronto, Department of Physics, 60 St George St, Toronto, ON M5S 3H8, Canada.}

\author{Darsh Kodwani}
\email{dkodwani@physics.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{University of Toronto, Department of Physics, 60 St George St, Toronto, ON M5S 3H8, Canada.}

\author{Ue-Li Pen}
\email{pen@cita.utoronto.ca}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{Canadian Institute for Advanced Research, CIFAR program in Gravitation and Cosmology.}
\affiliation{Dunlap Institute for Astronomy \& Astrophysics, University of Toronto, AB 120-50 St. George Street, Toronto, ON M5S 3H4, Canada.}
\affiliation{Perimeter Institute of Theoretical Physics, 31 Caroline Street North, Waterloo, ON N2L 2Y5, Canada.}

\author{I-Sheng Yang}

\email{isheng.yang@gmail.com}
\affiliation{Canadian Institute of Theoretical Astrophysics, 60 St George St, Toronto, ON M5S 3H8, Canada.}
\affiliation{Perimeter Institute of Theoretical Physics, 31 Caroline Street North, Waterloo, ON N2L 2Y5, Canada.}

\begin{abstract}
Abstract
\end{abstract}

\maketitle

\section{Introduction}

%Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things. In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically. There are points where this assumption breaks down and we can see a clear example of this in terms of the interference pattern of a double slit experiment(DESCRIBE THE SITUATION INVOLVING THE DOUBLE SPLIT EXPERIMENT HERE). In this paper we analyse when this description of quantum mechanics in a classical background breaks down in the presence of a BH.

\section{Calculation}

\subsection{Change in proper time due to shells}

\subsubsection{Background metric - no shells}

A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric

\begin{equation}
	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
\end{equation}

where we are working with units in which $G = c = 1$. We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}. Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole. An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$. We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}). By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation

\begin{equation}
	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
\end{equation}

where the superscript represents particle $1$ so $\bar{t_e}^{(1)}$ represents the time at which particle $1$ is emitted, $\bar{t_0}^{(1)}$ is when particle 1 is observed. Analogously for a particle $2$ that is emitted at $\bar{t_e}^{(2)}$ we have

\begin{equation}
	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
\end{equation}

Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that

\begin{equation}
	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
\end{equation}

Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig:1}.

\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.6]{propertime.pdf}
\caption{The two parts of this diagrams describe two different scenarios. The trajectories of the photon are the lines in orange. The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines. The bottom part is a general case of two particles coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$. The top part shows two particles coming from the same distance $r_e$ from a black hole of mass $M$. Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite ADM mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively, where $|\Delta M|<<M$. The region $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
\label{fig:1}
\end{center}
\end{figure}

We can convert $\delta\bar{t_0}$ to proper time

\begin{equation}
	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
\end{equation}

and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.

\subsubsection{Perturbed spacetime - double shell}

Now we introduce two shells of matter with equal and opposite ADM mass, $-\Delta M$ and $\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig:1}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M-\Delta M$ as shown in the top part of figure \ref{fig:1}.
\\
\\
As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by

\begin{equation}
	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M - \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
\end{equation}

We can propagate the particles through region $II$ from $r_1$ to $r_2$ and we know $\delta \hat{t}_1 = \delta \hat{t}_2$. From the fact that the proper time corresponding to the coordinate time intervals will be the same, we can relate $\delta \hat{t}_2$ back to $\delta t_2$ in region $I$,

\begin{equation}
	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M- \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
\end{equation}

Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$ by simply inverting Eq (\ref{7}) and multiplying by $ \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$,

\begin{eqnarray}
	\delta \tau_0 & = & \delta t_0 \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}, 	\nonumber	\\
	& =& \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
\end{eqnarray}

Since we assume the observer is far away we can neglect the term $\frac{2M}{r_0}$. The difference between the proper time interval in the presence of shells to the value without shells is

\begin{equation}
	\delta \tau_0 - \delta \bar{\tau_0} = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M -\Delta M)}{r_2 - 2(M- \Delta M)} \right)^\frac{1}{2} - 1\right),
\end{equation}

since $\delta t_e = \delta \bar{\tau_0}$ when the observer is far away, we can define a dimensionless quantity,

\begin{equation}
	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M-\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
\end{equation}

This expression is exact in the limit that the observer is far away. In the near horizon limit we expand the distances of the shells as,

\begin{eqnarray}
	r_1 & = & 2M + \epsilon 	\nonumber	\\
	 r_2 & = & 2M + \epsilon + \delta \epsilon 	\label{11'}
\end{eqnarray}

where $\epsilon<<2M, \ \delta \epsilon << \epsilon$. To leading order in small quantities Eq (\ref{10}) becomes,

\begin{equation}
	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = - \frac{\Delta M \delta \epsilon}{\epsilon^2}.	\label{11}
\end{equation}

\subsection{Defining local quantities}

\subsubsection{Energy of shell}

The quantities given on the right hand side of Eq (\ref{11}) are all coordinate dependent. To look at physical effects we must convert them to physical quantities. There is a natural choice of what to replace $\Delta M$ with and that is the $00$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC

\begin{equation}
	S^a_b =  [K^a_b] - [K]h^a_b
\end{equation}

where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics. We can define the induced metrics for constant $r$ values; for region $I$ it is

\begin{equation}
	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
\end{equation}

Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$

\begin{equation}
	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
\end{equation}

We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same. Therefore it is easy to find a relation between the two time coordinates

\begin{equation}
	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
\end{equation}

Using this, we calculate the extrinsic curvature components

\begin{eqnarray}
	K^t_t^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
	K^\theta_\theta^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} = K^\phi_\phi^{(M)}	\label{16}
\end{eqnarray}

where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$. Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}). With these ingredients we compute the $00$ component of the surface stress energy tensor

\begin{equation}
	S^0_0 = - \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
\end{equation}

This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$

\begin{equation}
	\mathcal{E} = - r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
\end{equation}

Substituting in for $r_1 = 2M + \epsilon$, where $\Delta M<<\epsilon<<2M$ and expanding to leading order in small quantities,

\begin{equation}
	\mathcal{E} = \left( \frac{2M}{\epsilon} \right)^\frac{1}{2} \Delta M.
\end{equation}

\subsubsection{Proper time between shells}

We calculate the proper time between the two shells, $\tau_{12}$, as seen by an observer at the first shell\footnote{One could also calculate the proper length between the shells.}. This is done with a view to replace $\delta \epsilon$ by $\tau_{12}.

\begin{eqnarray}
	\tau_{12} & = & \int^{t_2}_{t_1} \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} dt	\nonumber	\\
	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (t_2 - t_1)	\nonumber	\\
	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (r_2 - r_1 + 2M' \ln \left( \frac{r_2 - 2M'}{r_1 - 2M'} \right) \right).	
\end{eqnarray}

We substitute in for $r_1$ and $r_2$ from Eq (\ref{11'}) to give

\begin{equation}
	\tau_{12} = \delta \epsilon \left( \frac{\epsilon}{2M} \right)^\frac{1}{2} \left( 1 + \frac{2M}{\epsilon} \right).
\end{equation}

\subsubsection{Proper distance to the shell}

The proper length $l$ between the horizon and shell is calculated to replace $\epsilon$ in Eq (\ref{11}).

\begin{eqnarray}
	l & = & \int^{2M + \epsilon}_{2M} \frac{dr}{\left( 1 - \frac{2M}{r} \right)^\frac{1}{2}}	\nonumber	\\
	& = & (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right)
\end{eqnarray}

to leading order this reduces to

\begin{equation}
	l = 2 (2 \epsilon M)^\frac{1}{2}.
\end{equation}

Using these local quantities to replace the coordinate quantities in Eq (\ref{11}) gives

\begin{equation}
	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = - \frac{\mathcal{E} \tau_{12}}{l^4} \frac{64 M^2}{1 + \frac{16 M^2}{l^2}}
\end{equation}

In the limit that $M \rightarrow \infty$ we get a very simple result

\begin{equation}
	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} |_{M \rightarrow \infty} = - \frac{4 \mathcal{E} \tau_{12}}{l^2}.
\end{equation}

\section{Discussion}

\bibliography{all_active}

\end{document}

### 2016-07-15 Draft_BH_shells.tex

--- 2016-05-21 Draft_BH_shells.tex
@@
 
-\title{On the limitations of using quantum mechanics in a fixed background of a Schwarzschild black hole}
+\title{A self-consistency check for the unitary propagation of Hawking quanta}
 
@@
 \begin{abstract}
-Abstract
+The black hole information paradox presumes that local quantum field theory is valid to provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
+Instead of invoking unknown quantum-gravity effects to modify such assumption, we propose a self-consistency check.
+We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
+Feynmann showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern goes to infinitely far away.
+Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
+We present strong evidence that the result is negative, and we discuss its implications.
 \end{abstract}
@@
 
-\section{Introduction}
+\section{Introduction and Summary}
 
-Whenever we describe a quantum system, we assume that the system we are describing and the environment around it are separate things.
-In particular we assume the environment can be described classically and the system we are describing behaves quantum mechanically.
-There are points where this assumption breaks down and we can see a clear example of this in terms of the interference pattern of a double slit experiment(DESCRIBE THE SITUATION INVOLVING THE DOUBLE SPLIT EXPERIMENT HERE).
-In this paper we analyse when this description of quantum mechanics in a classical background breaks down in the presence of a BH.
+Quantum mechanical evolution of a full system is by-definition unitary. 
+Unfortunately, we are not always able to describe everything by quantum mechanics all together. 
+Practical descriptions are always about subsystems. 
+Namely, we assume that the full system can be separated into a ``classical background'' and a ``quantum subsystem''. 
+Since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
+\footnote{Even a time-dependent Hamiltonian leads to an apparently unitary evolution under this assumption.
+That is obviously not a physical fact since a unitary subsystem should be determined by its own initial state, not co-determined by initial state plus an arbitrary time-dependence.}
+However, such unitarity should not be taken as a physical fact unless one specifically checks the nature of interactions with the background.
+
+The most direct way to justify the classical-background assumption is to also describe the background in quantum mechanics, and verify that the quantum interaction between the background and the quantum subsystem indeed does not entangle them.
+This is clearly difficult in practice. 
+The very reason why we would like to apply the classical-background approximation is to avoid describing the far-too-complicated background by quantum mechanics. 
+A consistency check which requires us to do so defeats the purpose. 
+Furthermore, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
+Quantum field theory in curved spacetime is a perfect example. 
+In this case, the classical background is the geometry.
+One in-principle needs to know quantum gravity in order to model the quantum interaction with the background.
+
+Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent the above obstacle. 
+This trick, to a certain extend, enables us to perform a self-consistency check of the classical-background assumption {\bf without} knowing the quantum nature of the background.
+In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis on the double-slit experiment. 
+In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and the operational definition of subsystem unitarity is whether an interference pattern can be observed on the final projection screen.
+He showed that we can ignore the quantum details of the double-slits and summarize that as an uncertainty in its position, which is a classical quantity. 
+When such uncertainty is fixed, the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
+It is in this sense that a unitary evolution of the subsystem is an arbitrarily good approximation.
+
+The fundamental principle from Feynman's trick is that ``classical wave coherence'' should be taken as the prerequisit of ``quantum unitarity''. 
+In Sec.\ref{sec-QFT}, we argue that it has a natural generalization to local QFT in curved spacetime, thus we can apply it to re-examine the propagation of Hawking quanta. 
+This propagation is of particular importance because it plays a central role in the lasting debate of black hole information paradox. 
+The main dilemma is that one Hawking quantum needs to play two different roles. 
+Near the horizon, it has to be part of the local vacuum state; near spatial infinity, it has to recover a unitary evaporation process. 
+For an old black hole, the same state of a Hawking quantum cannot fulfill both requirements, thus the paradox. 
+If the propagation process from near the horizon to infinity is not unitary, then a near horizon mode and the asymptotic Hawking quantum does not have the same state, and the paradox loses its fundation.
+Thus before jumping into any conclusion regarding the paradox, we should try to confirm whether QFT in a curved spacetime is indeed justified to provide a unitary propagation of Hawking quanta.
+
+In Sec.\ref{sec-BlackHole}, we will provide our detail analysis and analogy. 
+Roughly speaking, the classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
+We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
+A classical wave plays the role of the interference pattern; if even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
+The common belief is that in the limit of a large black hole, gravitational effect outside the horizon is arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
+By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drops to zero when we take the large black hole limit.
+Interestingly, what we found seems to be the opposite. 
+We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
+By analogy to Feynman's analysis, this as a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
+
+{\bf XXX tbc by I-Sheng}
+
+\section{Feyman's analysis on double-slit experiments}
+\label{sec-DoubleSlit}
+
+Double-slit interference is the signature experiment to demonstrate the nature of quantum mechanics. Figure 1 shows a simple example of such experiment.
+When a group of particles of the same momentum pass through slit 1 only, they reach the final screen as some probability distribution $P_1(y)$. 
+When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
+When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$! 
+Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
+$P_i = \langle \phi_i | \phi_i \rangle$ and $P_{12} = (\langle \phi_1|+\langle \phi_2| ) (|\phi_1\rangle + | \phi_2 \rangle)=P_1 + P_2 + 2{\rm Re}\langle\phi_1|\phi_2\rangle$.
+
+\ \\ \ \\
+{\bf XXX insert the double-slit figure here: Darsh.}
+\ \\ \ \\
+
+This standard explanation works because we assume the particle is the only quantum-mechanical system here, and it can be describe by a pure state, $|\phi\rangle_{\rm particle} = |\phi_1\rangle + |\phi_2\rangle$.
+But if quantum mechanics is correct, this particle is not the only thing to be described by a wavefunction. 
+For example, we can also describe the double-slit by its wavefunction $|\psi\rangle_{\rm ds}$. The total wavefunction of the combined system can be in a pure state,
+\begin{equation}
+|\Psi\rangle_{\rm combined} = |\psi_1\rangle_{\rm ds}|\phi_1\rangle_{\rm particle} 
++ |\psi_2\rangle_{\rm ds}|\phi_2\rangle_{\rm particle} ~,
+\end{equation}
+but either subsystem does not have to be pure.
+
+When the two double-slit states are almost indistinguishable,
+\begin{equation}
+\langle\psi_1|\psi_2\rangle\langle\psi_2|\psi_1\rangle \approx 1~,
+\label{eq-pure}
+\end{equation}
+then the combined system factorizes,
+\begin{equation}
+|\Psi\rangle_{\rm combined} \approx |\psi_1\rangle_{\rm ds}
+\left(|\phi_1\rangle_{\rm particle} + |\phi_2\rangle_{\rm particle}\right) ~.
+\end{equation}
+The particle subsystem indeed stays as a pure state and there will be an interference pattern.
+
+On the other hand, if the two double-slit states are distinguishable,
+\begin{equation}
+\langle\psi_1|\psi_2\rangle\langle\psi_2|\psi_1\rangle \ll 1~,
+\label{eq-mixed}
+\end{equation}
+that means the interaction entangled the two systems. The particle subsystem becomes a mixed state,
+\begin{equation}
+\rho_{\rm particle} = {\rm Tr}_{\rm ds}|\Psi\rangle\langle\Psi| \approx
+|\phi_1\rangle\langle\phi_1| + |\phi_2\rangle\langle\phi_2|~,
+\end{equation}
+and there will be no interference pattern.
+
+Whether the double-slit states are given by Eq.~(\ref{eq-pure}) or (\ref{eq-mixed}) seems to require the knowledge about the actual quantum-mechanical interacton between the particles and the double-slit, which is unavailable in practice.
+Feynman pushed the above analysis further to overcome such problem.
+He pointed out that even if we try to keep the interaction minimal, there will be one inevitable interaction that makes $|\psi_1\rangle$ and $|\psi_2\rangle$ different.
+That is because when a particle reaches some place on the screen, its $y$-momentum must be different depending on which slit it passed through.
+\begin{equation}
+\Delta p_y^{\rm particle} \equiv 
+|\langle\phi_1|p_y|\phi_1\rangle - \langle\phi_2|p_y|\phi_2\rangle| 
+\approx p_x \frac{s}{L}~,
+\end{equation}
+where $p_x$ is the $x$ momentum of the particles, $s$ is the separation between the two slits, and $L$ is the distance to the screen. 
+This means two different values of recoil momentum on the double-slit,
+\begin{equation}
+\Delta p_y^{\rm ds} = \Delta p_y^{\rm particle} \approx p_x \frac{s}{L}~.
+\label{eq-dpds}
+\end{equation}
+The uncertainty principle sets a limit on how well we can measure this difference.
+Namely, we need a large uncertainty in the position to measure a small change in momentum.
+Setting $\hbar$ to 1, we can say that when the momentum difference is too small to be measured,
+\begin{equation}
+\Delta p_y^{\rm ds} < 1/\Delta y^{\rm ds}~,
+\label{eq-standard}
+\end{equation} 
+then Eq.~(\ref{eq-pure}) is true and the two states are indistinguishable. 
+Otherwise Eq.~(\ref{eq-mixed}) is true and the two states are distinguishable.
+
+The key point is that there is an alternative way to appreciate Eq.~(\ref{eq-standard}) {\it without} thinking about the quantum mechanics of the double-slit. 
+First of all, the interference pattern has a fringe width of  
+\begin{equation}
+w = L\frac{\lambda}{s}~,
+\end{equation}
+where $\lambda = p_x^{-1}$ is the de Broglie wavelength of the particle.
+This is the separation of bright/dark lines in the $y$ direction with a fixed reference point at the $y$ position of the double-slit.
+Thus the uncertainty in the $y$ position must be smaller than this value, so the interference pattern is not totally blurred.
+\begin{equation}
+\Delta y^{\rm ds} < w = \frac{L}{p_xs}~.
+\label{eq-stdcls}
+\end{equation}
+This is exactly the same condition as in Eq.~(\ref{eq-standard}).
+
+We should emphasize the key value of this result.
+We can treat both the position uncertainty $\Delta y^{\rm ds}$ and the interference fringe width $w$ as classical quantities.
+Eq.~(\ref{eq-stdcls}) is then a purely classical calculation to compare these two quantities, which tells us whether a classical wave pattern (the intereference pattern) loses coherence.
+If we only take its face value, it seems to be only a practical obstacle of measuring the interference pattern.
+One might argue that the underlying subsystem unitarity is still valid, just difficult to measure.
+
+What Feynman showed by this example is that Eq.~(\ref{eq-stdcls}) tells us exactly the same thing as Eq.~(\ref{eq-standard}).
+The later {\bf is} directly about quantum mechanics and shows how the subsystem unitarity can fail.
+Thus an apparently classical calculation can tell us something about the hidden quantum-mechanical nature of the interaction between the double-slit and the particle passing through it.
+In this example, it tells us whether the particles get entangled with the double-slit and loses its subsystem unitarity.
+
+One might object that the above analysis is only applicable if we are {\it given} a particular value of $\Delta y^{\rm ds}$, while in fact such quantity has to originate from the unknown quantum mechanics of the double-slit.
+This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}).
+Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit.
+Namely, its value should be fixed if we move the screen further away.
+Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition.
+Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible, thus the subsystem unitarity is valid.
+
+\section{Analogy in Quantum Field Theory}
+\label{sec-QFT}
+
+The double-slit interference is an example that both the classical coherence and quantum unitarity can be calculated explicitly and show that they follow the same condition.
+Here, we advocate that such relation is actually a general rule.
+{\it Classical coherence, instead of thinking it as a practically of measurements, should be treated as a prerequisit to quantum unitarity.} 
+Thus when classical coherence fails, not only have we no practical measurements to confirm the purely of the subsystem wavefunction, such wavefunction {\it actually did not evolve unitarily.}
+Whatever effect responsible for a classsical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.
+
+For quantum field theory in a curved spacetime, we always assume that the quantum fields is a subsystem that never entangles with the geometry, thus remains unitary.
+Since we do not know quantum gravity/geometry, we cannot directly check this assumption by an actual calculation of entanglement.
+However, we can always check classical coherence, and by this rule we advocate, the answer directly prove/disprove subsystem unitarity.
+
+If we go back to the basic of quantum field theory, this new rule we advocate makes a lot of sense.
+As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state.
+Any method to measure such quantum state assumes the knowledge of the classical mode function. 
+If the geometric uncertainty leads to an order one change in the classical mode function, then there is no practical way to reliably measure its quantum state. 
+We advocate that this is not only a practicality about measuring the quantum state, but it directly tells us that the quantum state loses its unitarity. 
+Just like in Feynman's example where the uncertainty of the double-slit guarantees its entanglement with the particles, whatever effect that leads to the geometric uncertainty here must entangle with the quantum state of this mode.
+Without a theory of quantum geometry, we cannot describe how that happens. 
+But through a classical calculation, we can determine whether it has happened or not.
+
+\ \\ \ \\
+{\bf XXX insert the QFT figure here: Darsh or I-Sheng}
+
+\section{Hawking quanta propagation}
+\label{sec-BlackHole}
+
+The usual treatment of how a near-horizon mode becomes an asymptotic Hawking quantum is also following a fixed-background assumption.
+The background is the Schwarzschild geometry.
+\begin{equation}
+ds^2 = -\left(1-\frac{2M}{r}\right)dt^2 + \frac{dr^2}{1-\frac{2M}{r}} + r^2d\Omega_2^2~.
+\end{equation}
+When one applies local quantum field theory to describe a field on this fixed background, the result is by-definition unitary, but that is not necessary a physical fact. 
+Given how little we understand quantum gravity, a classical self-consistency check as we described in the previous section is a reasonable thing to do.
+
+\subsection{Setup and summary}
+
+\begin{itemize}
+\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
+Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
+We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
+If such change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
+\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
+A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
+There are two major challenges here.
+\begin{enumerate}
+\item There are many more variables than the double-slit experiment. 
+We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
+It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
+\item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
+By relating it to the presence of extra matter, we can express it to a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
+\end{enumerate}
+Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
+However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
+Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
+\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
+In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
+We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
+Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
+\end{itemize}
+
+More concretely, our setup is like in Fig.\ref{fig-setup}. 
+We start by choosing two points at some $r_0\gg M$ with a $\delta t_0\sim M$ coordinate time separation between them.
+This represents one wavelength of the mode function of an asymptotic Hawking quantum.
+We then back-track two null geodesics from these two points back to two points near the horizon, at $r_A$ with $(r_A-2M)\ll 2M$.
+Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
+We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
+Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
+Only the process of propagation is affected.
+With the same two starting points near the horizon. we calculate the separation $\bar{\delta t_0}$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta t_0$.
+
+\begin{figure}[tb]
+\begin{center}
+\includegraphics[scale = 0.6]{Propertime.pdf}
+\caption{The two parts of this diagrams describe two different scenarios.
+The trajectories of the photon are the lines in orange.
+The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines.
+The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
+The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$.
+Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively.
+The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
+\label{fig-setup}
+\end{center}
+\end{figure}
+
+After some formal calculations in the {\bf Appendix}, we arrive at this simple expression:
+\begin{equation}
+\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = 
+\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M-\Delta M)}{r_2-2(M-\Delta M)}}-1\right)~,
+\label{eq-result}
+\end{equation}
+where $r_1$ is the location of the inner shell, $r_2$ is the location of the outer shell, and $\pm\Delta M$ are their individual ADM masses.
+
+\subsection{Physical interpretation}
+
+As the first step, we set $M=0$ in Eq.~(\ref{eq-result}) to study its meaning in Minkowski space.
+Assuming that $|r_1-r_2| \equiv \Delta r \ll r_1$ and $\Delta M \ll r_1$, the leading order result becomes
+\begin{equation}
+\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{\Delta M}{r_1^2} \Delta r 
+\equiv \sigma \Delta r~.
+\label{eq-Mink}
+\end{equation}
+This seems to be a reasonable answer. 
+First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
+It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
+Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
+For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
+We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.
+
+The na\"ive interpretation of Eq.~(\ref{eq-Mink}) is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
+By our definition, that poses some threat to QFT in Minkowski space.
+We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect of Eq.~(\ref{eq-Mink}).
+One can imagine a simple subtraction by a counter term.
+Or alternatively, since the actual value of $(\sigma\Delta r)$ is unknown, we assume that it is small enough to not cause any concern.
+
+Next we study Eq.~(\ref{eq-result}) with an actual black hole.
+When the double-shell is very far away from the black hole, $r_1\gg M$, it agrees with Eq.~(\ref{eq-Mink}) as expected.
+The interesting thing here is that when this pair of geodesics originate near the horizon, the double-shell could also be somewhere near the horizon.
+In that limit, Eq.~(\ref{eq-result}) can be approximated by
+\begin{equation}
+\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx
+\sigma \Delta l \left(\frac{2M}{l_1}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
+\label{eq-NearHorizon}
+\end{equation}
+where $l$ is the proper distance between $r_1$ and the horizon and $\Delta l$ is the proper distance between the two shells.
+We can see that in addition to the same gauge-invariant quantity in Minkowski space\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, there is an extra factor of $(2M/l_1)^2$ which diverges as the shell approaches the horizon.
+
+The small $l_1$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT.
+After all, we do not expect QFT to hold for arbitrarily small distance anyway.
+The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l_1$ at some scale that much longer than any scale that we expect UV problems.
+By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large.
+However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and diverges in the large black hole limit.
+
+\section{Discussion}
+
+{\bf XXX Maybe do this in the introduction: I-Sheng.}
+
+\appendix
 
 \section{Calculation}
+
+{\bf XXX Modify the content accordingly to fit their status in the appendix: Darsh/Daniel.}
 
@@
 
-In the case where there are no shells, $\bar{\omega}_\infty$ is exactly the frequency observed by the observer at $\bar{r}_0$ in the limit that $\bar{r}_0 \rightrrow \infty$.
+In the case where there are no shells, $\bar{\omega}_\infty$ is exactly the frequency observed by the observer at $\bar{r}_0$ in the limit that $\bar{r}_0 \rightarrow \infty$.
 In general, the frequency observed at $\bar{r}_0$, $\bar{\omega}_0$, will be redshifted

### 2016-07-21 Draft_BH_shells.tex

@@
 
-\title{A self-consistency check for the unitary propagation of Hawking quanta}
+\title{A self-consistency check for unitary propagation of Hawking quanta}
 
@@
 \begin{abstract}
-The black hole information paradox presumes that local quantum field theory is valid to provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
+The black hole information paradox presumes that local quantum field theory can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
 Instead of invoking unknown quantum-gravity effects to modify such assumption, we propose a self-consistency check.
 We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
-Feynmann showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern goes to infinitely far away.
+Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern goes to infinitely far away.
 Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
-We present strong evidence that the result is negative, and we discuss its implications.
+We present strong evidence that the result is negative, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
 \end{abstract}
@@
 
+The black hole information paradox \cite{Haw76a} was sharpened to show a self-inconsistency among the following three widely-believed statements \cite{AMPS}
+\footnote{Different physicists may believe in some of those more strongly than the others, but very few would have argued against any single statement without the explicitly conflict in the information paradox.}:
+\begin{itemize}
+\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer as a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
+\item {\bf General relativity:} The collapse-Schwarzschid geometry given by general relativity is a valid description to the spacetime everywhere except for near the singularity.
+Therefore, there is no drama while crossing the horizon.
+\item {\bf Local quantum field theory:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
+It manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
+\end{itemize}
+
+This conflict has inspired many different proposals to modify one of the above three statements. 
+For example, information loss or remnant \cite{Bek94} {\bf (XXX anyone knows a better reference for remnants?)} modifies the first statement; 
+firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies the second statement;
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
+\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch.
+Since ``whether there exists a causal patch to fit'' is a highly nonlocal condition, it is effectively a break-down of local QFT.} 
+modifies the last statement.
+Unfortunately, since the paradox only shows a conflict with the three statements combine, it is up to individual taste/bias to modify any one of them.
+
+In this paper, we will try to sharpen the problem even further. 
+We will try to argue that the last statement on its own is already self-conflicting. 
+In other words, {\bf the application of local QFT to a unitary propagation of Hawking quantum is not self-consistent. } 
+This should provide a much stronger motivation to modify the second statement than the other two. 
+Although there are still many different proposals capable of doing that, we hope such discovery can focus our efforts and make the progress even further.
+
+Before diving into details, we should explain why we focus on the last statement.
+That is becasue local QFT simply assumes a subsystem unitarity.
 Quantum mechanical evolution of a full system is by-definition unitary. 
-Unfortunately, we are not always able to describe everything by quantum mechanics all together. 
-Practical descriptions are always about subsystems. 
+However in practice, we are not able to describe everything by quantum mechanics all together, so we describe only subsystems. 
 Namely, we assume that the full system can be separated into a ``classical background'' and a ``quantum subsystem''. 
-Since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
+After such artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
 \footnote{Even a time-dependent Hamiltonian leads to an apparently unitary evolution under this assumption.
@@
 A consistency check which requires us to do so defeats the purpose. 
-Furthermore, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
-Quantum field theory in curved spacetime is a perfect example. 
-In this case, the classical background is the geometry.
-One in-principle needs to know quantum gravity in order to model the quantum interaction with the background.
+In particular, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
+Our problem at hand, QFT in curved spacetime, is exactly such annoying situation. 
+Since the classical background is the geometry, one in-principle needs to know quantum gravity in order to model the quantum interaction with the background.
 
 Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent the above obstacle. 
-This trick, to a certain extend, enables us to perform a self-consistency check of the classical-background assumption {\bf without} knowing the quantum nature of the background.
+This trick, to a certain extend, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
 In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis on the double-slit experiment. 
-In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and the operational definition of subsystem unitarity is whether an interference pattern can be observed on the final projection screen.
-He showed that we can ignore the quantum details of the double-slits and summarize that as an uncertainty in its position, which is a classical quantity. 
-When such uncertainty is fixed, the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
+In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and subsystem unitarity is checked by whether an interference pattern can be observed on the final projection screen.
+He showed that we can ignore the quantum details of the double-slit and summarize that as an uncertainty in its position, which is a classical quantity. 
+When such uncertainty is fixed, a classical calculation can show that the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
 It is in this sense that a unitary evolution of the subsystem is an arbitrarily good approximation.
 
-The fundamental principle from Feynman's trick is that ``classical wave coherence'' should be taken as the prerequisit of ``quantum unitarity''. 
+The fundamental principle behind Feynman's trick is that ``classical wave coherence'' should be taken as the prerequisite of ``quantum unitarity''. 
 In Sec.\ref{sec-QFT}, we argue that it has a natural generalization to local QFT in curved spacetime, thus we can apply it to re-examine the propagation of Hawking quanta.
-This propagation is of particular importance because it plays a central role in the lasting debate of black hole information paradox. 
-The main dilemma is that one Hawking quantum needs to play two different roles. 
-Near the horizon, it has to be part of the local vacuum state; near spatial infinity, it has to recover a unitary evaporation process. 
-For an old black hole, the same state of a Hawking quantum cannot fulfill both requirements, thus the paradox. 
-If the propagation process from near the horizon to infinity is not unitary, then a near horizon mode and the asymptotic Hawking quantum does not have the same state, and the paradox loses its fundation.
-Thus before jumping into any conclusion regarding the paradox, we should try to confirm whether QFT in a curved spacetime is indeed justified to provide a unitary propagation of Hawking quanta.
 
 In Sec.\ref{sec-BlackHole}, we will provide our detail analysis and analogy. 
-Roughly speaking, the classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
+The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
 We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
-A classical wave plays the role of the interference pattern; if even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
-The common belief is that in the limit of a large black hole, gravitational effect outside the horizon is arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
-By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drops to zero when we take the large black hole limit.
+A classical wave plays the role of the interference pattern. 
+When even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
+The common expectation is that in the limit of a large black hole, gravitational effect outside the horizon is arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
+By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drop to zero when we take the large black hole limit.
 Interestingly, what we found seems to be the opposite. 
 We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
-By analogy to Feynman's analysis, this as a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
+By analogy to Feynman's analysis, this is a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
 
-{\bf XXX tbc by I-Sheng}
+In Sec.\ref{sec-dis}, we discuss various implications of our finding. 
+First of all, our self-consistency check should be generally applicable to any geometry, and it does not invalidate local QFT entirely. 
+Likewise, even when unitarity is lost in local QFT, the values of many observables do not have to change. 
+Most existing applications of QFT in curved spacetime actually only care about the expectation value of particle numbers, which can be unaffected by the loss of subsystem unitarity. 
+Secondly, our finding resolve the information paradox by selecting one culprit among the three statements, but it does not yet resolve the information transfer puzzle. 
+We argue that our finding naturally implies an information exchange between a QFT quantum and the local geometry \cite{OsuPag16}.
+The the reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}.
 
@@
 where $l$ is the proper distance between $r_1$ and the horizon and $\Delta l$ is the proper distance between the two shells. 
-We can see that in addition to the same gauge-invariant quantity in Minkowski space\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, there is an extra factor of $(2M/l_1)^2$ which diverges as the shell approaches the horizon.
+We can see that in addition to the same gauge-invariant quantity in Minkowski space
+\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, 
+there is an extra factor of $(2M/l_1)^2$ which diverges as the shell approaches the horizon.
 
@@
 However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and diverges in the large black hole limit.
+Since the large black hole limit is supposed to be the best case scenario for information paradox, such a diverging uncertainty to decohere classical waves causes a strong doubt on the subsystem unitarity assumption in QFT.
 
@@
 
-{\bf XXX Maybe do this in the introduction: I-Sheng.}
+\subsection{The self-consistency check of local QFT}
+
+In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
+We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such check.
+As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
+We have chosen a particular form of uncertainty in our explicit calculation.
+Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.
+It is also interesting to apply the same check to other geometries, especially other types of horizons.
+
+We should emphasize that our check does not invalidate QFT all together.
+We simply suggest that the QFT degrees of freedom lose their subsystem unitarity.
+In the double-slit experiment, with or without the interference pattern, the total number of particles that passes through the double-slit is not affected, and the expectation value of the particle location remains in the center.
+The point is that we can always find a pair of pure and mixed density matrices which give identical expectation values to many observables.
+It is not unexpected that the only affected observable is the one explicitly checking unitarity.
+Thus we can still rely on QFT to calculate the values of other observables.
+
+Many existing results of QFT in curved/dynamical geometries are about particle numbers, such as the particle-production calculation following a Bogoliugov transformation. 
+As an example, one can easily see that
+\begin{equation}
+\rho_{\rm pure} = \left(\sum_n a_n|n\rangle\right)
+\left(\sum_n \langle n| a_n^*\right)
+\end{equation}
+and
+\begin{equation}
+\rho_{\rm mixed} = \sum_n |a_n|^2 |n\rangle\langle n|
+\end{equation}
+give the same particle number. 
+Thus there is no general crisis if we admit that local QFT sometimes loses subsystem unitarity.
+
+As far as we know, an observable that explicitly checks the subsystem unitarity of local QFT is the cosmological Bell inequality \cite{Mal15}. 
+One can apply our self-consistency check to such model and update the prediction of whether a violation of Bell inequality is actually expected.
+
+\subsection{The information-transfer puzzle}
+
+Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problem. 
+Usually, one pictures a nonunitarity process as losing information. 
+In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
+A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
+After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.
+
+Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry. 
+An abstract realization of this information-recovery process is recently demonstrated in \cite{OsuPag16}. 
+In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
+If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
+In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
+Thus the major objection to such picture is that the superpositons of classical geometries do not form a large enough Hilbert space to hold the required information.
+Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
+A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should persue this line of thoughts even further.
+
+Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
+Based on this picture, one may try to quantize the soft hairs and build a toy model that invovles quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
+That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.
 

### 2016-07-27 Draft_BH_shells.tex
typo label fixed

@@
 \begin{abstract}
-The black hole information paradox presumes that local quantum field theory can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
-Instead of invoking unknown quantum-gravity effects to modify such assumption, we propose a self-consistency check.
+The black hole information paradox presumes that local quantum field theory can provide unitary propagations for near-horizon modes to asymptotic Hawking quanta. 
+Instead of invoking unknown quantum-gravity effects to modify this assumption, we propose a self-consistency check.
 We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
-Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern goes to infinitely far away.
-Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
+Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern on goes infinitely far away.
+Analogously, here we ask whether unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
 We present strong evidence that the result is negative, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
@@
 modifies the last statement.
-Unfortunately, since the paradox only shows a conflict with the three statements combine, it is up to individual taste/bias to modify any one of them.
+Unfortunately, since the paradox only shows a conflict with the three statements combined, it is up to individual taste/bias to modify any one of them.
 
@@
 In particular, there are situations in which we in-principle do not know how to describe the classical background in quantum mechanics. 
-Our problem at hand, QFT in curved spacetime, is exactly such annoying situation. 
+Our problem at hand, QFT in curved spacetime, is exactly this annoying situation. 
 Since the classical background is the geometry, one in-principle needs to know quantum gravity in order to model the quantum interaction with the background.
 
-Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent the above obstacle. 
+Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent this obstacle. 
 This trick, to a certain extend, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
-In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis on the double-slit experiment. 
+In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis of the double-slit experiment. 
 In his case, the double-slit is the classical background, the particle passing through it is the quantum subsystem, and subsystem unitarity is checked by whether an interference pattern can be observed on the final projection screen.
@@
 
-In Sec.\ref{sec-BlackHole}, we will provide our detail analysis and analogy. 
-The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
-We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
+In Sec.\ref{sec-BlackHole}, we will provide our detailed analysis and analogy. 
+The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruin its subsystem unitarity. 
+We then assume that the unknown quantum nature of geometry can be parametrized by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
 A classical wave plays the role of the interference pattern. 
 When even a classical wave decoheres due to the uncertainty of geometry, there is no reason to believed that the quantized version of such wave has unitarity.
-The common expectation is that in the limit of a large black hole, gravitational effect outside the horizon is arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
+The common expectation is that in the limit of a large black hole, gravitational effects outside the horizon are arbitrarily weak, thus local QFT should be arbitrarily trustworthy.
 By analogy to Feynman's analysis, we should expect that with a fixed uncertainty in the geometry, any effect on the classical wave should drop to zero when we take the large black hole limit.
@@
 Most existing applications of QFT in curved spacetime actually only care about the expectation value of particle numbers, which can be unaffected by the loss of subsystem unitarity. 
-Secondly, our finding resolve the information paradox by selecting one culprit among the three statements, but it does not yet resolve the information transfer puzzle. 
+Secondly, our finding resolves the information paradox by selecting one culprit among the three statements, but it does not yet resolve the information transfer puzzle. 
 We argue that our finding naturally implies an information exchange between a QFT quantum and the local geometry \cite{OsuPag16}.
-The the reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}.
+The reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}.
 
@@
 When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
-When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$! 
+When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$
 Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
@@
 
-\ \\ \ \\
-{\bf XXX insert the double-slit figure here: Darsh.}
-\ \\ \ \\
+\begin{figure}[h!]
+\begin{center}.
+\includegraphics[scale = 0.5]{DSe.pdf}
+\caption{Schematic of the double slit experiment.
+The diagram shows two different scenarios.
+The top figure shows the behaviour one would expect of classical particles going through one slit or the other.
+The bottom figure shows the behaviour of classical waves creating an interference patter.
+Screen one shows the signal that one would see in each scenario (i.e classical particles or waves) if only one slit was open.
+If slit 1 was open we would see $P_1$ and see on.
+Screen 2 shows the signal we see if both the silts are open in each scenario.}
+\label{fig-doubleslit}
+\end{center}
+\end{figure}
 
@@
 The double-slit interference is an example that both the classical coherence and quantum unitarity can be calculated explicitly and show that they follow the same condition.
-Here, we advocate that such relation is actually a general rule.
-{\it Classical coherence, instead of thinking it as a practically of measurements, should be treated as a prerequisit to quantum unitarity.} 
-Thus when classical coherence fails, not only have we no practical measurements to confirm the purely of the subsystem wavefunction, such wavefunction {\it actually did not evolve unitarily.}
-Whatever effect responsible for a classsical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.
+Here, we advocate that such a relation is actually a general rule.
+{\it Classical coherence, instead of thinking of it as a practicality of measurements, should be treated as a prerequisit to quantum unitarity.} 
+Thus when classical coherence fails, not only have we no practical measurements to confirm the purity of the subsystem wavefunction, such wavefunctions {\it actually did not evolve unitarily.}
+Whatever effect responsible for a classical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.
 
-For quantum field theory in a curved spacetime, we always assume that the quantum fields is a subsystem that never entangles with the geometry, thus remains unitary.
+For quantum field theory in a curved spacetime, we always assume that the quantum field is a subsystem that never entangles with the geometry, thus remains unitary.
 Since we do not know quantum gravity/geometry, we cannot directly check this assumption by an actual calculation of entanglement.
-However, we can always check classical coherence, and by this rule we advocate, the answer directly prove/disprove subsystem unitarity.
+However, we can always check classical coherence, and by this rule we advocate, the answer directly proves/disproves subsystem unitarity.
 
-If we go back to the basic of quantum field theory, this new rule we advocate makes a lot of sense.
-As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state.
+If we go back to the basics of quantum field theory, this new rule we advocate makes a lot of sense.
+As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function $|\psi \rangle$, then quantizing its amplitude into a quantum state.
 Any method to measure such quantum state assumes the knowledge of the classical mode function. 
@@
 
-\ \\ \ \\
-{\bf XXX insert the QFT figure here: Darsh or I-Sheng}
+\begin{figure}[h!]
+\begin{center}.
+\includegraphics[scale = 0.5]{bh_coherence.pdf}
+\caption{Schematic showing the rule we advocate; as classical coherence fails, we loose quantum unitarity.}
+\label{fig-QFT}
+\end{center}
+\end{figure}
 
@@
 We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
-If such change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
+If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
@@
 
-More concretely, our setup is like in Fig.\ref{fig-setup}. 
+More concretely, our setup is shown in Fig.\ref{fig-setup}. 
 We start by choosing two points at some $r_0\gg M$ with a $\delta t_0\sim M$ coordinate time separation between them.
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{\Delta M}{r_1^2} \Delta r 
+\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
 \equiv \sigma \Delta r~.
@@
 \frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx
-\sigma \Delta l \left(\frac{2M}{l_1}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
+- \sigma \Delta l \left(\frac{2M}{l}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
 \label{eq-NearHorizon}
@@
 \footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, 
-there is an extra factor of $(2M/l_1)^2$ which diverges as the shell approaches the horizon.
+there is an extra factor of $(2M/l)^2$ which diverges as the shell approaches the horizon.
 
-The small $l_1$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
+The small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
 After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
-The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l_1$ at some scale that much longer than any scale that we expect UV problems. 
+The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
 By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
@@
 \section{Discussion}
+\label{sec-dis}
 
@@
 In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
-We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such check.
+We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such a check.
 As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
@@
 
-Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problem. 
+Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problems. 
 Usually, one pictures a nonunitarity process as losing information. 
@@
 
-\subsection{Proper time}
-
-\subsubsection{Background spacetime}
-
-First we consider the motion of Hawking photons coming from a Schwarzschild metric of the form
+A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric
 
 \begin{equation}
-	ds^2 = - \left( 1 - \frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2.
+	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
 \end{equation}
 
-Consider two Hawking photons coming from a fixed distance, $r_{e}$, just above a Schwarzschild black hole separated by a coordinate time interval $\bar{\delta t}_A$ and a corresponding proper time $\bar{\delta \tau}_A$ as shown in figure \ref{fig:1}.
-The two photons propagate through to the observer at $r_0$ following geodesics.
-We could potentially solve for the geodesics of the photons to find out the coordinate time of arrival of each photon, however in the absence of additional gravitational fields the coordinate time interval between the photons will not change\footnote{This will prove to be extremely helpful when we look at the calculation in the presence of shells.}, i.e $\bar{\delta t}_A = \bar{\delta t}_0$, and that is the quantity we need in order to compute the proper time $\bar{\delta \tau}_0$ observed by the observer at $r_0$,
+where we are working with units in which $G = c = 1$.
+We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}.
+Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole.
+An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$.
+We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}).
+By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation
+
+\begin{equation}
+	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
+\end{equation}
+
+where the superscript represents particle $1$ so $\bar{t_e}^{(1)}$ represents the time at which particle $1$ is emitted, $\bar{t_0}^{(1)}$ is when particle 1 is observed.
+Analogously for a particle $2$ that is emitted at $\bar{t_e}^{(2)}$ we have
+
+\begin{equation}
+	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
+\end{equation}
+
+Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that
+
+\begin{equation}
+	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
+\end{equation}
+
+Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.
+
+We can convert $\delta\bar{t_0}$ to proper time
+
+\begin{equation}
+	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
+\end{equation}
+
+and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.
+
+\subsubsection{Perturbed spacetime - double shell}
+
+Now we introduce two shells of matter with equal and opposite ADM mass, $-\Delta M$ and $\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
+We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells.
+In this case the particle's move through two different spacetime regions.
+Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M-\Delta M$ as shown in the top part of figure \ref{fig-setup}.
+\\
+\\
+As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$.
+Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$).
+To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC.
+The coordinate time intervals at $r_1$, in the two different regions, are therefore related by
+
+\begin{equation}
+	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M - \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
+\end{equation}
+
+We can propagate the particles through region $II$ from $r_1$ to $r_2$ and we know $\delta \hat{t}_1 = \delta \hat{t}_2$.
+From the fact that the proper time corresponding to the coordinate time intervals will be the same, we can relate $\delta \hat{t}_2$ back to $\delta t_2$ in region $I$,
+
+\begin{equation}
+	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M- \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
+\end{equation}
+
+Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$ by simply inverting Eq (\ref{7}) and multiplying by $ \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$,
 
 \begin{eqnarray}
-	\bar{\delta \tau}_0 & = & \left( 1- \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_0	\nonumber	\\
-	& = & \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2} \bar{\delta t}_A \approx \bar{\delta t}_{A} 
+	\delta \tau_0 & = & \delta t_0 \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}, 	\nonumber	\\
+	& =& \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
 \end{eqnarray}
 
-where in the last step we have assumed $r_0$ is very large.
-
-\subsubsection{Introducing perturbations: Double shells}
-
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[scale = 0.6]{Propertime.pdf}
-\caption{The two parts of this diagrams describe two different scenarios.
-The trajectories of the photon are the lines in orange.
-The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines.
-The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
-The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$.
-Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively.
-The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
-\label{fig:1}
-\end{center}
-\end{figure}
-
-In this section we consider the top part of figure \ref{fig:1}.
-To distinguish the results from the previous section without shell we will not have an overbar in any of the quantities described in this scenario.
-The same initial conditions for the two Hawking photons are assumed.
-Using the argument described in the previous section we expect the coordinate time intervals between $r_A$ and $r_1$ to be equal, $\delta t_A = \delta t_1$.
-Analogously for the coordinate time interval between $r_2$ and $r_0$, $\delta t_2 = \delta t_0$.
-The new region is between $r_2$ and $r_1$ where the metric is different; it is defined by a mass $M - \Delta M$.
-The coordinate time interval at $r_1$ will also have a representation in the $II$ metric.
-Quantities evaluated in the $II$ metric will be denoted by a hat on top.
-By imposing the physical condition that there cannot be any discontinuities in spacetime we know that the proper times in both the metrics must be the same at $r_1$, $\delta \tau_1 = \delta \hat{\tau}_1$ and this gives a relation between the coordinate time intervals
+Since we assume the observer is far away we can neglect the term $\frac{2M}{r_0}$. The difference between the proper time interval in the presence of shells to the value without shells is
 
 \begin{equation}
-	\delta t_1 = \left( \frac{1 - \frac{ 2(\Delta M -M)}{r_1})}{1 - \frac{ 2M}{r_1}}  \right)^\frac{1}{2} \delta \hat{t}_1.	\label{shell1}
+	\delta \tau_0 - \delta \bar{\tau_0} = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M -\Delta M)}{r_2 - 2(M- \Delta M)} \right)^\frac{1}{2} - 1\right),
 \end{equation}
 
-Applying the same condition to the proper times at $r_2$ gives the analogous relation between the coordinate time intervals at $r_2$,
+since $\delta t_e = \delta \bar{\tau_0}$ when the observer is far away, we can define a dimensionless quantity,
 
 \begin{equation}
-	\delta t_2 = \left( \frac{1 - \frac{ 2(\Delta M -M)}{r_2})}{1 - \frac{ 2M}{r_2}}  \right)^\frac{1}{2} \delta \hat{t}_2. 	\label{shell2}
+	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M-\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
 \end{equation}
 
-Since $\delta \hat{t}_1$ and $\delta \hat{t}_2$ are both evaluated in the same metric they must be equal and therefore we can combine Eq (\ref{shell1}) and Eq (\ref{shell2}) to give a relation between $\delta t_1$ and $\delta t_2$,
+This expression is exact in the limit that the observer is far away. By expressing the distances from the horizon as, 
+\begin{eqnarray}
+	r_1 & = & 2M + \epsilon 	\nonumber	\\
+	 r_2 & = & 2M + \epsilon + \epsilon 	\label{11'},
+\end{eqnarray}
+
+we can write Eq (\ref{10}) as
+
+\begin{equation}
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right).
+\label{12}
+\end{equation}
+
+This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect.
+More interestingly we see that there is no $M$ dependence in this equation.
+This suggests the effect is present in flat space as well.
+One may interpret this effect as being a phase shift between the photons as the travel through two different gravitational potential wells.
+Before jumping to any conclusions, however, we should convert the coordinate quantities in Eq (\ref{12}) into physical quantities.
+
+%
+%where $\epsilon<<2M, \ \epsilon << \epsilon$. To leading order in small quantities Eq (\ref{10}) becomes, 
+%
+%\begin{equation}
+%	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = - \frac{\Delta M \epsilon}{\epsilon^2}.	\label{11}
+%\end{equation}
+
+\subsection{Defining local quantities}
+
+\subsubsection{Energy of shell}
+
+There is a natural choice of what physical quantity we should use to replace $\Delta M$ with and that is the $tt$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC
+
+\begin{equation}
+	S^a_b =  [K^a_b] - [K]h^a_b
+\end{equation}
+
+where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics.
+We can define the induced metrics for constant $r$ values; for region $I$ it is
+
+\begin{equation}
+	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+\end{equation}
+
+Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
+
+\begin{equation}
+	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+\end{equation}
+
+We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
+Therefore it is easy to find a relation between the two time coordinates
+
+\begin{equation}
+	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
+\end{equation}
+
+Using this, we calculate the extrinsic curvature components
 
 \begin{eqnarray}
-	\delta t_{1} & = & \left( \frac{ \left( 1 - \frac{2 M - \Delta M}{r_{1}} \right) \left( \frac{1 - 2M}{r_{2}} \right)}{\left( 1 - \frac{2M}{r_{1}} \right)  \left( 1 - \frac{2(M - \Delta M)}{r_{2}} \right)} \right)^\frac{1}{2} \delta t_{2}	\nonumber	\\
-	& = & \left( \frac{2M - r_2}{2M - r_1} \right)^\frac{1}{2} \left( \frac{ 2(\Delta M - M) + r_1}{2(\Delta M - M) + r_2} \right)^\frac{1}{2} \delta {t}_{2}.
+	K^t_t^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
+	K^\theta_\theta^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} = K^\phi_\phi^{(M)}	\label{16}
 \end{eqnarray}
 
-We see that $\delta t_1 = \delta t_2$ in the limit that $r_1 = r_2$ as then the shells will cancel out their masses and we are left with just metric $I$.
-By continuing these trajectories forward to the observer at $r_0$ we know that $\delta t_0 = \delta t_2 \approx \delta \tau_0$.
-
-%\begin{SCfigure}
-% \centering
-%\includegraphics[height= 7 cm]{Propertime.pdf}	\label{fig:1}
-%  \caption{The two parts of this diagrams describe two different scenarios.
-The trajectories of the photon are the lines in orange.
-The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines.
-The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
-The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$.
-Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively.
-The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
-%\end{SCfigure}
-
-%\twocolumngrid
-
-Without shells we saw that the proper time interval $\bar{\delta \tau}_0 \approx \delta t_A$, thus the difference in the proper time intervals with the shells is
+where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
+Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
+With these ingredients we compute the $00$ component of the surface stress energy tensor
 
 \begin{equation}
-	\delta \tau_0 - \bar{\delta \tau_0} = \delta t_A \left( \left( \frac{2M - r_2}{2M - r_1} \right)^\frac{1}{2} \left( \frac{ 2(\Delta M - M) + r_1}{2(\Delta M - M) + r_2} \right)^\frac{1}{2} - 1 \right).
-	\label{PTD}
+	S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
 \end{equation}
-As a check we see that when $r_1 = r_2$, $\delta \tau_0 = \bar{\delta \tau}_0$ as expected.
 
-We can explore this relation further by going to a region close to the horizon.
-If we choose $r_1 = 2M + \epsilon_1$ and $r_2 = 2M + \epsilon_2$ where $\epsilon_{1,2} <<1$, the expression in Eq (\ref{PTD}) reduces to
+This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$
 
 \begin{equation}
-	\delta \tau_0 - \bar{\delta \tau_0} = \left( \left( \frac{\epsilon_2}{\epsilon_1} \left( \frac{2\Delta M + \epsilon_1}{2 \Delta M + \epsilon_2}\right) \right)^\frac{1}{2} - 1 \right) 
+	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
 \end{equation}
 
-\subsection{Frequency of Hawking photons}
+%Substituting in for $r_1 = 2M + \epsilon$, where $\Delta M<<\epsilon<<2M$ and expanding to leading order in small quantities, 
+%
+%\begin{equation}
+%	\mathcal{E} = \left( \frac{2M}{\epsilon} \right)^\frac{1}{2} \Delta M.
+%\end{equation}
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[scale = 0.6]{frequency.pdf}
-\caption{This diagram follows the same notation as figure \ref{fig:1} except we are looking at one photon represented by the orange line.
-The frequency at each relevant point is denoted on the diagram.
-The quantities in the metric $I$ on the left of the shells are denoted with overbars.
-Quantities in metric $II$ are denoted without any overbars or hats.
-Quantities in metric $I$ to the right are denoted with hats on top.}
-\label{fig:2}
-\end{center}
-\end{figure}
+%
+%\subsubsection{Proper time between shells}
+%
+%We calculate the proper time between the two shells, $\tau_{12}$, as seen by an observer at the first shell\footnote{One could also calculate the proper length between the shells.}.
+This is done with a view to replace $\delta \epsilon$ by $\tau_{12}.
+%
+%\begin{eqnarray}
+%	\tau_{12} & = & \int^{t_2}_{t_1} \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} dt	\nonumber	\\
+%	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (t_2 - t_1)	\nonumber	\\
+%	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (r_2 - r_1 + 2M' \ln \left( \frac{r_2 - 2M'}{r_1 - 2M'} \right) \right).	
+%\end{eqnarray}
+%
+%We substitute in for $r_1$ and $r_2$ from Eq (\ref{11'}) to give
+%
+%\begin{equation}
+%	\tau_{12} = \delta \epsilon \left( \frac{\epsilon}{2M} \right)^\frac{1}{2} \left( 1 + \frac{2M}{\epsilon} \right).
+%\end{equation}
+%
 
-\subsubsection{Background spacetime}
-We can do an analogous calculation to see this effect.
-Instead of looking at the proper time interval between photons we can consider the shift in frequency of single Hawking photon in the same two scenarios as were described in the previous section.
-We can write the photon four vector at distance $r$ as
+\subsubsection{Proper distances}
+
+The proper length $l$ between the horizon and shell is,
+
+\begin{eqnarray}
+	l & = & \int^{2M + \epsilon}_{2M} \frac{dr}{\left( 1 - \frac{2M}{r} \right)^\frac{1}{2}}	\nonumber	\\
+	& = & (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
+\end{eqnarray}
+
+Similarly, the proper distance between the two shells, $\delta l$, is given by
+
+\begin{eqnarray}
+	\delta l & = & \int^{2M + \epsilon + \delta \epsilon}_{2M + \epsilon} \frac{dr}{\left(1 - \frac{2M'}{r} \right)^\frac{1}{2}} \nonumber	\\
+	& = & (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
+\end{eqnarray}
+
+Eqs (\ref{19}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
+It is not possible to do this analytically but it can be done numerically.
+We show the plots of $\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}}$ as functions of $M$.
+\\
+\\
+We can obtain analytic expressions in the limit that the shells are very close to the horizon and this is what is presented in the next section.
+
+\subsection{Near horizon limit}
+
+In the near horizon limit we assume $\epsilon<< 2M$ and furthermore assume that the perturbations $\Delta M, \delta \epsilon$ are much smaller than $\epsilon$.
+Under these assumptions Eq (\ref{12}), to leading order om small quantities, becomes
 
 \begin{equation}
-	\bar{k}^\mu (\bar{\omega}_\infty, \bar{r}) = \bar{\omega}_\infty \left( \left( 1 - \frac{2M}{\bar{r}_A} \right)^{-1}, \sqrt{ 1 - \frac{\bar{b}^2}{\bar{r}_A^2} \left( 1 - \frac{2M}{\bar{r}_A} \right)}, \frac{\bar{b}}{\bar{r}_A^2}, 0 \right),
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = - \frac{\Delta M \delta \epsilon}{\epsilon^2}
 \end{equation}
-where $\bar{\omega}_\infty$ is the frequency observed by a stationary observer at infinity and $b$ is the impact parameter of the photon.
-The general four velocity, $\bar{u}^\mu(\bar{r})$ of a stationary object in this geometry is
+
+and the conversion to proper quantities from Eqs (\ref{19}, \ref{20}, \ref{21}) gives, to leading order,
 
 \begin{equation}
-	\bar{u}^\mu(\bar{r}) = \left( \left( 1 - \frac{2M}{\bar{r}} \right)^{-\frac{1}{2}}, 0, 0, 0 \right).
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} =  - \frac{\mathcal{E} \delta l}{l^2} = - \sigma \delta l \left( \frac{2M}{l} \right)^2
 \end{equation}
 
-In the case where there are no shells, $\bar{\omega}_\infty$ is exactly the frequency observed by the observer at $\bar{r}_0$ in the limit that $\bar{r}_0 \rightarrow \infty$.
-In general, the frequency observed at $\bar{r}_0$, $\bar{\omega}_0$, will be redshifted
+where $\sigma \approx \frac{\mathcal{E}}{(2M)^2}$.
 
-\begin{eqnarray}
-	\bar{\omega}_0 & = & \bar{k}^\mu(\bar{\omega}_\infty, \bar{r}_0) \bar{u}^\nu(\bar{r}_0) \bar{g}_{\mu \nu}(\bar{r}_0) 	\nonumber	\\
-	& = & - \bar{\omega}_\infty \left( 1 - \frac{2M}{\bar{r}_0} \right)^{-\frac{1}{2} }
-\end{eqnarray}
+%to leading order this reduces to 
+%
+%\begin{equation}
+%	l = 2 (2 \epsilon M)^\frac{1}{2}.	\label{25}
+%\end{equation}
+%
+%We can further calculate $\delta l$, the distance between the two shells, from Eq (\ref{25})
+%
+%\begin{equation}
+%	\delta l = \frac{4 M \delta \epsilon}{l}.
+%\end{equation}
 
-of course in the limit $\bar{r}_0 \rightarrow \infty$ we get $\bar{\omega}_0 = -\bar{\omega}_\infty$.
-
-\subsubsection{Introducing perturbations: Double shells}
-
-The frequency measured at $r_1$ in metric $I$, $\bar{\omega}_1$ is
-
-\begin{equation}
-	\bar{\omega}_1 = - \bar{\omega}_\infty \left (1 - \frac{2M}{\bar{r}_1} \right)^{-\frac{1}{2}}.
-\end{equation}
-
-In metric $II$ the observed frequency $\omega_1$ is
-
-\begin{eqnarray}
-	\omega_1 & = & g_{\mu \nu}(r_1) k^\mu(\omega_\infty, r_1) u^\nu(r_1)	\nonumber	\\
-	& = & - \omega_\infty \left( 1 - \frac{2(M- \Delta M)}{r_1} \right)^{-\frac{1}{2}}.
-\end{eqnarray}
-
-Since $\omega_1$ is a physical quantity we expect it to be the same in both in metrics, $\omega_1 = \bar{\omega}_1$ and also we expect $r_1 = \bar{r}_1, r_2 = \bar{r}_2$ (since the radius of the shell corresponds to a physical sphere of radius of $r$).
-This gives a relation between $\omega_\infty$ and $\bar{\omega}_\infty$
-
-\begin{equation}
-	\bar{\omega}_\infty = \omega_\infty \left( 1 - \frac{2 \Delta M}{2(\Delta M  - M)+ r_1} \right)^\frac{1}{2}.	\label{13}
-\end{equation}
-
-At $r_2$ we can again equate the observed frequencies in both metrics.
-In this case we define the frequency observed at infinity in metric $I$ on the right side of $r_2$ as $\hat{\omega}_\infty$, i.e the photon vector in metric $I$ for $r > r_2$ is $\hat{k}$ (But we expect the four velocity of the shell to be $\bar{u}_2$).
-From $k^\mu(\omega_2, r_2) u^\nu(r_2) g_{\mu \nu}(r_2) = \hat{k}^\mu(\bar{r}_2) \bar{u}^\nu(\bar{r}_2) \bar{g}_{\mu \nu} (\bar{r}_2)$ we have
-
-\begin{equation}
-	\hat{\omega}_\infty = \omega_\infty \left( 1 - \frac{2 \Delta M}{2(M-\Delta M) + r_2} \right)^\frac{1}{2}.	\label{14}
-\end{equation}
-
-By combining Eq (\ref{13}) and (\ref{14}) we get
-
-\begin{equation}
-	\hat{\omega}_\infty = \bar{\omega}_\infty \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
-\end{equation}
-
-The observed frequency at $r_0$, $\hat{\omega}_0$, is
-
-\begin{eqnarray}
-	\hat{\omega}_0 & = & u^\mu(r_0) k^\nu(\hat{\omega}_\infty, r_0) g_{\mu \nu}(r_0) 	\nonumber	\\
-	& = & - \bar{\omega}_\infty \left( 1 - \frac{2M}{r_0} \right)^{-\frac{1}{2}}  \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
-\end{eqnarray}
-
-In the limit that $r_0 \rightarrow \infty$,
-
-\begin{equation}
-	\hat{\omega}_0 = - \bar{\omega}_\infty \left( \frac{(2 (\Delta M - M) + r_1)(r_2 - 2M)}{(r_1 - 2M)(2(\Delta M - M) + r_2)} \right)^\frac{1}{2}
-\end{equation}
-
-Looking at dynamics close to the horizon,
-
-\begin{eqnarray}
-	r_1 & = & 2M + \epsilon_1	\nonumber	\\
-	r_2 & = & 2M + \epsilon_2
-\end{eqnarray}
-
-we get
-
-\begin{equation}
-	\hat{\omega}_0 = - \bar{\omega}_\infty \left( \frac{\epsilon_2}{\epsilon_1} \left( \frac{2 \Delta M + \epsilon_1}{2 \Delta M + \epsilon_2} \right) \right)^\frac{1}{2}
-\end{equation}
+%Using these local quantities to replace the coordinate quantities in Eq (\ref{11}) gives
+%
+%\begin{equation}
+%	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \frac{4 \mathcal{E} \delta l}{l^2}.	\label{24'}
+%\end{equation}
+%
+%We want to define the local energy density of the shell, $\sigma$, which is, in the near horizon limit, given by $\sim \frac{\mathcal{E}}{(2M)^2}$. Thus we can rewrite Eq (\ref{24'}) by, 
+%
+%\begin{equation}
+%	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta {\bar{\tau_0}}} = 4 \sigma \delta l \left( \frac{M}{l} \right)^2	\label{25'}
+%\end{equation}
+%
+%If we take $\sigma$ and $\delta l$ to be fixed (since they represent the fluctuations of the spacetime), we see that Eq (\ref{25'}) increases linearly with $M$.
 

### 2016-07-29 Draft_BH_shells.tex
merged

@@
 \begin{abstract}
-The black hole information paradox presumes that local quantum field theory can provide unitary propagations for near-horizon modes to asymptotic Hawking quanta. 
-Instead of invoking unknown quantum-gravity effects to modify this assumption, we propose a self-consistency check.
+The black hole information paradox presumes that local quantum field theory can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
+Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
 We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
-Feynman showed that the assumption of subsystem unitarity in double-slit experiment, namely ignoring the entanglement with the double-slit, becomes arbitrarily reliable when the screen to project the interference pattern on goes infinitely far away.
-Analogously, here we ask whether unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole. 
-We present strong evidence that the result is negative, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
+Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
+Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole and asymptotic observers.
+We present curious results to suggest a negative answer, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
 \end{abstract}
@@
 \item {\bf Local quantum field theory:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
-It manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
+For large black holes, it manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
 \end{itemize}
@@
 In other words, {\bf the application of local QFT to a unitary propagation of Hawking quantum is not self-consistent. } 
-This should provide a much stronger motivation to modify the second statement than the other two. 
+This should provide a much stronger motivation to modify the last statement instead of the other two. 
 Although there are still many different proposals capable of doing that, we hope such discovery can focus our efforts and make the progress even further.
@@
 Before diving into details, we should explain why we focus on the last statement.
-That is becasue local QFT simply assumes a subsystem unitarity.
+That is because local QFT simply assumes {\bf subsystem unitarity}.
 Quantum mechanical evolution of a full system is by-definition unitary. 
@@
 The fundamental principle behind Feynman's trick is that ``classical wave coherence'' should be taken as the prerequisite of ``quantum unitarity''. 
-In Sec.\ref{sec-QFT}, we argue that it has a natural generalization to local QFT in curved spacetime, thus we can apply it to re-examine the propagation of Hawking quanta.
+In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
+We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from quantizing graviton.
 
-In Sec.\ref{sec-BlackHole}, we will provide our detailed analysis and analogy. 
-The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruin its subsystem unitarity. 
-We then assume that the unknown quantum nature of geometry can be parametrized by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
+In Sec.\ref{sec-BlackHole}, we apply the self-consistency check to the propagation of Hawking quanta in a close analogy to Feynman's analysis. 
+The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
+We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
 A classical wave plays the role of the interference pattern. 
@@
 First of all, our self-consistency check should be generally applicable to any geometry, and it does not invalidate local QFT entirely. 
-Likewise, even when unitarity is lost in local QFT, the values of many observables do not have to change. 
+Even when unitarity is lost in local QFT, the values of many observables do not have to change. 
 Most existing applications of QFT in curved spacetime actually only care about the expectation value of particle numbers, which can be unaffected by the loss of subsystem unitarity. 
@@
 
-One might object that the above analysis is only applicable if we are {\it given} a particular value of $\Delta y^{\rm ds}$, while in fact such quantity has to originate from the unknown quantum mechanics of the double-slit.
+One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit. 
 This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
 Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit. 
-Namely, its value should be fixed if we move the screen further away.
-Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition.
+Namely, its value should be fixed if we move the screen further away. Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition. 
 Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible, thus the subsystem unitarity is valid.
@@
 
-If we go back to the basics of quantum field theory, this new rule we advocate makes a lot of sense.
-As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function $|\psi \rangle$, then quantizing its amplitude into a quantum state.
+If we go back to the basic of quantum field theory, there is a natural generalization of this new rule. 
+As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state. 
 Any method to measure such quantum state assumes the knowledge of the classical mode function. 
@@
 \end{figure}
+
+While such generalization to QFT seems straightforward in theory, there are a few subtleties in practice.
+In the double-slit experiment, the position uncertainty of the double-slit was the only obvious uncertainty of the background that we need to keep track of.
+It is also the reasonable thing to hold fixed while moving the projection screen away.
+In QFT, the background is the entire geometry, and there are infinitely many ways a geometry can be uncertain.
+For a full analogy to Feynman's analysis, not only we need to parametrize those uncertainties, we also need to choose the appropriate combination to hold fixed as we take a similar limit.
+At this moment, we do not have a general formalism to setup such self-consistency check that can be applied to any general geometry. 
+In Sec.\ref{sec-BlackHole}, we propose a specific way to apply such self-consistency check to the propagation of Hawking quanta.
+In addition to gaining insights into the information paradox, we hope to learn some lessons to inspire a more general formalism of such self-consistency check.
+
+QFT theorists might think that a more direct self-consistency check is feasible.
+Instead of parametrizing a classical geometric uncertainty, one can treat deviations from the background geometry as a field and quantize it as any other fields.
+Then a standard QFT calculation of scattering with this new field (graviton) should capture all interactions with the geometry, and a small scattering amplitude should guarantee that the interaction is suppressed.
+The concern for such method is that IR issues for these scattering calculations cannot be unambiguously regulated like in global Minkowski space.
+Since soft gravitons lead to real physical changes in the geometry that can be seen in memory effects \cite{Wei65,HeLys14}, an IR ambiguity signals our ignorance on how these geometric changes enter QFT.
+Thus a direct graviton scattering calculation cannot be the full extend of a self-consistency check, and it is reasonable for our method to give extra constraints on the reliability of local QFT.
 
@@
 \begin{eqnarray}
-	K^t_t^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
-	K^\theta_\theta^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} = K^\phi_\phi^{(M)}	\label{16}
+	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
+	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
+	= (K^\phi_\phi)^{(M)}	\label{16}
 \end{eqnarray}

### 2016-08-13 Draft_BH_shells.tex
updated appendix with new results

@@
 Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
-Based on this picture, one may try to quantize the soft hairs and build a toy model that invovles quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
+Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
 That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.
@@
 
-where the superscript represents particle $1$ so $\bar{t_e}^{(1)}$ represents the time at which particle $1$ is emitted, $\bar{t_0}^{(1)}$ is when particle 1 is observed.
-Analogously for a particle $2$ that is emitted at $\bar{t_e}^{(2)}$ we have
+where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2.
 
@@
 
-We can convert $\delta\bar{t_0}$ to proper time
-
-\begin{equation}
-	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
-\end{equation}
-
-and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.
+%We can convert $\delta\bar{t_0}$ to proper time
+%
+%\begin{equation}
+%	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
+%\end{equation}
+%
+%and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.
 
@@
 
-Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$ by simply inverting Eq (\ref{7}) and multiplying by $ \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$,
+Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$,
 
-\begin{eqnarray}
-	\delta \tau_0 & = & \delta t_0 \left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}, 	\nonumber	\\
-	& =& \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
-\end{eqnarray}
+\begin{equation}
+	\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
+\end{equation}
 
@@
 
-This expression is exact in the limit that the observer is far away. By expressing the distances from the horizon as, 
-\begin{eqnarray}
-	r_1 & = & 2M + \epsilon 	\nonumber	\\
-	 r_2 & = & 2M + \epsilon + \epsilon 	\label{11'},
-\end{eqnarray}
-
-we can write Eq (\ref{10}) as
+This expression is exact in the limit that the observer is far away.
+By expressing the distances from the horizon as, $r_1  =  2M + \epsilon,  r_2  =  2M + \epsilon + \delta \epsilon$, we can write Eq (\ref{10}) as
 
 \begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right).
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \delta \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \delta \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right).
 \label{12}
@@
 \begin{equation}
-	S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
+	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
 \end{equation}
 
-This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$
-
-\begin{equation}
-	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
-\end{equation}
+%This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$
+%
+%\begin{equation}
+%	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
+%\end{equation}
 
@@
 
-\begin{eqnarray}
-	l & = & \int^{2M + \epsilon}_{2M} \frac{dr}{\left( 1 - \frac{2M}{r} \right)^\frac{1}{2}}	\nonumber	\\
-	& = & (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
-\end{eqnarray}
+\begin{equation}
+	l =  (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
+\end{equation}
 
@@
 
-\begin{eqnarray}
-	\delta l & = & \int^{2M + \epsilon + \delta \epsilon}_{2M + \epsilon} \frac{dr}{\left(1 - \frac{2M'}{r} \right)^\frac{1}{2}} \nonumber	\\
-	& = & (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
-\end{eqnarray}
+\begin{equation}
+	\delta l = (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
+\end{equation}
 
-Eqs (\ref{19}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
+Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
 It is not possible to do this analytically but it can be done numerically.
@@
 In the near horizon limit we assume $\epsilon<< 2M$ and furthermore assume that the perturbations $\Delta M, \delta \epsilon$ are much smaller than $\epsilon$.
-Under these assumptions Eq (\ref{12}), to leading order om small quantities, becomes
+Under these assumptions Eq (\ref{12}), to leading order in small quantities, becomes
 
@@
 
-and the conversion to proper quantities from Eqs (\ref{19}, \ref{20}, \ref{21}) gives, to leading order,
+and the conversion to proper quantities from Eqs (\ref{sig}, \ref{20}, \ref{21}) gives, to leading order,
 
 \begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} =  - \frac{\mathcal{E} \delta l}{l^2} = - \sigma \delta l \left( \frac{2M}{l} \right)^2
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.
 \end{equation}
-
-where $\sigma \approx \frac{\mathcal{E}}{(2M)^2}$.
 
@@
 
+\begin{figure}[h!]
+\begin{center}.
+\includegraphics[scale = 0.5]{tau_compare.pdf}
+\caption{}
+\label{}
+\end{center}
+\end{figure}
+
 \bibliography{all_active}

### 2016-08-16 Draft_BH_shells.tex

@@
 \item {\bf Local quantum field theory:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
-For large black holes, it manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
+For large black holes, it manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
 \end{itemize}
@@
 Fortunately, Feynman, in his famous lectures, presented an interesting trick to circumvent this obstacle. 
-This trick, to a certain extend, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
+This trick, to a certain extent, enables us to perform a {\bf self-consistency check} of the classical-background assumption {\bf without} knowing the quantum nature of the background.
 In Sec.\ref{sec-DoubleSlit}, we will review Feynman's analysis of the double-slit experiment. 
@@
 \item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
-By relating it to the presence of extra matter, we can express it to a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
+By relating it to the presence of extra matter, we can express it as a gauge-invariant local quantity, which is the natural thing to hold fixed in our analysis.
 \end{enumerate}
@@
 As far as we know, an observable that explicitly checks the subsystem unitarity of local QFT is the cosmological Bell inequality \cite{Mal15}. 
-One can apply our self-consistency check to such model and update the prediction of whether a violation of Bell inequality is actually expected.
+One can apply our self-consistency check to such a model and update the prediction of whether a violation of Bell inequality is actually expected.
 
@@
 \section{Calculation}
-
-{\bf XXX Modify the content accordingly to fit their status in the appendix: Darsh/Daniel.}
 
@@
 
-Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0$,
-
-\begin{equation}
-	\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \left( 1 -\frac{2M}{r_0} \right) \right)^\frac{1}{2}. 
-\end{equation}
-
-Since we assume the observer is far away we can neglect the term $\frac{2M}{r_0}$. The difference between the proper time interval in the presence of shells to the value without shells is
-
-\begin{equation}
-	\delta \tau_0 - \delta \bar{\tau_0} = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M -\Delta M)}{r_2 - 2(M- \Delta M)} \right)^\frac{1}{2} - 1\right),
-\end{equation}
-
-since $\delta t_e = \delta \bar{\tau_0}$ when the observer is far away, we can define a dimensionless quantity,
+Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \right)^\frac{1}{2}$.
+Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away.
+$\delta t_e = \delta \bar{\tau_0}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,
 
@@
 where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics.
-We can define the induced metrics for constant $r$ values; for region $I$ it is
+%
+%We can define the induced metrics for constant $r$ values; for region $I$ it is 
+%
+%\begin{equation}
+%	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+%\end{equation}
+%
+%Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
+%
+%\begin{equation}
+%	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+%\end{equation}
+%
+%We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
+Therefore it is easy to find a relation between the two time coordinates
+%
+%\begin{equation}
+%	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
+%\end{equation}
+%
+%Using this, we calculate the extrinsic curvature components
+%
+%\begin{eqnarray}
+%	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
+%	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
+%	= (K^\phi_\phi)^{(M)}	\label{16}
+%\end{eqnarray}
+%
+%where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
+Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
 
-\begin{equation}
-	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
-\end{equation}
-
-Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
-
-\begin{equation}
-	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
-\end{equation}
-
-We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
-Therefore it is easy to find a relation between the two time coordinates
-
-\begin{equation}
-	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
-\end{equation}
-
-Using this, we calculate the extrinsic curvature components
-
-\begin{eqnarray}
-	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
-	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
-	= (K^\phi_\phi)^{(M)}	\label{16}
-\end{eqnarray}
-
-where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
-Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
-With these ingredients we compute the $00$ component of the surface stress energy tensor
+The $tt$ component of the surface stress energy tensor is
 
@@
 We show the plots of $\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}}$ as functions of $M$.
-\\
-\\
-We can obtain analytic expressions in the limit that the shells are very close to the horizon and this is what is presented in the next section.
+We can obtain analytic expressions for Eq (\ref{12}) in the limit that the shells are very close to the horizon and this is what is presented in the next section.
 
@@
 
-\begin{figure}[h!]
-\begin{center}.
-\includegraphics[scale = 0.5]{tau_compare.pdf}
-\caption{}
-\label{}
-\end{center}
-\end{figure}
-
 \bibliography{all_active}

### 2016-08-26 Draft_BH_shells.tex

@@
 \end{itemize}
+Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quantum by a unitary transformation, therefore carrying the same qubit of information. 
+However statement 1 and 2 demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
+This conflict has inspired many different proposals to modify one of the above three statements. 
+For example, information loss or remnant \cite{Bek94} modifies Statement One; 
+firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
+\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch.}
+modifies Statement Three.
 
-This conflict has inspired many different proposals to modify one of the above three statements. 
-For example, information loss or remnant \cite{Bek94} {\bf (XXX anyone knows a better reference for remnants?)} modifies the first statement; 
-firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies the second statement;
-various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
-\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch.
-Since ``whether there exists a causal patch to fit'' is a highly nonlocal condition, it is effectively a break-down of local QFT.} 
-modifies the last statement.
-Unfortunately, since the paradox only shows a conflict with the three statements combined, it is up to individual taste/bias to modify any one of them.
+In this paper, we will try to provide a stronger motivation to modify Statement Three. 
+In fact, we will argue that it is already problematic on its own. 
+In other words, {\bf the application of local QFT to a unitary propagation of Hawking quantum is not self-consistent. }
 
-In this paper, we will try to sharpen the problem even further. 
-We will try to argue that the last statement on its own is already self-conflicting. 
-In other words, {\bf the application of local QFT to a unitary propagation of Hawking quantum is not self-consistent. } 
-This should provide a much stronger motivation to modify the last statement instead of the other two. 
-Although there are still many different proposals capable of doing that, we hope such discovery can focus our efforts and make the progress even further.
+Before presenting our argument, we will first explain its relation to some existing ideas.
+The recent paper by Osuga and Page \cite{OsuPag16} provides an abstract framework of how modifying Statement Three resolves the paradox.
+Basically, the near horizon mode is thermal as demanded by Statement Two.
+But it propagates out in a non-unitary process, gaining the appropriate information to restore a unitary $S$-matrix as demanded by Statement One. 
+For such abstract model to work in practice, such non-unitary propagation should be understood as interacting with a hidden system.
+Here hidden simply means something that is ignorant to a na\"ive application of local QFT.
+The obvious candidate of such hidden system is the geometry.
+
+One proposal along this line of thoughts was discussed in \cite{NomVar12}. 
+The idea was that the black hole acquires a large uncertainty during the evaporation process. 
+If we treat the superposition of different classical geometries (black holes with different locations/momenta) as a quantum system, it may qualify as the hidden system that is responsible for the non-unitary propagation of Hawking quanta.
+Unfortunately, such proposal can be defeated by counting entropy.
+In order for a non-unitary process to restore the asymptotic $S$-matrix, this hidden system must store the required information, which is comparable to the mount of microscopic information carried by the black hole.
+However, the black-hole-no-hair theorem states that two black holes with identical macroscopic parameters (mass, angular momentum, change) are isometric to each other. 
+This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
+As a result, the Hilbert space of superposed classical geometries has far less dimensions than necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
+Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix; therefore such modification of Statement Three alone is insufficient to resolve the paradox.
+
+The recent development on black-hole-soft-hairs \cite{HawPer16} hinted a way to revive this idea.
+Basically, it was realized that two isometric (regions of) geometries should not always be considered as the same state.
+If one maps the geometries with congruences of geodesics, two isometric regions with different maps are actually different states.
+That is because changes in the mapping geodesics are measurable memory effects, and a consistent physical theory must be able to distinguish them.
+This realization dramatically increases the number of different states encoded in classical geometries.
+A tentative counting of state on a black hole horizon yields exactly the required number such that a modification to Statement Three can indeed resolve the paradox.
 

### 2016-09-09 Draft_BH_shells.tex
Small changes made to appendix
intro update

@@
 Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quantum by a unitary transformation, therefore carrying the same qubit of information. 
-However statement 1 and 2 demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
+However Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
 This conflict has inspired many different proposals to modify one of the above three statements. 
@@
 But it propagates out in a non-unitary process, gaining the appropriate information to restore a unitary $S$-matrix as demanded by Statement One. 
-For such abstract model to work in practice, such non-unitary propagation should be understood as interacting with a hidden system.
+For such abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
 Here hidden simply means something that is ignorant to a na\"ive application of local QFT.
@@
 The idea was that the black hole acquires a large uncertainty during the evaporation process. 
-If we treat the superposition of different classical geometries (black holes with different locations/momenta) as a quantum system, it may qualify as the hidden system that is responsible for the non-unitary propagation of Hawking quanta.
+If we treat the superposition of different classical geometries as a quantum system, it may qualify as the hidden system that is responsible for the non-unitary propagation of Hawking quanta. 
 Unfortunately, such proposal can be defeated by counting entropy.
-In order for a non-unitary process to restore the asymptotic $S$-matrix, this hidden system must store the required information, which is comparable to the mount of microscopic information carried by the black hole.
-However, the black-hole-no-hair theorem states that two black holes with identical macroscopic parameters (mass, angular momentum, change) are isometric to each other. 
+In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the mount of microscopic information carried by the black hole.
+However, the black-hole-no-hair theorem states that two black holes with identical macroscopic parameters (mass, momentum, angular momentum, charge) are isometric to each other. 
 This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
@@
 This realization dramatically increases the number of different states encoded in classical geometries.
-A tentative counting of state on a black hole horizon yields exactly the required number such that a modification to Statement Three can indeed resolve the paradox.
+A tentative counting of state on a black hole horizon yields exactly the required number such that a modification to Statement Three can indeed resolve the paradox \cite{HawPer16}.
 
-Before diving into details, we should explain why we focus on the last statement.
-That is because local QFT simply assumes {\bf subsystem unitarity}.
+In this paper, we still take another step that is complementary to the above progress. It is exciting to know that modifying Statement Three can in-principle resolve the paradox. 
+However, it remains a great mystery of why should local QFT break down in low curvature regions. 
+If we just demand that it breaks down in order to resolve the information paradox, then there is no reason why this solution is preferred over modifying Statement One or Two. 
+We would like argue that the application of QFT to a unitary propagation from a near horizon mode to an asymptotic Hawking quantum is already self-inconsistent. 
+Thus it is only natural to modify Statement Three.
+
+The starting point of our argument involves no new physics at all.
+We simply recognize that local QFT implies a standard assumption of {\bf subsystem unitarity}.
 Quantum mechanical evolution of a full system is by-definition unitary. 

### 2016-09-12 Draft_BH_shells.tex
Updated the calculation in main text

@@
 \item {\bf Local quantum field theory:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
-For large black holes, it manifests as a unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
+For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
 \end{itemize}
-Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quantum by a unitary transformation, therefore carrying the same qubit of information. 
-However Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
+Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, therefore carrying the same qubit of information. 
+However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
 This conflict has inspired many different proposals to modify one of the above three statements. 
@@
 Unfortunately, such proposal can be defeated by counting entropy.
-In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the mount of microscopic information carried by the black hole.
+In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the amount of microscopic information carried by the black hole.
 However, the black-hole-no-hair theorem states that two black holes with identical macroscopic parameters (mass, momentum, angular momentum, charge) are isometric to each other. 
 This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
-As a result, the Hilbert space of superposed classical geometries has far less dimensions than necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
+As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than are necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
 Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix; therefore such modification of Statement Three alone is insufficient to resolve the paradox.
@@
 In Sec.\ref{sec-BlackHole}, we apply the self-consistency check to the propagation of Hawking quanta in a close analogy to Feynman's analysis. 
-The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruins its subsystem unitarity. 
+The classical geometry plays the role of the double-slit, a background that can potentially entangle with the Hawking quanta wavefunction and ruin its subsystem unitarity. 
 We then assume that the unknown quantum nature of geometry can be parametrize by a classical uncertainty with an unknown but fixed, gauge-invariant size. 
@@
 When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
-When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$
-Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
+When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$,
+instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
 $P_i = \langle \phi_i | \phi_i \rangle$ and $P_{12} = (\langle \phi_1|+\langle \phi_2| ) (|\phi_1\rangle + | \phi_2 \rangle)=P_1 + P_2 + 2{\rm Re}\langle\phi_1|\phi_2\rangle$.
@@
 The top figure shows the behaviour one would expect of classical particles going through one slit or the other.
-The bottom figure shows the behaviour of classical waves creating an interference patter.
+The bottom figure shows the behaviour of classical waves creating an interference pattern.
 Screen one shows the signal that one would see in each scenario (i.e classical particles or waves) if only one slit was open.
@@
 Since soft gravitons lead to real physical changes in the geometry that can be seen in memory effects \cite{Wei65,HeLys14}, an IR ambiguity signals our ignorance on how these geometric changes enter QFT.
-Thus a direct graviton scattering calculation cannot be the full extend of a self-consistency check, and it is reasonable for our method to give extra constraints on the reliability of local QFT.
+Thus a direct graviton scattering calculation cannot be the full extent of a self-consistency check, and it is reasonable for our method to give extra constraints on the reliability of local QFT.
 
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx
-- \sigma \Delta l \left(\frac{2M}{l}\right)^2~, \ \ \ \ {\rm \bf XXX \ check \ coefficients}
-\label{eq-NearHorizon}
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
 \end{equation}
-where $l$ is the proper distance between $r_1$ and the horizon and $\Delta l$ is the proper distance between the two shells. 
-We can see that in addition to the same gauge-invariant quantity in Minkowski space
-\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\Delta l$.}, 
-there is an extra factor of $(2M/l)^2$ which diverges as the shell approaches the horizon.
-
-The small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT. 
+where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
+We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
+\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}.
+We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} = -1$, which is the largest possible effect in the arrival times of two geodesics.
+However, the small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT.
 After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
@@
 By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
-However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and diverges in the large black hole limit.
-Since the large black hole limit is supposed to be the best case scenario for information paradox, such a diverging uncertainty to decohere classical waves causes a strong doubt on the subsystem unitarity assumption in QFT.
+However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
+Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
 
@@
 Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
-It is not possible to do this analytically but it can be done numerically.
-We show the plots of $\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}}$ as functions of $M$.
 We can obtain analytic expressions for Eq (\ref{12}) in the limit that the shells are very close to the horizon and this is what is presented in the next section.

### 2016-10-12 Draft_BH_shells.tex
update bib

@@
 Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry.
-An abstract realization of this information-recovery process is recently demonstrated in \cite{OsuPag16}. 
-In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
-If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
-In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
-Thus the major objection to such picture is that the superpositons of classical geometries do not form a large enough Hilbert space to hold the required information.
-Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
-A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should persue this line of thoughts even further.
-
-Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
+More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertraslation\cite{GW_memory,HeLys14,KodPen16}.
+This naturally echoes the idea that the soft hairs \cite{HawPer16} encodes the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}.
 Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
 That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.
+
+\acknowledgements
+
+We thank XXX for discussions.
 

### 2016-10-26 Draft_BH_shells.tex
intro

@@
 \begin{abstract}
-The black hole information paradox presumes that local quantum field theory can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
+The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
 Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
@@
 Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
-Analogously, here we ask whether a unitary propagation of Hawking quanta, namely ignoring the entanglement with the geometry, also becomes arbitrarily reliable in the limit of a large black hole and asymptotic observers.
+We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
+We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole and asymptotic observers.
 We present curious results to suggest a negative answer, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
@@
 \section{Introduction and Summary}
+
+\subsection{Black Hole Information Paradox}
 
@@
 For such abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
-Here hidden simply means something that is ignorant to a na\"ive application of local QFT.
+Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
 The obvious candidate of such hidden system is the geometry.
@@
 Thus it is only natural to modify Statement Three.
+
+\subsection{Quantum Field Theory in Curved Spacetime}
 
@@
 If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
+\footnote{In the geometric limit, the shift in geodesics faithfully represents the shift in wave modes.
+Away from the geometric limit, the relation between them is more complicated, but one being large still implies that the other is, too.}
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 

### 2016-10-26 Draft_BH_shells.tex
minor changes

@@
 If we treat the superposition of different classical geometries as a quantum system, it may qualify as the hidden system that is responsible for the non-unitary propagation of Hawking quanta. 
-Unfortunately, such proposal can be defeated by counting entropy.
+Unfortunately, the early version of such proposal can be defeated by counting entropy.
 In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the amount of microscopic information carried by the black hole.
@@
 This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
-As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than are necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
+As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than what is necessary to carry the required amount of information.
+\footnote{We thank Raphael Bousso for private communication.}
 Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix; therefore such modification of Statement Three alone is insufficient to resolve the paradox.
@@
 If we just demand that it breaks down in order to resolve the information paradox, then there is no reason why this solution is preferred over modifying Statement One or Two. 
-We would like argue that the application of QFT to a unitary propagation from a near horizon mode to an asymptotic Hawking quantum is already self-inconsistent. 
+We would like to argue that there is a self-consistency check that we should apply to QFT in curved spacetime, for a reason that is totally independent from the information paradox.
+Applying such self-consistency check, we can show that a unitary propagation from a near horizon mode to an asymptotic Hawking quantum is already self-inconsistent. 
 Thus it is only natural to modify Statement Three.
 
-\subsection{Quantum Field Theory in Curved Spacetime}
+\subsection{Quantum Field Theory in Curved Spacetime Requires a Self-Consistency Check}
 
@@
 After such artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
-\footnote{Even a time-dependent Hamiltonian leads to an apparently unitary evolution under this assumption.
+%\footnote{Even a time-dependent Hamiltonian leads to an apparently unitary evolution under this assumption.
 That is obviously not a physical fact since a unitary subsystem should be determined by its own initial state, not co-determined by initial state plus an arbitrary time-dependence.}
@@
 In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
-We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from quantizing graviton.
+We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from perturbative calculations of gravitons.
 
@@
 \end{enumerate}
-Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
-However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
-Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
+%If we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. 
+%However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. 
+%Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
 \item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
@@
 A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
-After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.
+After the non-unitary propagation, such a informationless mode has to become an asymptotic Hawking quantum which carries the information to purify the rest of the Hawking radiation there.
+The exact detail of this process remains an enigma.
 
 Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry.
-More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertraslation\cite{GW_memory,HeLys14,KodPen16}.
-This naturally echoes the idea that the soft hairs \cite{HawPer16} encodes the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}.
+More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertranslation\cite{GW_memory,HeLys14,KodPen16}.
+This naturally echoes the idea that the soft hairs \cite{HawPer16} might encode the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}.
 Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.

### 2016-10-30 Draft_BH_shells.tex
Update Draft_BH_shells.tex

@@
 If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
-\footnote{In the geometric limit, the shift in geodesics faithfully represents the shift in wave modes.
-Away from the geometric limit, the relation between them is more complicated, but one being large still implies that the other is, too.}
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
@@
 \end{enumerate}
-%If we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example. 
-%However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that. 
-%Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
+Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
+However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
+Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
 \item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
@@
 The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$.
-Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $-\Delta M, \Delta M$ at $r_{1}, r_{2}$ respectively.
+Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
 The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
@@
 
-After some formal calculations in the {\bf Appendix}, we arrive at this simple expression:
+After some formal calculations in the appendix \ref{Dtime}, we arrive at this simple expression:
 \begin{equation}
 \frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = 
-\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M-\Delta M)}{r_2-2(M-\Delta M)}}-1\right)~,
+\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}-1\right)~,
 \label{eq-result}
@@
 
-As the first step, we set $M=0$ in Eq.~(\ref{eq-result}) to study its meaning in Minkowski space.
-Assuming that $|r_1-r_2| \equiv \Delta r \ll r_1$ and $\Delta M \ll r_1$, the leading order result becomes
+\textbf{XXX I-Sheng: Add a sentence about why we are using this limit?}
+
+We can expand Eq (\ref{eq-result}) in the limit that $r_1>> \Delta M$ and $r_1>> \Delta r = r_2 - r_1$
+
 \begin{equation}
-\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
-\equiv \sigma \Delta r~.	
-\label{eq-Mink}
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2}	\label{lim-result}
 \end{equation}
-This seems to be a reasonable answer. 
+
+This expression can be evaluated in three limits; 1) The Minkowski limit ($M=0$), 2) Far from horizon ($M <<r_1$), 3) Near horizon limit ($r_1<<M$).
+These limits have to be calculated using physical, local quantities, which are the local surface energy of the shell $\sigma$ and the proper distances.
+The calculations are performed in appendix \ref{finalEq} and the results are summarized below:
+
+\begin{equation}
+\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \begin{cases}
+ \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
+- 4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M<<r_1)	\\
+- 64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M>>r_1).
+\end{cases}	\label{fin-result}
+\end{equation}
+
+Lets try to interpret each of these terms.
+
+\begin{itemize}
+
+\item \textbf{Minkowski limit ($M=0$)}: This seems to be a reasonable answer. 
 First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
@@
 
-The na\"ive interpretation of Eq.~(\ref{eq-Mink}) is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
+The na\"ive interpretation of the $M=0$ result is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
 By our definition, that poses some threat to QFT in Minkowski space.
-We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect of Eq.~(\ref{eq-Mink}).
+We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect at $M=0$.
 One can imagine a simple subtraction by a counter term.
@@
 
-Next we study Eq.~(\ref{eq-result}) with an actual black hole. 
-When the double-shell is very far away from the black hole, $r_1\gg M$, it agrees with Eq.~(\ref{eq-Mink}) as expected. 
-The interesting thing here is that when this pair of geodesics originate near the horizon, the double-shell could also be somewhere near the horizon. 
-In that limit, Eq.~(\ref{eq-result}) can be approximated by
-\begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
-\end{equation}
-where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
-We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
-\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}.
+\item \textbf{Far from horizon ($M<<r_1$)}: This is a region where we expect to understand the physics well.
+Indeed the QFT we test here on earth can be considered an example of this limit.
+If we keep $l$ fixed and along with the gauge invariant $\sigma \Delta l$, we see that the effect grows with $M$.
+Of course, we cannot assume that this grows without bound since we have to maintain the $M<<r_1$ limit.
+It is interesting to note that similar behaviour is observed when this limit no longer holds and this is what we describe next.
+
+\item \textbf{Near horizon ($M>>r_1$)}: We can see that the same gauge-invariant quantity in Minkowski space from the $M=0$ limit appears here.
+We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} \rightarrow \infty$, which is the largest possible effect in the arrival times of two geodesics.
+However, the small $l$ limit may not be the best way to appreciate how this limit poses a threat to QFT.
+After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
+The best way to understand this limit is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
+By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
+However, the problem is that this effect grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
+Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
+
+\end{itemize}
+
+%In that limit, Eq.~(\ref{eq-result}) can be approximated by
+%\begin{equation}
+%	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
+%\end{equation}
+%where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
+%We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
+%\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}.
 We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} = -1$, which is the largest possible effect in the arrival times of two geodesics.
 However, the small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT.
-After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
-The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
-By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
-However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
-Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
+%After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
+%The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
+%By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
+%However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
+%Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
 
@@
 A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
-After the non-unitary propagation, such a informationless mode has to become an asymptotic Hawking quantum which carries the information to purify the rest of the Hawking radiation there.
-The exact detail of this process remains an enigma.
+After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.
 
 Since unitarity is lost to the local geometric uncertainty, what restores information must be the interaction with the local geometry. 
-More precisely, the particular effect of local geometric uncertainty here is to create extra shifts between parallel null geodesics, which is reminiscent of memory effects or supertranslation\cite{GW_memory,HeLys14,KodPen16}.
-This naturally echoes the idea that the soft hairs \cite{HawPer16} might encode the black hole information and returns them to the Hawking radiation via an interaction that is beyond the na\"ive local QFT\cite{OsuPag16}.
+An abstract realization of this information-recovery process is recently demonstrated in \cite{OsuPag16}. 
+In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
+If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
+In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
+Thus the major objection to such picture is that the superpositions of classical geometries do not form a large enough Hilbert space to hold the required information.
+Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
+A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should pursue this line of thoughts even further.
+
+Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
 Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
@@
 
-\acknowledgements
-
-We thank XXX for discussions.
-
 \appendix
 
-\section{Calculation}
+\section{Calculation of proper time change}\label{Dtime}
+
+\subsection{Background spacetime - no shell}
 
@@
 
-\subsubsection{Perturbed spacetime - double shell}
+\subsection{Perturbed spacetime - double shell}
 
-Now we introduce two shells of matter with equal and opposite ADM mass, $-\Delta M$ and $\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
+Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
 We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells.
 In this case the particle's move through two different spacetime regions.
-Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M-\Delta M$ as shown in the top part of figure \ref{fig-setup}.
+Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
 \\
@@
 \begin{equation}
-	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M - \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
+	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M + \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
 \end{equation}
@@
 \begin{equation}
-	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M- \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
+	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M + \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
 \end{equation}
 
-Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M - \Delta M)} \right) \right)^\frac{1}{2}$.
+Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M + \Delta M)} \right) \right)^\frac{1}{2}$.
 Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away.
@@
 \begin{equation}
-	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M-\Delta M)}{r_2 - 2(M-\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
-\end{equation}
-
-This expression is exact in the limit that the observer is far away.
-By expressing the distances from the horizon as, $r_1  =  2M + \epsilon,  r_2  =  2M + \epsilon + \delta \epsilon$, we can write Eq (\ref{10}) as
-
-\begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = \left( \left( \frac{\epsilon + \delta \epsilon}{\epsilon} \right)^\frac{1}{2} \left( \frac{\epsilon + 2 \Delta M}{\epsilon + \delta \epsilon + 2\Delta M} \right)^\frac{1}{2} - 1\right).
-\label{12}
+	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M+\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
 \end{equation}
@@
 This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect.
-More interestingly we see that there is no $M$ dependence in this equation.
-This suggests the effect is present in flat space as well.
-One may interpret this effect as being a phase shift between the photons as the travel through two different gravitational potential wells.
-Before jumping to any conclusions, however, we should convert the coordinate quantities in Eq (\ref{12}) into physical quantities.
+
+\subsection{Leading order expansion limit}
+
+By assuming $r_1>> \Delta r \equiv r_2 - r_1$ and $r_1>> \Delta M$ we can expand Eq (\ref{eq-result}), to leading order in small quantities,
+
+\begin{eqnarray}
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} & = & \left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1	\nonumber	\\
+	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 \right) \left( 1 + \frac{\Delta M}{r_1 - 2M} - \frac{1}{2} \left(\frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r+ 2 \Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) - 1	\nonumber	\\
+	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r + 2 \Delta M}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r + 2\Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) -1 \nonumber	\\
+	& = & - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 - \frac{1}{4} \frac{( \Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} + \frac{3}{8} \frac{(\Delta r+ 2 \Delta M)^2}{(r_1 - 2M)^2} 	\nonumber	\\
+	& = & \frac{\Delta M \Delta r}{(r_1 - 2M)^2}.
+\end{eqnarray}
 
@@
 
-\subsection{Defining local quantities}
+\section{Deriving Eq (\ref{fin-result})}\label{finalEq}
 
-\subsubsection{Energy of shell}
+The first step in this derivation is write down the physical, local, quantities needed to replace $\Delta M, r_1$ and $\Delta r$.
+The natural thing to replace $\Delta M$ is the surface stress energy, $\sigma$, of the shell.
+This is given by the $tt$ component of the surface stress energy tensor $S_{ab}$ given by the IJC.
 
-There is a natural choice of what physical quantity we should use to replace $\Delta M$ with and that is the $tt$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC
+%As the first step, we set $M=0$ in Eq.~(\ref{lim-result}) to study its meaning in Minkowski space,
+%
+%\begin{equation}
+%\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
+%\equiv \sigma \Delta r~.	
+%\label{eq-Mink}
+%\end{equation}
+%
+%Next we study Eq.~(\ref{lim-result}) with an actual black hole. 
+%Before we perform any analysis with a black hole it is important to convert the coordinate quantities in Eq (\ref{lim-result}) to physical quantities.
+We implicitly did this in the Minkowski limit; the variables in Eq (\ref{eq-Mink}) indeed represent the physical surface energy of the shell and the proper distance to it.
+In the case of a black hole we have to be more careful.
+The natural quantity to use for the local surface energy of the shell is the time component of the surface stress energy term, $S_{ab}$, given by the IJC
 
 \begin{equation}
-	S^a_b =  [K^a_b] - [K]h^a_b
+	S^a_b = [K^a_b] - [K]h^a_b,
 \end{equation}
 
-where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics.
-%
-%We can define the induced metrics for constant $r$ values; for region $I$ it is 
+where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric, $h^{ab}$, we are using. $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
+We can define the induced metrics for constant $r$ values; for region $I$ it is
+
+\begin{equation}
+	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+\end{equation}
+
+Analogously we have the metric corresponding to mass $M' = M+ \Delta M$ in region $II$
+
+\begin{equation}
+	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+\end{equation}
+
+We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
+Therefore it is easy to find a relation between the two time coordinates
+
+\begin{equation}
+	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
+\end{equation}
+
+Using this, we calculate the extrinsic curvature components
+
+\begin{eqnarray}
+	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
+	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
+	= (K^\phi_\phi)^{(M)}	\label{16}
+\end{eqnarray}
+
+where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
+Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
+ The time component of the surface stress energy tensor $S^0_0$ is
+
+\begin{equation}
+	\sigma = S^0_0 = \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2(M+\Delta M)}{r_1} \right)^\frac{1}{2} \right).
+\end{equation}
+
+This expression represents a small change in the mass and thus can be written as
+
+\begin{eqnarray}
+	\sigma & = & \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M. \nonumber	\\
+	& = &  \frac{\Delta M}{4 \pi r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}}.	\label{sig-Dm}
+\end{eqnarray}
+
+Next we need to replace the coordinate distance $\Delta r$ with the proper distance $\Delta l$ and the relation between them is given by
+
+\begin{equation}
+	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
+\end{equation}
+
+This can be integrated to give the proper distance, $l$, between the inner shell and the horizon
+
+\begin{eqnarray}
+	l & = & \int^{r_1}_{2M} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}} dr	\nonumber	\\
+	& = & \sqrt{(r_1 - 2M)r_1} + M \log \left( \frac{ r_1 - M + \sqrt{(r_1 - 2M)r_1}}{M} \right)	\label{l-r}
+\end{eqnarray}
+
+\subsection{Minkowski limit ($M=0$)}
+
+In the Minkowski limit we set $M=0$ in Eq (\ref{lim-result}) and put in the physical quantities from Eqs (\ref{sig-Dm}, \ref{Dl-Dr}, \ref{l-r}) to get
+
+\begin{equation}
+	\frac{\delta t_0 - \bar{t_0}}{\delta t_0} = \frac{\Delta M \Delta l}{l^2} = \sigma \Delta l.
+\end{equation}
+
+\subsection{Far from horizon limit ($M<<r_1$)}
+
+In this limit Eq (\ref{l-r}) can be expanded to first order to give
+
+\begin{equation}
+	l = r_1 - 2M - M \ln \left( \frac{r_1 - 2M}{M} \right) \Rightarrow r_1 - 2M = l - M \ln \left( \frac{l}{M} \right)	\label{l-r1}.
+\end{equation}
+
+Where in the last step we have used $x = y + \ln (y) \Rightarrow y = x - \ln(x)$ to leading order when $x \approx y$.
+We can substitute this, along with Eqs (\ref{sig-Dm}, \ref{Dl-Dr}) into Eq (\ref{lim-result}) to get
+
+\begin{eqnarray}
+	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = & 4 \pi \sigma \frac{r^2}{(r_1 - 2M)^2} \left( 1 - \frac{2M}{r_1} \right)^{\frac{1}{2}} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2}  \nonumber	\\
+	& = & 4 \pi \sigma \Delta l \left( 1  + \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \frac{2M}{r_1} \right)	\nonumber	\\
+	& = & 4 \pi \sigma \dDelta l \left( 1 + \frac{2M}{l} \right) + \mathcal{O}(l^{-2})
+\end{eqnarray}
+
+\subsection{Near horizon ($M>>r_1$)}
+
+in this limit the coordinate distance $r_1$ and proper distance $l$ are related by
+
+\begin{equation}
+	r_1 = \frac{l^2}{8M} + 2M
+\end{equation}
+
+Again, we substitute this expression along with Eqs (\ref{sig-Dm}, \ref{Dl-Dr}) into Eq (\ref{lim-result}) to get
+
+\begin{eqnarray}
+	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = &  4 \pi \sigma \delta l \left( 1+ \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \left( 1 + \frac{r_1 - 2M}{2M} \right)^{-1} \right)	\nonumber	\\
+	& =& 4 \pi \sigma \delta l \left( \frac{2M}{r_1 - 2M}\right)^2 \left( \frac{r_1 - 2M}{2M}  + \mathcal{O}(M^{-2}) \right)	\nonumber	\\
+	& = & 64 \pi \sigma \delta l \frac{M^2}{l^2}
+\end{eqnarray}
+
+%There is a natural choice of what physical quantity we should use to replace $\Delta M$ with and that is the $tt$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC
 %
 %\begin{equation}
-%	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+%	S^a_b =  [K^a_b] - [K]h^a_b
 %\end{equation}
 %
-%Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
+%where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics.
+%%
+%%We can define the induced metrics for constant $r$ values; for region $I$ it is 
+%%
+%%\begin{equation}
+%%	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+%%\end{equation}
+%%
+%%Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
+%%
+%%\begin{equation}
+%%	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+%%\end{equation}
+%%
+%%We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
+Therefore it is easy to find a relation between the two time coordinates
+%%
+%%\begin{equation}
+%%	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
+%%\end{equation}
+%%
+%%Using this, we calculate the extrinsic curvature components
+%%
+%%\begin{eqnarray}
+%%	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
+%%	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
+%%	= (K^\phi_\phi)^{(M)}	\label{16}
+%%\end{eqnarray}
+%%
+%%where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
+Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
+%
+%The $tt$ component of the surface stress energy tensor is
 %
 %\begin{equation}
-%	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+%	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
 %\end{equation}
-%
-%We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
-Therefore it is easy to find a relation between the two time coordinates
-%
-%\begin{equation}
-%	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
-%\end{equation}
-%
-%Using this, we calculate the extrinsic curvature components
-%
-%\begin{eqnarray}
-%	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
-%	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
-%	= (K^\phi_\phi)^{(M)}	\label{16}
-%\end{eqnarray}
-%
-%where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
-Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
-
-The $tt$ component of the surface stress energy tensor is
-
-\begin{equation}
-	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
-\end{equation}
 
@@
 
-\subsubsection{Proper distances}
-
-The proper length $l$ between the horizon and shell is,
-
-\begin{equation}
-	l =  (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
-\end{equation}
-
-Similarly, the proper distance between the two shells, $\delta l$, is given by
-
-\begin{equation}
-	\delta l = (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
-\end{equation}
-
-Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
+%\subsubsection{Deriving Eq (\ref{fin-result})}
+%
+%The proper length $l$ between the horizon and shell is,
+%
+%\begin{equation}
+%	l =  (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
+%\end{equation}
+%
+%Similarly, the proper distance between the two shells, $\delta l$, is given by
+%
+%\begin{equation}
+%	\delta l = (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
+%\end{equation}
+%	
+%Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
 We can obtain analytic expressions for Eq (\ref{12}) in the limit that the shells are very close to the horizon and this is what is presented in the next section.
-
-\subsection{Near horizon limit}
-
-In the near horizon limit we assume $\epsilon<< 2M$ and furthermore assume that the perturbations $\Delta M, \delta \epsilon$ are much smaller than $\epsilon$.
-Under these assumptions Eq (\ref{12}), to leading order in small quantities, becomes
-
-\begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = - \frac{\Delta M \delta \epsilon}{\epsilon^2}
-\end{equation}
-
-and the conversion to proper quantities from Eqs (\ref{sig}, \ref{20}, \ref{21}) gives, to leading order,
-
-\begin{equation}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.
-\end{equation}
-
-%to leading order this reduces to 
+%
+%
+%
+%%to leading order this reduces to 
 %

### 2016-10-31 Draft_BH_shells.tex
restoring wrong removal
restore acknowledgments and some other minor changes

@@
-\documentclass[aps,showpacs,twocolumn,floats,prd,superscriptaddress,nofootinbib]{revtex4-1} 
+\documentclass[aps,showpacs,onecolumn,floats,prd,superscriptaddress,nofootinbib]{revtex4-1} 
 \usepackage{graphicx,amsmath,amssymb,amstext}
@@
 
-\title{A self-consistency check for unitary propagation of Hawking quanta}
+\title{A self-consistency check for unitary Hawking radiation}
 
@@
 \maketitle
-
-\onecolumngrid
 
@@
 We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
-If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
+The change of distance (arrival time difference) between these two geodesics qualitatively represent the change a mode function will have.
+As such change gets large, we should lose faith on the apparent unitarity in the QFT calculation.
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
@@
 \end{enumerate}
-Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
+Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validity of learning a general lesson from a special example.
 However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
@@
 \item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
-In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
+In our case, we will see that even in Minkowski space, geometric uncertainty already leads to an in-principle-finite change between the two null geodesics.
 We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
-Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
+Our surprising result is that in the black hole case, we get an infinitely larger effects than in Minkowski space, which is difficult to blame on the usual divergence of QFT.
 \end{itemize}
@@
 Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
-We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
+We then introduce a geometric uncertainty as two shells of zero total ADM mass. 
 Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
@@
 
+\acknowledgments
+
+We thank XXX for discussions. We are supported by XXX fundings.
+
 \appendix
 
-\section{Calculation of proper time change}\label{Dtime}
+\section{Calculation of proper time change}
+\label{Dtime}
 
@@
 \begin{eqnarray}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} & = & \left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1	\nonumber	\\
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} & = & 
+	\left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1 \right)	\nonumber	\\
 	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 \right) \left( 1 + \frac{\Delta M}{r_1 - 2M} - \frac{1}{2} \left(\frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r+ 2 \Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) - 1	\nonumber	\\
 	%& = & \left( 1 + \frac{1}{2} \frac{\Delta r + 2 \Delta M}{r_1 - 2M} - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 \right) \left( 1 - \frac{1}{2} \frac{\Delta r + 2\Delta M}{r_1 - 2M} + \frac{3}{8} \frac{(\Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} \right) -1 \nonumber	\\
-	& = & - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + \frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - \frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 - \frac{1}{4} \frac{( \Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} + \frac{3}{8} \frac{(\Delta r+ 2 \Delta M)^2}{(r_1 - 2M)^2} 	\nonumber	\\
+	& = & - \frac{1}{8} \left( \frac{\Delta r}{r_1 - 2M} \right)^2 + 
+	\frac{1}{2} \frac{\Delta r \Delta M}{(r_1 - 2M)^2} - 
+	\frac{1}{2} \left( \frac{\Delta M}{r_1 - 2M} \right)^2 - 
+	\frac{1}{4} \frac{( \Delta r + 2 \Delta M)^2}{(r_1 - 2M)^2} + 
+	\frac{3}{8} \frac{(\Delta r+ 2 \Delta M)^2}{(r_1 - 2M)^2} 	\nonumber	\\
 	& = & \frac{\Delta M \Delta r}{(r_1 - 2M)^2}.
@@
 \section{Deriving Eq (\ref{fin-result})}\label{finalEq}
+\label{finalEq}
 
@@
 	& = & 4 \pi \sigma \Delta l \left( 1  + \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \frac{2M}{r_1} \right)	\nonumber	\\
-	& = & 4 \pi \sigma \dDelta l \left( 1 + \frac{2M}{l} \right) + \mathcal{O}(l^{-2})
+	& = & 4 \pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) + \mathcal{O}(l^{-2})
 \end{eqnarray}

### 2016-10-31 Draft_BH_shells.tex
some more minor changes
punctuations, line/paragraph breaking in the appendix

@@
 
-A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric
-
+A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric,
 \begin{equation}
-	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
+	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}~,
 \end{equation}
-
 where we are working with units in which $G = c = 1$.
@@
 We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}).
-By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation
 
+Confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation,
 \begin{equation}
-	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
+	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)~,	
+	\label{3}
 \end{equation}
-
 where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2. 
-
 \begin{equation}
-	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
+	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)~.	\label{4}
 \end{equation}
-
 Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that
-
 \begin{equation}
-	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
+	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}~.
 \end{equation}
-
 Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.
@@
 Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
-\\
-\\
+
 As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$.

### 2016-10-31 Draft_BH_shells.tex
minor changes

@@
 We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
-Our surprising result is that in the black hole case, we get an infinitely larger effects than in Minkowski space, which is difficult to blame on the usual divergence of QFT.
+Our surprising result is that in the black hole case, we get an arbitrarily larger effects than in Minkowski space, which is difficult to blame on the usual divergence of QFT.
 \end{itemize}

### 2016-11-01 Draft_BH_shells.tex
Changes from today

--- 2016-10-31 Draft_BH_shells.tex
@@
 
-\title{A self-consistency check for unitary Hawking radiation}
+\title{A self-consistency check for unitary propagation of Hawking quanta}
 
@@
 
-\author{I-Sheng Yang}
+\author{I-Sheng Yang}s
 
@@
 We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
-The change of distance (arrival time difference) between these two geodesics qualitatively represent the change a mode function will have.
-As such change gets large, we should lose faith on the apparent unitarity in the QFT calculation.
+If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
@@
 \end{enumerate}
-Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validity of learning a general lesson from a special example.
+Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
 However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
@@
 \item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
-In our case, we will see that even in Minkowski space, geometric uncertainty already leads to an in-principle-finite change between the two null geodesics.
+In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
 We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
-Our surprising result is that in the black hole case, we get an infinitely larger effects than in Minkowski space, which is difficult to blame on the usual divergence of QFT.
+Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
 \end{itemize}
@@
 Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
-We then introduce a geometric uncertainty as two shells of zero total ADM mass. 
+We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
 Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
@@
 Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
-The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M-\Delta M$.}
+The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$.}
 \label{fig-setup}
@@
 \begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2}	\label{lim-result}
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{rr}^{2}	\label{lim-result}
 \end{equation}
 
+In fact, this expression can be written in general (see Eq (\ref{Eq-mink}) in the appendix for derivation) in terms of physical, local quantities, which are the local surface energy of the shell $\sigma$ and the proper distances,
+
+\begin{equation}
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = 4 \pi \sigma \Delta l g_{rr}
+\end{equation}
+
+where $g_{rr}$ is the radial component of the Schwasrchild metric.
 This expression can be evaluated in three limits; 1) The Minkowski limit ($M=0$), 2) Far from horizon ($M <<r_1$), 3) Near horizon limit ($r_1<<M$).
-These limits have to be calculated using physical, local quantities, which are the local surface energy of the shell $\sigma$ and the proper distances.
 The calculations are performed in appendix \ref{finalEq} and the results are summarized below:
@@
 \frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \begin{cases}
- \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
-- 4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M<<r_1)	\\
-- 64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M>>r_1).
+ 4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
+4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M<<r_1)	\\
+64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M>>r_1).
 \end{cases}	\label{fin-result}
@@
 
-Many existing results of QFT in curved/dynamical geometries are about particle numbers, such as the particle-production calculation following a Bogoliugov transformation. 
+Many existing results of QFT in curved/dynamical geometries are about particle numbers, such as the particle-production calculation following a Bogoliubov transformation. 
 As an example, one can easily see that
@@
 That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.
-
-\acknowledgments
-
-We thank XXX for discussions. We are supported by XXX fundings.
 
@@
 
-\section{Deriving Eq (\ref{fin-result})}\label{finalEq}
+%\section{Deriving Eq (\ref{fin-result})}\label{finalEq}
+\section{Whatever section name it was}
 \label{finalEq}
@@
 \begin{equation}
-	\frac{\delta t_0 - \bar{t_0}}{\delta t_0} = \frac{\Delta M \Delta l}{l^2} = \sigma \Delta l.
+	\frac{\delta t_0 - \bar{t_0}}{\delta t_0} = \frac{\Delta M \Delta l}{l^2} = 4 \pi \sigma \Delta l.	\label{Eq-mink}
 \end{equation}
 
-\subsection{Far from horizon limit ($M<<r_1$)}
-
-In this limit Eq (\ref{l-r}) can be expanded to first order to give
+Very far away from the horizon, we expect a small deviation in Eq (\ref{Eq-mink}) from the Minkowski result as we know that the Schwarzschild geometry is asymptotically flat.
+By assuming $r_1>>M$ we  expanded Eq \ref{l-r} to first order to give
 
@@
 \begin{eqnarray}
-	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = & 4 \pi \sigma \frac{r^2}{(r_1 - 2M)^2} \left( 1 - \frac{2M}{r_1} \right)^{\frac{1}{2}} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2}  \nonumber	\\
-	& = & 4 \pi \sigma \Delta l \left( 1  + \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \frac{2M}{r_1} \right)	\nonumber	\\
-	& = & 4 \pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) + \mathcal{O}(l^{-2})
+	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = & 4 \pi \sigma \frac{r_1^2}{(r_1 - 2M)^2} \left( 1 - \frac{2M}{r_1} \right)^{\frac{1}{2}} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2}  \nonumber	\\
+	& = & 4 \pi \sigma \Delta l \left( 1 - \frac{2M}{r_1} \right)^{-1} = 4 \pi \sigma \Delta l g_{rr}	\label{gen-result}
 \end{eqnarray}
+
+Note that this is actually a general result so far in terms of the coordinate distance $r_1$. We can expand this to leading order now by assuming $2M/r_1 <<1$,
+
+\begin{equation}
+	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} = 4 \pi \sigma \Delta l \left( 1 + \frac{2M}{r_1} \right) 
+\end{equation}
 
@@
 
-in this limit the coordinate distance $r_1$ and proper distance $l$ are related by
+In this limit the coordinate distance $r_1$ and proper distance $l$ are related by
 
@@
 	& =& 4 \pi \sigma \delta l \left( \frac{2M}{r_1 - 2M}\right)^2 \left( \frac{r_1 - 2M}{2M}  + \mathcal{O}(M^{-2}) \right)	\nonumber	\\
-	& = & 64 \pi \sigma \delta l \frac{M^2}{l^2}
+	& = & 64 \pi \sigma \delta l \frac{M^2}{l^2} + \mathcal{O}(r^{-2})
 \end{eqnarray}

### 2016-11-01 Draft_BH_shells.tex
Changes from today
fixed typo
title update

@@
 
-\author{I-Sheng Yang}s
+\author{I-Sheng Yang}
 
@@
 
-If we go back to the basic of quantum field theory, there is a natural generalization of this new rule. 
+If we go back to the basic of quantum field theory, there is a natural description of this new rule. 
 As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state. 
 Any method to measure such quantum state assumes the knowledge of the classical mode function. 
-If the geometric uncertainty leads to an order one change in the classical mode function, then there is no practical way to reliably measure its quantum state. 
+If the geometric uncertainty leads to a significant uncertainty in the classical mode function, then there is no practical way to reliably measure its quantum state. 
 We advocate that this is not only a practicality about measuring the quantum state, but it directly tells us that the quantum state loses its unitarity. 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tb]
 \begin{center}.

### 2016-11-01 Draft_BH_shells.tex
updating

@@
 firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
-various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16} or causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}
-\footnote{Independent of the particular realization, causal-patch complementarity basically claims that QFT breaks down if one applies it to a region that does not fit into any observer's causal patch.}
-modifies Statement Three.
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modifies Statement Three.
+\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
 
@@
 That is because changes in the mapping geodesics are measurable memory effects, and a consistent physical theory must be able to distinguish them.
-This realization dramatically increases the number of different states encoded in classical geometries.
+This realization may dramatically increase the number of different states encoded in classical geometries.
 A tentative counting of state on a black hole horizon yields exactly the required number such that a modification to Statement Three can indeed resolve the paradox \cite{HawPer16}.
@@
 We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
-If this change is comparable to the wavelength, then the mode function of this wavelength loses classical coherence.
+As this change increases, one should gradually lose faith in the unitary propagation of such mode, since it becomes increasingly difficult to experimentally verify.
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
@@
 We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
-Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on renormalization.
+Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on the usual divergence of QFT.
 \end{itemize}
@@
 This represents one wavelength of the mode function of an asymptotic Hawking quantum.
-We then back-track two null geodesics from these two points back to two points near the horizon, at $r_A$ with $(r_A-2M)\ll 2M$.
+We then back-track two null geodesics from these two points back to two points near the horizon, at $r_e$ with $(r_e-2M)\ll 2M$.
 Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
@@
 
-After some formal calculations in the appendix \ref{Dtime}, we arrive at this simple expression:
+Note that we have assumed two stationary and spherically symmetric shells to simplify the calculation, but that is not the actual physical picture.
+There is no reason why vacuum fluctuation suddenly manifests two complete shells together to surround the black hole, and holding them at a fixed location will require unphysically large pressure if they are close to the horizon.
+As it will become clear later, our result only cares about the local energy density of two small pieces of shells at the ``location and time'' where the pair of null rays actually pass through.
+It does not care about whether the whole shell exists or not, and the pressure does not directly affect the answer.
+Our result is also invariant under radial boosts, thus it does not matter how the shells move before and after the crossing, or whether the shells are actually stationary.
+
+After some formal calculations in Appendix \ref{Dtime}, we arrive at this simple expression:
 \begin{equation}
@@
 
-\textbf{XXX I-Sheng: Add a sentence about why we are using this limit?}
+In the entire calculation, we will stay in the regime that $r_1, 2M, (r_1-2M) \gg \Delta M, \Delta r$, where $\Delta r \equiv(r_2-r_1)$. 
+This guarantees that the geometric fluctuation is small, as it only affects a small region $\Delta r$, and the change in the metric $\Delta g_{\mu\nu}/g_{\mu\nu}$ is small in the affected region.
+Under this assumption, we can expand Eq (\ref{eq-result}) to get 
+\begin{equation}
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}~.
+		\label{lim-result}
+\end{equation}
+Here $g_{tt}=(1-2M/r_1)$ is the radial component of the metric in the background geometry, evaluated at the location where the null rays pass through the geometric uncertainty.
 
-We can expand Eq (\ref{eq-result}) in the limit that $r_1>> \Delta M$ and $r_1>> \Delta r = r_2 - r_1$
+It is more enlightening to write this expression in the local physical quantities (see Appendix \ref{finalEq} for derivation).
+Let $\sigma$ be the energy density of the shell in its rest frame, and $\Delta l$ be the physical distance between the shells in that frame, we get
+\begin{equation}
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = 4 \pi \sigma \Delta l g_{tt}^{-1}~.
+	\label{eq-inv}
+\end{equation}
+Here we can see that the effect is due to the local energy density which the null rays pass through.
+Also, the combination $(\sigma\Delta l)$ is invariant under radial boosts, thus Eq.~(\ref{eq-inv}) does not care about whether the shells are actually at rest, nor in which frame we calculate it.
 
-\begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{rr}^{2}	\label{lim-result}
-\end{equation}
-
-In fact, this expression can be written in general (see Eq (\ref{Eq-mink}) in the appendix for derivation) in terms of physical, local quantities, which are the local surface energy of the shell $\sigma$ and the proper distances,
-
-\begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = 4 \pi \sigma \Delta l g_{rr}
-\end{equation}
-
-where $g_{rr}$ is the radial component of the Schwasrchild metric.
-This expression can be evaluated in three limits; 1) The Minkowski limit ($M=0$), 2) Far from horizon ($M <<r_1$), 3) Near horizon limit ($r_1<<M$).
-The calculations are performed in appendix \ref{finalEq} and the results are summarized below:
+In order to appreciate the effect of such geometric uncertainty near the horizon of a large black hole (which is usually considered the ideal situation to formulate the information paradox), we evaluate Eq.~(\ref{eq-inv}) in three regimes;
+1) The Minkowski limit: $M=0$; 
+2) Small black holes / far from horizon: $M \ll r_1$; 
+3) Large black holes / near horizon: $r_1\gg M$. 
+Instead of using the coordinate $r_1$, we will express the answer with the physical distance $l$ between the horizon and the shells. 
+The relation between $r$ and $l$ can also be found in Appendix \ref{finalEq}. 
+We will hold $l$, $\Delta l$ and $\sigma$ fixed while the black hole mass is being varied.
 
@@
  4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
-4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M<<r_1)	\\
-64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M>>r_1).
+4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M \ll r_1)	\\
+64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M \ll r_1).
 \end{cases}	\label{fin-result}
@@
 
-Lets try to interpret each of these terms.
-
 \begin{itemize}
 
-\item \textbf{Minkowski limit ($M=0$)}: This seems to be a reasonable answer. 
-First of all, it is quite unlikely that the entire shell of mass $\Delta M$ fluctuates out of vacuum.
-It is reasonable that any change to the null geodesics is about a local energy density of the particular piece of shell they happen to pass through.
-Secondly, this result is gauge invariant. For an observer at rest, $\sigma$ is the local energy density and $\Delta r$ is the proper distance. 
-For a boosted observer, $\sigma$ increases by a boost factor while $\Delta r$ contracts by the same factor.
-We take it as a good sign that other forms of geometric uncertainty can also be parametrize by a similar, gauge invariant quantity.
-
+\item \textbf{Minkowski limit ($M=0$)}: 
 The na\"ive interpretation of the $M=0$ result is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
@@
 
-\item \textbf{Far from horizon ($M<<r_1$)}: This is a region where we expect to understand the physics well.
-Indeed the QFT we test here on earth can be considered an example of this limit.
-If we keep $l$ fixed and along with the gauge invariant $\sigma \Delta l$, we see that the effect grows with $M$.
-Of course, we cannot assume that this grows without bound since we have to maintain the $M<<r_1$ limit.
-It is interesting to note that similar behaviour is observed when this limit no longer holds and this is what we describe next.
+\item \textbf{Far from horizon ($M \ll l$)}: 
+If we send signals from the Earth surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
+It starts to show a small deviation from the Minkowski result, but in the $M \ll r_1$ limit, it is almost indistinguishable.
 
-\item \textbf{Near horizon ($M>>r_1$)}: We can see that the same gauge-invariant quantity in Minkowski space from the $M=0$ limit appears here.
+\item \textbf{Near horizon ($M \gg l$)}: We can see that the same gauge-invariant quantity in Minkowski space from the $M=0$ limit appears here.
 We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} \rightarrow \infty$, which is the largest possible effect in the arrival times of two geodesics.
@@
 \end{itemize}
-
-%In that limit, Eq.~(\ref{eq-result}) can be approximated by
-%\begin{equation}
-%	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx \frac{l}{4M} \sqrt{\frac{1}{(6 \pi \delta l \sigma - 1)^\frac{2}{3} -1 }} - 1.	\label{eq-NearHorizon}
-%\end{equation}
-%where $l$ is the proper distance between $r_1$ and the horizon and $\delta l$ is the proper distance between the two shells. 
-%We can see that the same gauge-invariant quantity in Minkowski space from Eq. (\ref{eq-Mink}) appears in the denominator this time
-%\footnote{In Minkowski space, the radial coordinate is the proper distance, $\Delta r=\delta l$.}.
-We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} = -1$, which is the largest possible effect in the arrival times of two geodesics.
-However, the small $l$ limit may not be the best way to appreciate how Eq.~(\ref{eq-NearHorizon}) poses a threat to QFT.
-%After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
-%The best way to understand Eq.~(\ref{eq-NearHorizon}) is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
-%By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
-%However, the problem caused by Eq.~(\ref{eq-NearHorizon}) grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
-%Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
 
@@
 
-%\section{Deriving Eq (\ref{fin-result})}\label{finalEq}
-\section{Whatever section name it was}
+\section{Local physical quantities}
 \label{finalEq}
@@
 This is given by the $tt$ component of the surface stress energy tensor $S_{ab}$ given by the IJC.
-
-%As the first step, we set $M=0$ in Eq.~(\ref{lim-result}) to study its meaning in Minkowski space,
-%
-%\begin{equation}
-%\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} \approx - \frac{\Delta M}{r_1^2} \Delta r 
-%\equiv \sigma \Delta r~.	
-%\label{eq-Mink}
-%\end{equation}
-%
-%Next we study Eq.~(\ref{lim-result}) with an actual black hole. 
-%Before we perform any analysis with a black hole it is important to convert the coordinate quantities in Eq (\ref{lim-result}) to physical quantities.
-We implicitly did this in the Minkowski limit; the variables in Eq (\ref{eq-Mink}) indeed represent the physical surface energy of the shell and the proper distance to it.
-In the case of a black hole we have to be more careful.
-The natural quantity to use for the local surface energy of the shell is the time component of the surface stress energy term, $S_{ab}$, given by the IJC
 
@@
 
-%There is a natural choice of what physical quantity we should use to replace $\Delta M$ with and that is the $tt$ component of the surface stress energy tensor, $S_{ab}$, of the shell as computed by the IJC
-%
-%\begin{equation}
-%	S^a_b =  [K^a_b] - [K]h^a_b
-%\end{equation}
-%
-%where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric we are using, $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature taken with respect to the induced metric and the notation of square brackets represents the difference in a quantity in two different induced metrics.
-%%
-%%We can define the induced metrics for constant $r$ values; for region $I$ it is 
-%%
-%%\begin{equation}
-%%	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
-%%\end{equation}
-%%
-%%Analogously we have the metric corresponding to mass $M' = M- \Delta M$ in region $II$
-%%
-%%\begin{equation}
-%%	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
-%%\end{equation}
-%%
-%%We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
-Therefore it is easy to find a relation between the two time coordinates
-%%
-%%\begin{equation}
-%%	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
-%%\end{equation}
-%%
-%%Using this, we calculate the extrinsic curvature components
-%%
-%%\begin{eqnarray}
-%%	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
-%%	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
-%%	= (K^\phi_\phi)^{(M)}	\label{16}
-%%\end{eqnarray}
-%%
-%%where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
-Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
-%
-%The $tt$ component of the surface stress energy tensor is
-%
-%\begin{equation}
-%	\sigma = S^0_0 =  \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{sig}
-%\end{equation}
-
-%This represents the surface energy density, to convert it to the energy of the shell, $\mathcal{E}$, we multiply by the surface area of the shell which is $4 \pi r_1^2$
-%
-%\begin{equation}
-%	\mathcal{E} =  r_1 \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).	\label{19}
-%\end{equation}
-
-%Substituting in for $r_1 = 2M + \epsilon$, where $\Delta M<<\epsilon<<2M$ and expanding to leading order in small quantities, 
-%
-%\begin{equation}
-%	\mathcal{E} = \left( \frac{2M}{\epsilon} \right)^\frac{1}{2} \Delta M.
-%\end{equation}
-
-%
-%\subsubsection{Proper time between shells}
-%
-%We calculate the proper time between the two shells, $\tau_{12}$, as seen by an observer at the first shell\footnote{One could also calculate the proper length between the shells.}.
-This is done with a view to replace $\delta \epsilon$ by $\tau_{12}.
-%
-%\begin{eqnarray}
-%	\tau_{12} & = & \int^{t_2}_{t_1} \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} dt	\nonumber	\\
-%	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (t_2 - t_1)	\nonumber	\\
-%	& = & \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} (r_2 - r_1 + 2M' \ln \left( \frac{r_2 - 2M'}{r_1 - 2M'} \right) \right).	
-%\end{eqnarray}
-%
-%We substitute in for $r_1$ and $r_2$ from Eq (\ref{11'}) to give
-%
-%\begin{equation}
-%	\tau_{12} = \delta \epsilon \left( \frac{\epsilon}{2M} \right)^\frac{1}{2} \left( 1 + \frac{2M}{\epsilon} \right).
-%\end{equation}
-%
-
-%\subsubsection{Deriving Eq (\ref{fin-result})}
-%
-%The proper length $l$ between the horizon and shell is,
-%
-%\begin{equation}
-%	l =  (2M \epsilon)^\frac{1}{2}  + M \ln \left( \frac{M + \epsilon + (2M\epsilon)^\frac{1}{2}}{M} \right).	\label{20}
-%\end{equation}
-%
-%Similarly, the proper distance between the two shells, $\delta l$, is given by
-%
-%\begin{equation}
-%	\delta l = (2M'(\epsilon + \delta \epsilon))^{\frac{1}{2}} + M' \ln \left(\frac{M' + \epsilon + \delta \epsilon + (2M'(\epsilon +\delta \epsilon))^{\frac{1}{2}}}{M'} \right) - (2M'\epsilon)^\frac{1}{2} - M' \ln \left( \frac{M' + \epsilon + (2M' \epsilon)^\frac{1}{2}}{M'} \right)	\label{21}
-%\end{equation}
-%	
-%Eqs (\ref{sig}, \ref{20}, \ref{21}) can be used in Eq (\ref{12}) to replace $\Delta M, \epsilon, \delta \epsilon$ respectively by the appropriate physical quantities.
-We can obtain analytic expressions for Eq (\ref{12}) in the limit that the shells are very close to the horizon and this is what is presented in the next section.
-%
-%
-%
-%%to leading order this reduces to 
-%
-%\begin{equation}
-%	l = 2 (2 \epsilon M)^\frac{1}{2}.	\label{25}
-%\end{equation}
-%
-%We can further calculate $\delta l$, the distance between the two shells, from Eq (\ref{25})
-%
-%\begin{equation}
-%	\delta l = \frac{4 M \delta \epsilon}{l}.
-%\end{equation}
-
-%Using these local quantities to replace the coordinate quantities in Eq (\ref{11}) gives
-%
-%\begin{equation}
-%	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \frac{4 \mathcal{E} \delta l}{l^2}.	\label{24'}
-%\end{equation}
-%
-%We want to define the local energy density of the shell, $\sigma$, which is, in the near horizon limit, given by $\sim \frac{\mathcal{E}}{(2M)^2}$. Thus we can rewrite Eq (\ref{24'}) by, 
-%
-%\begin{equation}
-%	\frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta {\bar{\tau_0}}} = 4 \sigma \delta l \left( \frac{M}{l} \right)^2	\label{25'}
-%\end{equation}
-%
-%If we take $\sigma$ and $\delta l$ to be fixed (since they represent the fluctuations of the spacetime), we see that Eq (\ref{25'}) increases linearly with $M$.
-
 \bibliography{all_active}

### 2016-11-01 Draft_BH_shells.tex
main text done

@@
 Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
-We re-examine this assumption by establishing an analogy to Feynman's analysis of a double-slit experiment. 
+We establish an analogy to Feynman's analysis of a double-slit experiment. 
 Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
 We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
-We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole and asymptotic observers.
-We present curious results to suggest a negative answer, and we discuss how this is related to the information transfer from near-horizon geometry and the soft-hair proposal.
+We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
+We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT is related to the soft-hair-memory effect.
 \end{abstract}
@@
 firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
-various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modifies Statement Three.
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.
 \footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
@@
 
-In this paper, we still take another step that is complementary to the above progress. It is exciting to know that modifying Statement Three can in-principle resolve the paradox. 
+In this paper, we will take another step that is complementary to the above progress. It is exciting to know that modifying Statement Three can in-principle resolve the paradox. 
 However, it remains a great mystery of why should local QFT break down in low curvature regions. 
@@
 After such artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
-%\footnote{Even a time-dependent Hamiltonian leads to an apparently unitary evolution under this assumption.
-That is obviously not a physical fact since a unitary subsystem should be determined by its own initial state, not co-determined by initial state plus an arbitrary time-dependence.}
 However, such unitarity should not be taken as a physical fact unless one specifically checks the nature of interactions with the background.
@@
 
-It is more enlightening to write this expression in the local physical quantities (see Appendix \ref{finalEq} for derivation).
+It is more enlightening to write this expression in the local physical quantities (see Appendix \ref{finalEq} for derivations).
 Let $\sigma$ be the energy density of the shell in its rest frame, and $\Delta l$ be the physical distance between the shells in that frame, we get
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \begin{cases}
- 4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
-4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M \ll r_1)	\\
-64 \pi  \sigma \Delta l \frac{M^2}{l^2} & \ \ \ \ \ (M \ll r_1).
+\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0}  \begin{cases}
+= 4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
+\approx 4\pi \sigma \Delta l \left( 1 + \frac{2M}{l} \right) & \ \ \ \ \ (M \ll l)	\\
+\approx 4 \pi  \sigma \Delta l \frac{16M^2}{l^2} & \ \ \ \ \ (M \gg l).
 \end{cases}	\label{fin-result}
@@
 
-\item \textbf{Near horizon ($M \gg l$)}: We can see that the same gauge-invariant quantity in Minkowski space from the $M=0$ limit appears here.
-We see that taking the small $l$ limit with $\delta l \sigma$ fixed gives $\frac{\delta t_0 - \delta \hat{t_0}}{\delta t_0} \rightarrow \infty$, which is the largest possible effect in the arrival times of two geodesics.
-However, the small $l$ limit may not be the best way to appreciate how this limit poses a threat to QFT.
-After all, we do not expect QFT to hold for arbitrarily small distance anyway. 
-The best way to understand this limit is to fix $l$ at some scale that much longer than any scale that we expect UV problems. 
-By conventional knowledge, the effect of gravity near horizon gets arbitrarily weak as the black hole becomes large. 
-However, the problem is that this effect grows larger as the black hole becomes larger, and gives the maximum effect as the black hole mass becomes infinite.
-Since the large black hole limit is supposed to be the best case scenario for the information paradox and this is the regime that gives rise to maximum uncertainty to decohere classical waves, one is forced to have strong doubts about assuming subsystem unitarity in QFT.
+\item \textbf{Near horizon ($M \gg l$)}: 
+If we consider a region of size $l$ across the horizon of a large black hole $M\gg l$, QFT believes that such region is locally the same as empty Minkowski.
+As long as $l$ is much larger than the UV cut-off scale of the QFT, one would believe that modes in this region propagates out to become Hawking quanta, and QFT guarantees the unitarity of such process.
+Here we hold $\sigma\Delta l$ fixed at the same value of empty Minkowski space, we can see that the effect of geometric uncertainty gets arbitrarily larger than in the Minkowski space.
+Note that the absolute value of the effect cannot become arbitrarily large, since it is actually bounded at order one by the validity constraint of our calculation: $\Delta g_{\mu\nu} \ll g_{\mu\nu}$.
+However, seeing that it can be arbitrarily larger than the Minkowski result should be a sufficient reason to raise a reasonable doubt about the unitarity of the propagation process.
 
@@
 In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
-We have shown that the near-horizon geometry of a Schwarzschild black hole seems to fail such a check.
+We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
 As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
@@
 Thus we can still rely on QFT to calculate the values of other observables.
+For example, the particle number and energy spectrum of Hawking radiation can remain the same as the conventional result.
 
@@
 
-As far as we know, an observable that explicitly checks the subsystem unitarity of local QFT is the cosmological Bell inequality \cite{Mal15}. 
-One can apply our self-consistency check to such a model and update the prediction of whether a violation of Bell inequality is actually expected.
+As far as we know, an observable that explicitly checks the subsystem unitarity of local QFT during particle-production events is the cosmological Bell inequality \cite{Mal15}. 
+One might be able to apply a similar self-consistency check to such a model and update the prediction of whether a violation of Bell inequality is actually expected.
 
-\subsection{The information-transfer puzzle}
+\subsection{The information paradox}
 
-Showing the lack of unitarity in the propagation of Hawking quanta does not resolve all the problems. 
-Usually, one pictures a nonunitarity process as losing information. 
+While formulating the information paradox, it is customary to take the large black hole limit.
+Such limit allows us to identify modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
+For these modes, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
+This large black hole limit, which is effectively a near-Minkowski limit of a near horizon region, is the key argument to eliminate many na\"ive solutions to the information paradox.
+
+The main result in this paper shows that there is a competing effect which stops us from taking this convenient limit.
+The geometric uncertainty at distance $l$ from the horizon will only affect near-horizon modes of wavelength shorter than $l$.
+If we fix the wavelength of the relevant near-horizon modes and increase the black hole size, our result shows that the unitary propagation to asymptotic Hawking radiation becomes less and less trustworthy.
+Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.
+We think such competing nature is a good sign and will take us closer to the solution of information paradox.
+
+Let us assume that indeed the QFT-subsystem unitarity is lost during the propagation of Hawking quanta.
+This alone does not resolve all the problems. 
+Usually, one pictures a non-unitarity process as losing information. 
 In the context of black hole information, a Hawking quantum actually has to {\it recover} information. 
 A near-horizon mode starts from a maximally mixed (thermal) state with no information, since its partner is the interior mode that never comes out of the horizon. 
-After the nonunitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.
+After the non-unitarity propagation to become an asymptotic Hawking quantum, it has to carry information to purify the rest of the Hawking radiation there.
 
@@
 Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
+Two neighbouring null rays simply ``remember'' the geometric uncertainty they passed through.
+Na\"ively speaking, a propagating mode of a massless field should remember a similar effect. 
 Based on this picture, one may try to quantize the soft hairs and build a toy model that involves quantum interaction, therefore entanglement, between the soft hairs and the usual QFT modes.
 That would provide a complete picture that the loss of subsystem unitarity is really just entanglement with another subsystem which was originally (and illegitimately, as we argued) assumed as the classical background.
+
+\acknowledgments
+
+We thank XXX for discussions. We are supported by XXX.
 

### 2016-11-01 Draft_BH_shells.tex
minor
phrasing change

@@
 We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
-We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT is related to the soft-hair-memory effect.
+We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT might be related to the soft-hair-memory effect.
 \end{abstract}

### 2016-11-02 Draft_BH_shells.tex

--- 2016-11-01 Draft_BH_shells.tex
@@
 The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
-Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
+Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
 We establish an analogy to Feynman's analysis of a double-slit experiment. 
@@
 
-The black hole information paradox \cite{Haw76a} was sharpened to show a self-inconsistency among the following three widely-believed statements \cite{AMPS}
-\footnote{Different physicists may believe in some of those more strongly than the others, but very few would have argued against any single statement without the explicitly conflict in the information paradox.}:
+The black hole information paradox \cite{Haw76a} was sharpened to show a self-inconsistency among the following three widely-believed statements \cite{AMPS}\footnote{Different physicists may believe in some of those more strongly than the others, but very few would have argued against any single statement without the explicit conflict in the information paradox.}:
 \begin{itemize}
-\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer as a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
-\item {\bf General relativity:} The collapse-Schwarzschid geometry given by general relativity is a valid description to the spacetime everywhere except for near the singularity.
+\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer by a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
+\item {\bf General relativity:} The collapse-Schwarzschid geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
 Therefore, there is no drama while crossing the horizon.
@@
 firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
-various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.
-\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
 
@@
 In fact, we will argue that it is already problematic on its own. 
-In other words, {\bf the application of local QFT to a unitary propagation of Hawking quantum is not self-consistent. }
+In other words, {\bf the application of local QFT to unitary propagation of Hawking quanta is not self-consistent. }
 
@@
 This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
-As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than what is necessary to carry the required amount of information.
-\footnote{We thank Raphael Bousso for private communication.}
+As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than what is necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
 Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix; therefore such modification of Statement Three alone is insufficient to resolve the paradox.
@@
 We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
-By analogy to Feynman's analysis, this is a strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
+By analogy to Feynman's analysis, this is strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
 
@@
 Screen one shows the signal that one would see in each scenario (i.e classical particles or waves) if only one slit was open.
-If slit 1 was open we would see $P_1$ and see on.
+If slit 1 was open we would see $P_1$ and so on.
 Screen 2 shows the signal we see if both the silts are open in each scenario.}
@@
 
-If we go back to the basic of quantum field theory, there is a natural description of this new rule. 
+If we go back to the basics of quantum field theory, there is a natural description of this new rule. 
 As shown in Fig.\ref{fig-QFT}, QFT starts from solving a classical mode function, then quantizing its amplitude into a quantum state. 
@@
 In QFT, the background is the entire geometry, and there are infinitely many ways a geometry can be uncertain.
-For a full analogy to Feynman's analysis, not only we need to parametrize those uncertainties, we also need to choose the appropriate combination to hold fixed as we take a similar limit.
+For a full analogy to Feynman's analysis, not only do we need to parametrize those uncertainties, we also need to choose the appropriate combination to hold fixed as we take a similar limit.
 At this moment, we do not have a general formalism to setup such self-consistency check that can be applied to any general geometry. 
@@
 We consider only one particular form of $\Delta g_{\mu\nu}$ in this paper---back-reactions from the presence of extra matter of zero total energy. 
-It is simple to calculate and reflects the physcial intuition of vacuum pair fluctuation.
+It is simple to calculate and reflects the physical intuition of vacuum pair fluctuation.
 \item The value of $\Delta g_{\mu\nu}$ is gauge dependent. 
@@
 More concretely, our setup is shown in Fig.\ref{fig-setup}. 
-We start by choosing two points at some $r_0\gg M$ with a $\delta t_0\sim M$ coordinate time separation between them.
+We start by choosing two points at some $r_0\gg M$ with a $\delta \bar{t_0}\sim M$ coordinate time separation between them.
 This represents one wavelength of the mode function of an asymptotic Hawking quantum.
@@
 Only the process of propagation is affected.
-With the same two starting points near the horizon. we calculate the separation $\bar{\delta t_0}$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta t_0$.
+With the same two starting points near the horizon we calculate the separation $\delta t_0$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta \bar{t_0}$.
 
@@
 The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines.
-The bottom part is a general case of two Hawking photons coming from a distance $r_A$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
-The top part shows two Hawking photons coming from the same distance $r_A$ from a black hole of mass $M$.
+The bottom part is a general case of two Hawking photons coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
+The top part shows two Hawking photons coming from the same distance $r_e$ from a black hole of mass $M$.
 Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} = 
+\frac{\delta t_0 - \bar{\delta t_0}}{\delta \bar{t_0}} = 
 \left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}-1\right)~,
@@
 \begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}~.
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}~.
 		\label{lim-result}
 \end{equation}
-Here $g_{tt}=(1-2M/r_1)$ is the radial component of the metric in the background geometry, evaluated at the location where the null rays pass through the geometric uncertainty.
+Here $g_{tt}=(1-2M/r_1)$ is the time component of the metric in the background geometry, evaluated at the location where the null rays pass through the geometric uncertainty.
 
-It is more enlightening to write this expression in the local physical quantities (see Appendix \ref{finalEq} for derivations).
+It is more enlightening to write this expression in terms of local physical quantities (see Appendix \ref{finalEq} for derivations).
 Let $\sigma$ be the energy density of the shell in its rest frame, and $\Delta l$ be the physical distance between the shells in that frame, we get
 \begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0} = 4 \pi \sigma \Delta l g_{tt}^{-1}~.
+	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}} = 4 \pi \sigma \Delta l g_{tt}^{-1}~.
 	\label{eq-inv}
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{ \delta t_0}}{\delta t_0}  \begin{cases}
+\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}}  \begin{cases}
 = 4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
@@
 
-Classically, soft hairs manifest as memory effects that alters the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
+Classically, soft hairs manifest as memory effects that alter the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
 Two neighbouring null rays simply ``remember'' the geometric uncertainty they passed through.
@@
 \begin{equation}
-	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
+	ds^2 = - \left( 1 -\frac{2M}{r} \right) d\bar{t}^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
 \end{equation}
@@
 where we are working with units in which $G = c = 1$.
+The bar is used over the time coordinate to differentiate it from the time coordinate we will use in the spacetime with mass $M'$.
 We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}.
@@
 \begin{equation}
-	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
+	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = r_0 - r_e + 2M \ln \left( \frac{r_0 - 2M}{r_e - 2M}  \right)	\label{3}
 \end{equation}
@@
 \begin{equation}
-	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
+	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = r_0 - r_e + 2M \ln \left( \frac{r_0 - 2M}{r_e - 2M}  \right).	\label{4}
 \end{equation}
@@
 In this case the particle's move through two different spacetime regions.
-Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
-\\
-\\
-As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$.
-Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$).
-To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC.
+Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M' \equiv M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
+The metric in region II is given by
+
+\begin{equation}
+	ds^2 = - \left( 1 - \frac{2M'}{r} \right) d t^2 + \left( 1 - \frac{2M'}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{2}.
+\end{equation}
+
+Note that the time coordinate is different from the one in Eq (\ref{1}).
+The radial coordinate is however the same as the shell connecting the two spacetimes is a physical surface with a fixed radius $r$.
+As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta \bar{t_e}$, is the same as the coordinate time interval at $r_1$, $\delta \bar{t_1}$.
+Now we need to find the corresponding coordinate time interval in region $II$, $\delta t_1$.
+To do this we simply note that the corresponding proper time at $r_1$, $\delta \bar{\tau_1}$ must be the same in both regions of spacetime - this is a simple consequence of the IJC.
 The coordinate time intervals at $r_1$, in the two different regions, are therefore related by
@@
 \begin{equation}
-	\delta t_1 = \delta t_0 = \left( \frac{1 - \frac{2(M + \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta \hat{t}_1.
+	\delta \bar{t_1} = \delta \bar{t_e} = \left( \frac{1 - \frac{2(M + \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta t_1.
 \end{equation}
 
-We can propagate the particles through region $II$ from $r_1$ to $r_2$ and we know $\delta \hat{t}_1 = \delta \hat{t}_2$.
-From the fact that the proper time corresponding to the coordinate time intervals will be the same, we can relate $\delta \hat{t}_2$ back to $\delta t_2$ in region $I$,
+We can propagate the particles through region $II$ from $r_1$ to $r_2$ and we know $\delta t_1 = \delta t_2$.
+From the fact that the proper time corresponding to the coordinate time intervals will be the same, we can relate $\delta t_2$ back to $\delta \bar{t_2}$ in region $I$,
 
 \begin{equation}
-	\delta \hat{t}_2 = \delta \hat{t}_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M + \Delta M)}{r_2}} \right) \delta t_2.	\label{7}
+	\delta t_2 = \delta t_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M + \Delta M)}{r_2}} \right) \delta \bar{t_2}.	\label{7}
 \end{equation}
 
-Since $\delta t_2$ is equal to the time interval observed by the observer at $r_0$, $\delta t_0$, we can find the proper time observed by the observer, $\delta \tau_0  = \delta t_e \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M + \Delta M)} \right) \right)^\frac{1}{2}$.
+Since $\delta \bar{t_2}$ is equal to the time interval observed by the observer at $r_0$, $\delta \bar{t_0}$, we can find the proper time observed by the observer, $\delta {\tau_0}  = \delta {\bar{t_e}} \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M + \Delta M)} \right) \right)^\frac{1}{2}$.
 Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away.
-$\delta t_e = \delta \bar{\tau_0}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,
+$\delta {\bar{t_e}} = \delta {\bar{\tau_0}}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,
 
@@
 This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect.
-
-\subsection{Leading order expansion limit}
-
 By assuming $r_1>> \Delta r \equiv r_2 - r_1$ and $r_1>> \Delta M$ we can expand Eq (\ref{eq-result}), to leading order in small quantities,
@@
 \begin{eqnarray}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta t_0} & = & 
+	\frac{\delta t_0 - \bar{\delta t_0}}{\delta \bar{t_0}} & = & 
 	\left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1 \right)	\nonumber	\\
@@
 	\frac{3}{8} \frac{(\Delta r+ 2 \Delta M)^2}{(r_1 - 2M)^2} 	\nonumber	\\
-	& = & \frac{\Delta M \Delta r}{(r_1 - 2M)^2}.
+	& = & \frac{\Delta M \Delta r}{(r_1 - 2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}.
 \end{eqnarray}
@@
 
-where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric, $h^{ab}$, we are using. $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
+where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric, $h_{ab}$, we are using. $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
 We can define the induced metrics for constant $r$ values; for region $I$ it is
@@
 	\sigma & = & \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M. \nonumber	\\
-	& = &  \frac{\Delta M}{4 \pi r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}}.	\label{sig-Dm}
+	& = &  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
 \end{eqnarray}
@@
 \begin{equation}
-	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
+	\Delta l = \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} \Delta r = g_{tt}^{-\frac{1}{2}} \Delta r.	\label{Dl-Dr}
 \end{equation}
@@
 
-\subsection{Minkowski limit ($M=0$)}
-
-In the Minkowski limit we set $M=0$ in Eq (\ref{lim-result}) and put in the physical quantities from Eqs (\ref{sig-Dm}, \ref{Dl-Dr}, \ref{l-r}) to get
+We will be interested in three limits of $M=0$, $M \ll l$ and $M \gg l$ and the value of $l$ in these three limits is
 
 \begin{equation}
-	\frac{\delta t_0 - \bar{t_0}}{\delta t_0} = \frac{\Delta M \Delta l}{l^2} = 4 \pi \sigma \Delta l.	\label{Eq-mink}
+l \begin{cases}
+= r_1	 &\ \ \ \ \ (M = 0)\\
+\approx r_1 - 2M & \ \ \ \ \ (M \ll l)	\\
+\approx \sqrt{8M(r_1 - 2M)} & \ \ \ \ \ (M \gg l).
+\end{cases}	
 \end{equation}
 
-Very far away from the horizon, we expect a small deviation in Eq (\ref{Eq-mink}) from the Minkowski result as we know that the Schwarzschild geometry is asymptotically flat.
+%
+%\subsection{Minkowski limit ($M=0$)}
+%
+%In the Minkowski limit we set $M=0$ in Eq (\ref{lim-result}) and put in the physical quantities from Eqs (\ref{sig-Dm}, \ref{Dl-Dr}, \ref{l-r}) to get
+%
+%\begin{equation}
+%	\frac{\delta t_0 - \bar{t_0}}{\delta t_0} = \frac{\Delta M \Delta l}{l^2} = 4 \pi \sigma \Delta l.	\label{Eq-mink}
+%\end{equation}
+%
+%Very far away from the horizon, we expect a small deviation in Eq (\ref{Eq-mink}) from the Minkowski result as we know that the Schwarzschild geometry is asymptotically flat.
 By assuming $r_1>>M$ we  expanded Eq \ref{l-r} to first order to give
-
-\begin{equation}
-	l = r_1 - 2M - M \ln \left( \frac{r_1 - 2M}{M} \right) \Rightarrow r_1 - 2M = l - M \ln \left( \frac{l}{M} \right)	\label{l-r1}.
-\end{equation}
-
-Where in the last step we have used $x = y + \ln (y) \Rightarrow y = x - \ln(x)$ to leading order when $x \approx y$.
+%
+%\begin{equation}
+%	l = r_1 - 2M - M \ln \left( \frac{r_1 - 2M}{M} \right) \Rightarrow r_1 - 2M = l - M \ln \left( \frac{l}{M} \right)	\label{l-r1}.
+%\end{equation}
+%
+%Where in the last step we have used $x = y + \ln (y) \Rightarrow y = x - \ln(x)$ to leading order when $x \approx y$.
 We can substitute this, along with Eqs (\ref{sig-Dm}, \ref{Dl-Dr}) into Eq (\ref{lim-result}) to get
-
-\begin{eqnarray}
-	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = & 4 \pi \sigma \frac{r_1^2}{(r_1 - 2M)^2} \left( 1 - \frac{2M}{r_1} \right)^{\frac{1}{2}} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2}  \nonumber	\\
-	& = & 4 \pi \sigma \Delta l \left( 1 - \frac{2M}{r_1} \right)^{-1} = 4 \pi \sigma \Delta l g_{rr}	\label{gen-result}
-\end{eqnarray}
-
-Note that this is actually a general result so far in terms of the coordinate distance $r_1$. We can expand this to leading order now by assuming $2M/r_1 <<1$,
-
-\begin{equation}
-	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} = 4 \pi \sigma \Delta l \left( 1 + \frac{2M}{r_1} \right) 
-\end{equation}
-
-\subsection{Near horizon ($M>>r_1$)}
-
-In this limit the coordinate distance $r_1$ and proper distance $l$ are related by
-
-\begin{equation}
-	r_1 = \frac{l^2}{8M} + 2M
-\end{equation}
-
-Again, we substitute this expression along with Eqs (\ref{sig-Dm}, \ref{Dl-Dr}) into Eq (\ref{lim-result}) to get
-
-\begin{eqnarray}
-	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = &  4 \pi \sigma \delta l \left( 1+ \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \left( 1 + \frac{r_1 - 2M}{2M} \right)^{-1} \right)	\nonumber	\\
-	& =& 4 \pi \sigma \delta l \left( \frac{2M}{r_1 - 2M}\right)^2 \left( \frac{r_1 - 2M}{2M}  + \mathcal{O}(M^{-2}) \right)	\nonumber	\\
-	& = & 64 \pi \sigma \delta l \frac{M^2}{l^2} + \mathcal{O}(r^{-2})
-\end{eqnarray}
+%
+%\begin{eqnarray}
+%	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = & 4 \pi \sigma \frac{r_1^2}{(r_1 - 2M)^2} \left( 1 - \frac{2M}{r_1} \right)^{\frac{1}{2}} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2}  \nonumber	\\
+%	& = & 4 \pi \sigma \Delta l \left( 1 - \frac{2M}{r_1} \right)^{-1} = 4 \pi \sigma \Delta l g_{rr}	\label{gen-result}
+%\end{eqnarray}
+%
+%Note that this is actually a general result so far in terms of the coordinate distance $r_1$. We can expand this to leading order now by assuming $2M/r_1 <<1$,
+%
+%\begin{equation}
+%	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} = 4 \pi \sigma \Delta l \left( 1 + \frac{2M}{r_1} \right) 
+%\end{equation}
+%
+%\subsection{Near horizon ($M>>r_1$)}
+%
+%In this limit the coordinate distance $r_1$ and proper distance $l$ are related by
+%
+%\begin{equation}
+%	r_1 = \frac{l^2}{8M} + 2M
+%\end{equation}
+%
+%Again, we substitute this expression along with Eqs (\ref{sig-Dm}, \ref{Dl-Dr}) into Eq (\ref{lim-result}) to get 
+%
+%\begin{eqnarray}
+%	\frac{\delta t_0 - \delta \bar{t_0}}{\delta t_0} & = &  4 \pi \sigma \delta l \left( 1+ \frac{2M}{r_1 - 2M} \right)^2 \left( 1 - \left( 1 + \frac{r_1 - 2M}{2M} \right)^{-1} \right)	\nonumber	\\
+%	& =& 4 \pi \sigma \delta l \left( \frac{2M}{r_1 - 2M}\right)^2 \left( \frac{r_1 - 2M}{2M}  + \mathcal{O}(M^{-2}) \right)	\nonumber	\\
+%	& = & 64 \pi \sigma \delta l \frac{M^2}{l^2} + \mathcal{O}(r^{-2})
+%\end{eqnarray}
+%
 

### 2016-11-03 Draft_BH_shells.tex

--- 2016-11-02 Draft_BH_shells.tex
@@
 We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
-We apply it to the propagation of Hawking quanta, testing whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
-We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT is related to the soft-hair-memory effect.
+We apply it to the propagation of Hawking quanta and test whether ignoring the entanglement with the geometry also becomes arbitrarily reliable in the limit of a large black hole. 
+We present curious results to suggest a negative answer, and we discuss how this loss of na\"ive unitarity in QFT might be related to a solution of the paradox based on the soft-hair-memory effect.
 \end{abstract}
@@
 \item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer by a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
-\item {\bf General relativity:} The collapse-Schwarzschid geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
+\item {\bf General relativity:} The collapse-Schwarzschild geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
 Therefore, there is no drama while crossing the horizon.
@@
 ds^2 = -\left(1-\frac{2M}{r}\right)dt^2 + \frac{dr^2}{1-\frac{2M}{r}} + r^2d\Omega_2^2~.
+\label{eq-metric}
 \end{equation}
@@
 \end{enumerate}
-Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validaty of learning a general lesson from a special example.
+Note that if we were reporting a positive result, that such uncertainty upholds unitarity, then one should question the validity of learning a general lesson from a special example.
 However, we will show that this particular form of $\Delta g_{\mu\nu}$ is already sufficient to question unitarity, and we did not choose this form to specifically do that.
 Thus our limited analysis is sufficient to raise a reasonable doubt to the classical-background approximation.
-\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffer from UV/IR divergences.
+\item {\bf Renormalization.} It is well-known that na\"ive applications of QFT often suffers from UV/IR divergences.
 In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
@@
 More concretely, our setup is shown in Fig.\ref{fig-setup}. 
-We start by choosing two points at some $r_0\gg M$ with a $\delta \bar{t_0}\sim M$ coordinate time separation between them.
-This represents one wavelength of the mode function of an asymptotic Hawking quantum.
-We then back-track two null geodesics from these two points back to two points near the horizon, at $r_e$ with $(r_e-2M)\ll 2M$.
-Now their separation represents one wavelength of a near-horizon mode, which would have propagated to the asymptotic mode if there were no geometric uncertainty. 
-We then introduce introduce a geometric uncertainty as two shells of zero total ADM mass. 
-Therefore, both the near horizon and the asymptotic regions are not affected by such uncertainty.
-Only the process of propagation is affected.
-With the same two starting points near the horizon we calculate the separation $\delta t_0$ of the two null geodesics when they arrive at $r_0$, and compare it with $\delta \bar{t_0}$.
+We start by choosing two out-going null rays in the background Schwarzschild spacetime given by Eq.~(\ref{eq-metric}).
+Far away from the black hole, at $r_0\gg M$, they are separated by time $T \sim M$, which is one period of an asymptotic Hawking quantum.
+Near the horizon, at $r_e$ with $(r_e-2M)\ll 2M$, the same two null rays will have the same coordinate time separation, but a much smaller proper time separation.
+This represent a near-horizon mode.
+
+Next, we introduce geometric uncertainty as two shells of zero total ADM mass.
+Both the near horizon and the asymptotic regions are not affected by such uncertainty.
+Thus it is a well-defined question to ask how the same near-horizon mode will end up when they reached the same large $r_0$. 
+It turns out that the time separation between these two null rays will be different. 
+Following the calculation in Appendix \ref{Dtime}, we arrive at this simple expression:
+\begin{equation}
+\frac{\Delta T}{T} = 
+\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}-1\right)~,
+\label{eq-result}
+\end{equation}
+where $(T+\Delta T)$ is the new separation with the geometric uncertainty, $r_1$ is the location of the inner shell, $r_2$ is the location of the outer shell, and $\pm\Delta M$ are their individual ADM masses.
 
@@
 
-After some formal calculations in Appendix \ref{Dtime}, we arrive at this simple expression:
-\begin{equation}
-\frac{\delta t_0 - \bar{\delta t_0}}{\delta \bar{t_0}} = 
-\left(\sqrt{\frac{r_2-2M}{r_1-2M}}\sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}-1\right)~,
-\label{eq-result}
-\end{equation}
-where $r_1$ is the location of the inner shell, $r_2$ is the location of the outer shell, and $\pm\Delta M$ are their individual ADM masses.
-
 \subsection{Physical interpretation}
 
-In the entire calculation, we will stay in the regime that $r_1, 2M, (r_1-2M) \gg \Delta M, \Delta r$, where $\Delta r \equiv(r_2-r_1)$. 
+In the rest of this paper, we will stay in the regime that $r_1, 2M, (r_1-2M) \gg \Delta M, \Delta r$, where $\Delta r \equiv(r_2-r_1)$. 
 This guarantees that the geometric fluctuation is small, as it only affects a small region $\Delta r$, and the change in the metric $\Delta g_{\mu\nu}/g_{\mu\nu}$ is small in the affected region.
-Under this assumption, we can expand Eq (\ref{eq-result}) to get 
+Under this assumption, we can expand Eq.~(\ref{eq-result}) to get 
 \begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}~.
+	\frac{\Delta T}{T} = \frac{\Delta M \Delta r}{(r_1-2M)^2} = \frac{\Delta M \Delta r}{r_1^2} g_{tt}^{-2}~.
 		\label{lim-result}
@@
 \begin{equation}
-	\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}} = 4 \pi \sigma \Delta l g_{tt}^{-1}~.
+	\frac{\Delta T}{T} = 4 \pi \sigma \Delta l g_{tt}^{-1}~.
 	\label{eq-inv}
@@
 Also, the combination $(\sigma\Delta l)$ is invariant under radial boosts, thus Eq.~(\ref{eq-inv}) does not care about whether the shells are actually at rest, nor in which frame we calculate it.
+
+The physical meaning of Eq.~(\ref{eq-inv}) is quite obvious.
 
@@
 \begin{equation}
-\frac{\delta t_0 - \bar{ \delta t_0}}{\delta \bar{t_0}}  \begin{cases}
+\frac{\Delta T}{T} ~ \begin{cases}
 = 4 \pi \sigma \Delta l~	 &\ \ \ \ \ (M = 0)\\
@@
 As long as $l$ is much larger than the UV cut-off scale of the QFT, one would believe that modes in this region propagates out to become Hawking quanta, and QFT guarantees the unitarity of such process.
-Here we hold $\sigma\Delta l$ fixed at the same value of empty Minkowski space, we can see that the effect of geometric uncertainty gets arbitrarily larger than in the Minkowski space.
+Here we hold $(\sigma\Delta l)$ fixed at the same value of empty Minkowski space, we can see that the effect of geometric uncertainty gets arbitrarily larger than in the Minkowski space.
 Note that the absolute value of the effect cannot become arbitrarily large, since it is actually bounded at order one by the validity constraint of our calculation: $\Delta g_{\mu\nu} \ll g_{\mu\nu}$.
@@
 Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.
-It is also interesting to apply the same check to other geometries, especially other types of horizons.
+
+In the hindsight, the physical meaning of our effect, Eq.~(\ref{eq-inv}), is quite clear.
+The geometric uncertainty, parametrized by $(\sigma\Delta l)$, leads to a fixed physical change locally where it is.
+When there is a large gravitational redshift, such effect is amplified.
+In the large black hole limit, starting from a fixed physical distance from the horizon, the redshift gets arbitrarily large, so the effect gets amplified by an arbitrarily large factor.
+It is natural to expect similar effects in other geometries with horizons or even just expansions.
+We look forward to exploring those more general cases.
 
@@
 While formulating the information paradox, it is customary to take the large black hole limit.
-Such limit allows us to identify modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
+Such limit allows us to identify near-horizon modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
 For these modes, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
@@
 
-A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric
-
+The background geometry is given by Eq.~(\ref{eq-metric}).
+An out-going radial null ray is given by
 \begin{equation}
-	ds^2 = - \left( 1 -\frac{2M}{r} \right) d\bar{t}^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
+	t - t_e = r - r_e + 2M \ln \left( \frac{r - 2M}{r_e - 2M}  \right)~,
+	\label{3}
 \end{equation}
-
-where we are working with units in which $G = c = 1$.
-The bar is used over the time coordinate to differentiate it from the time coordinate we will use in the spacetime with mass $M'$.
-We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}.
-Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole.
-An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$.
-We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}).
-By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation
-
+where $r_e$ and $t_e$ are the starting point of this null ray.
+A second null ray which reaches some asymptotic $r=r_0\gg M$ at a later time is simply
 \begin{equation}
-	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = r_0 - r_e + 2M \ln \left( \frac{r_0 - 2M}{r_e - 2M}  \right)	\label{3}
+	t - (t_e + T) = r - r_e + 2M \ln \left( \frac{r - 2M}{r_e - 2M}  \right)~.
 \end{equation}
-
-where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2.
-
-\begin{equation}
-	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = r_0 - r_e + 2M \ln \left( \frac{r_0 - 2M}{r_e - 2M}  \right).	\label{4}
-\end{equation}
-
-Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that
-
-\begin{equation}
-	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
-\end{equation}
-
-Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.
+Clearly, they have the same coordinate time separation $\Delta t = T$ everywhere, we illustrate in the lower part of Figure \ref{fig-setup}.
 
@@
 
-Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
+Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M| \ll M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
 We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells.
+
 In this case the particle's move through two different spacetime regions.

### 2016-11-03 Draft_BH_shells.tex
simplify notations

@@
 The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
-Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
+Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
 We establish an analogy to Feynman's analysis of a double-slit experiment. 
@@
 Therefore, there is no drama while crossing the horizon.
-\item {\bf Local quantum field theory:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
+\item {\bf Quantum field theory in curved spacetime:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
 For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
@@
 As this change increases, one should gradually lose faith in the unitary propagation of such mode, since it becomes increasingly difficult to experimentally verify.
-\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$. 
+\item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$ in Eq.~(\ref{eq-metric}). 
 A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
@@
 
-Next, we introduce geometric uncertainty as two shells of zero total ADM mass.
+Next, we introduce geometric uncertainty as sourced by two shells of zero total ADM mass.
 Both the near horizon and the asymptotic regions are not affected by such uncertainty.
@@
 The physical meaning of Eq.~(\ref{eq-inv}) is quite obvious. 
-
-In order to appreciate the effect of such geometric uncertainty near the horizon of a large black hole (which is usually considered the ideal situation to formulate the information paradox), we evaluate Eq.~(\ref{eq-inv}) in three regimes;
+Geometric uncertainty creates a fixed-size uncertainty in the local proper time where it occurs.
+If it happens in the region which the wavelength of a mode is blue-shifted, then it gets magnified to be relatively larger.
+To be more precise, we evaluate Eq.~(\ref{eq-inv}) in three regimes; 
 1) The Minkowski limit: $M=0$; 
@@
 
-\subsection{The self-consistency check of local QFT}
+\subsection{The self-consistency check of QFT}
 
-In this paper, we proposed a self-consistency check of local QFT in curved spacetime geometries.
+In this paper, we proposed a self-consistency check of QFT in curved spacetime geometries.
 We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
@@
 give the same particle number. 
-Thus there is no general crisis if we admit that local QFT sometimes loses subsystem unitarity.
+Thus there is no general crisis if we admit that QFT sometimes loses subsystem unitarity.
 
-As far as we know, an observable that explicitly checks the subsystem unitarity of local QFT during particle-production events is the cosmological Bell inequality \cite{Mal15}. 
+As far as we know, an observable that explicitly checks the subsystem unitarity of QFT during particle-production events is the cosmological Bell inequality \cite{Mal15}. 
 One might be able to apply a similar self-consistency check to such a model and update the prediction of whether a violation of Bell inequality is actually expected.
@@
 
-\section{Calculation of proper time change}
+\section{Calculation of time shift at $r_0\gg M$}
 \label{Dtime}
-
-\subsection{Background spacetime - no shell}
 
@@
 where $r_e$ and $t_e$ are the starting point of this null ray.
-A second null ray which reaches some asymptotic $r=r_0\gg M$ at a later time is simply
+A second null ray which reaches some asymptotic $r_0\gg M$ at a later time is simply
 \begin{equation}
@@
 \end{equation}
-Clearly, they have the same coordinate time separation $\Delta t = T$ everywhere, we illustrate in the lower part of Figure \ref{fig-setup}.
+Clearly, they have the same coordinate time separation $\Delta t = T$ everywhere, and we illustrate in the lower part of Figure \ref{fig-setup}.
 
-%We can convert $\delta\bar{t_0}$ to proper time
-%
-%\begin{equation}
-%	\delta \bar{\tau_0} = \left( 1 -\frac{2M}{r_0} \right)^\frac{1}{2} \delta \bar{t_0}
-%\end{equation}
-%
-%and in the limit that the observer is very far away $\delta \bar{\tau_0} \approx \delta \bar{t_0}$.
+Next we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M| \ll M$, at distances $r_1 < r_2$ as shown in the top part of figure \ref{fig-setup}.
+We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. 
+The metric remains the same as Eq.~(\ref{eq-metric}), except for the region between the two shells, which is given by
+\begin{equation}
+	ds^2 = - \left( 1 - \frac{2M'}{r} \right) d t'^2 + \left( 1 - \frac{2M'}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2~.	\label{2}
+\end{equation}
+Here $M' = M + \Delta M$. 
+Due to spherical symmetry, we can demand that the angular and radial coordinates to be the same as the background metric. 
+But the time coordinate will be different, so we denote that as $t'$.
 
-\subsection{Perturbed spacetime - double shell}
+At the two junctions, the proper time on both sides should be identical, which is the zeroth-order IJC---continuity of spacetime.
+That means
+\begin{eqnarray}
+	\sqrt{1-\frac{2M}{r_1}} \delta t_1 &=& \sqrt{1-\frac{2M'}{r_1}} \delta t'_1~, \\
+         \sqrt{1-\frac{2M}{r_2}} \delta t_2 &=& \sqrt{1-\frac{2M'}{r_2}} \delta t'_2~.
+\end{eqnarray}
 
-Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M| \ll M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}.
-We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells.
-
-In this case the particle's move through two different spacetime regions.
-Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M' \equiv M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
-The metric in region II is given by
-
+Therefore, the two null rays starting with a separation $T$ at $r_e<r_1$, going through this geometric uncertainty, will end up having a different separation given by
 \begin{equation}
-	ds^2 = - \left( 1 - \frac{2M'}{r} \right) d t^2 + \left( 1 - \frac{2M'}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{2}.
+T+\Delta T = \sqrt{\frac{r_2-2M}{r_1-2M}} \sqrt{\frac{r_1-2(M+\Delta M)}{r_2-2(M+\Delta M)}}~.
+\end{equation}
+This clearly leads to Eq.~(\ref{eq-result}):
+\begin{equation}
+	\frac{\Delta T}{T} 
+	= \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M+\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
 \end{equation}
 
-Note that the time coordinate is different from the one in Eq (\ref{1}).
-The radial coordinate is however the same as the shell connecting the two spacetimes is a physical surface with a fixed radius $r$.
-As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta \bar{t_e}$, is the same as the coordinate time interval at $r_1$, $\delta \bar{t_1}$.
-Now we need to find the corresponding coordinate time interval in region $II$, $\delta t_1$.
-To do this we simply note that the corresponding proper time at $r_1$, $\delta \bar{\tau_1}$ must be the same in both regions of spacetime - this is a simple consequence of the IJC.
-The coordinate time intervals at $r_1$, in the two different regions, are therefore related by
-
-\begin{equation}
-	\delta \bar{t_1} = \delta \bar{t_e} = \left( \frac{1 - \frac{2(M + \Delta M)}{r_1}}{1 - \frac{2M}{r_1}} \right)^\frac{1}{2} \delta t_1.
-\end{equation}
-
-We can propagate the particles through region $II$ from $r_1$ to $r_2$ and we know $\delta t_1 = \delta t_2$.
-From the fact that the proper time corresponding to the coordinate time intervals will be the same, we can relate $\delta t_2$ back to $\delta \bar{t_2}$ in region $I$,
-
-\begin{equation}
-	\delta t_2 = \delta t_1= \left( \frac{1 - \frac{2M}{r_2}}{1 - \frac{2(M + \Delta M)}{r_2}} \right) \delta \bar{t_2}.	\label{7}
-\end{equation}
-
-Since $\delta \bar{t_2}$ is equal to the time interval observed by the observer at $r_0$, $\delta \bar{t_0}$, we can find the proper time observed by the observer, $\delta {\tau_0}  = \delta {\bar{t_e}} \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right) \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M + \Delta M)} \right) \right)^\frac{1}{2}$.
-Where we have dropped the $\left( 1 - \frac{2M}{r_0} \right)^\frac{1}{2}$ term since we assume the observer is very far away.
-$\delta {\bar{t_e}} = \delta {\bar{\tau_0}}$ when the observer is far away therefore we can define a dimensionless quantity that quantifies the change in proper time intervals for consecutive photons in perturbed spacetime case and the unperturbed case,
-
-\begin{equation}
-	 \frac{\delta \tau_0 - \delta \bar{\tau_0}}{\delta \bar{\tau_0}} = \left( \left( \frac{r_2 - 2M}{r_1 - 2M} \right)^\frac{1}{2} \left( \frac{r_1 - 2(M+\Delta M)}{r_2 - 2(M+\Delta M)} \right)^\frac{1}{2} - 1\right).	\label{10}
-\end{equation}
-
-This shows that when there are no shells, $\Delta M = 0$, there is no change in proper time intervals which is what one would expect.
-By assuming $r_1>> \Delta r \equiv r_2 - r_1$ and $r_1>> \Delta M$ we can expand Eq (\ref{eq-result}), to leading order in small quantities,
-
+Assuming $r_1$, $r_2$, $M$, $r_1-2M$ are all much larger than $\Delta M$ and $\Delta r=(r_2-r_1)$, we can expand Eq (\ref{eq-result}) to leading order of these two small quantities.
 \begin{eqnarray}
-	\frac{\delta t_0 - \bar{\delta t_0}}{\delta \bar{t_0}} & = & 
+	\frac{\Delta T}{T} & = & 
 	\left( \left( 1+ \frac{\Delta r}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{2\Delta M}{r_1 - 2M} \right)^\frac{1}{2} \left( 1 + \frac{\Delta r + 2 \Delta M}{r_1 - 2M} \right)^{-\frac{1}{2}} - 1 \right)	\nonumber	\\
@@
 
-The first step in this derivation is write down the physical, local, quantities needed to replace $\Delta M, r_1$ and $\Delta r$.
-The natural thing to replace $\Delta M$ is the surface stress energy, $\sigma$, of the shell.
-This is given by the $tt$ component of the surface stress energy tensor $S_{ab}$ given by the IJC.
+Here we will translate the coordinate quantities, $\Delta M, r_1$ and $\Delta r$, into the local physical quantities: $\sigma$ as the co-dimension-one energy density of the shell, $l$ as the physical distance from the horizon, and $\Delta l$ as the physical distance between the two shells.
+This is given by the Israel Junction Condition.
+\begin{equation}
+	S^a_b = [K^a_b] - [K]h^a_b~.
+\end{equation}
+Here $K_{ab}$ is the extrinsic curvature corresponding to the induced metric.
+$K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
+The middle brackets ``[ ]'' means we are calculating the extrinsic curvature from both sides of the junction and take their difference.
 
+The induced metrics for the junction at $r_1$, expressed in the coordinate of region $I$ in Fig.\ref{fig-setup}, is the following.
 \begin{equation}
-	S^a_b = [K^a_b] - [K]h^a_b,
+	ds_{\rm induced, \ region \ I}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
 \end{equation}
+The extrinsic curvature from this side will simply be the $r$ derivative.
+Analogously we have the same induced metric written in the coordinate of region $II$,
+\begin{equation}
+	ds_{\rm induced, \ region \ II}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+\end{equation}
+Similarly taking the $r$ derivative here leads to the extrinsic curvature from this side.
+Combine with the continuity condition that relates $t$ to $t'$, 
+\begin{equation}
+	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2~,
+\end{equation}
+we can calculate the extrinsic curvature components.
+\begin{eqnarray}
+	(K^t_t)^{I} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} ~.	\nonumber	\\
+	(K^\theta_\theta)^{I} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
+	= (K^\phi_\phi)^{I}~.	\label{16}
+\end{eqnarray}
+It is obvious that for region II, we simply replace $M$ by $M'$.
 
-where $K_{ab}$ is the extrinsic curvature corresponding to the induced metric, $h_{ab}$, we are using. $K = K_{ab} h^{ab}$ is the trace of the extrinsic curvature.
-We can define the induced metrics for constant $r$ values; for region $I$ it is
-
-\begin{equation}
-	ds_{3M}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
-\end{equation}
-
-Analogously we have the metric corresponding to mass $M' = M+ \Delta M$ in region $II$
-
-\begin{equation}
-	ds_{3M'}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
-\end{equation}
-
-We could rewrite Eq (\ref{13}) and (\ref{14}) in Gaussian normal coordinates (where the coefficient in front of the time component is 1), however the first order junction condition is that the induced metric on both sides of the shell must be the same.
-Therefore it is easy to find a relation between the two time coordinates
-
-\begin{equation}
-	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2.
-\end{equation}
-
-Using this, we calculate the extrinsic curvature components
-
-\begin{eqnarray}
-	(K^t_t)^{(M)} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} 	\nonumber	\\
-	(K^\theta_\theta)^{(M)} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
-	= (K^\phi_\phi)^{(M)}	\label{16}
-\end{eqnarray}
-
-where the superscript of $M$ denotes the quantities evaluated in the metric of mass $M$.
-Analogous expressions hold for the extrinsic curvature components calculated in the metric of mass $M'$ by just replacing $M$ by $M'$ in Eq (\ref{16}).
- The time component of the surface stress energy tensor $S^0_0$ is
-
+The time component $S^0_0$ is the surface energy density.
 \begin{equation}
@@
 \end{equation}
-
-This expression represents a small change in the mass and thus can be written as
-
+When $2\Delta M \ll (r_1-2M)$, this is approximately given by 
 \begin{eqnarray}
-	\sigma & = & \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M. \nonumber	\\
-	& = &  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
+	\sigma  =  \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
+	 =  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
 \end{eqnarray}
-
 Next we need to replace the coordinate distance $\Delta r$ with the proper distance $\Delta l$ and the relation between them is given by
-
 \begin{equation}
@@
 \end{equation}
+These equations allow us to replacing $\Delta M$ by $\sigma$ and $\Delta r$ by $\Delta l$ in Eq.~(\ref{eq-result}) to get Eq.~(\ref{eq-inv}).
 
-This can be integrated to give the proper distance, $l$, between the inner shell and the horizon
-
+Finally, Eq.~(\ref{Dl-Dr}) can be integrated to give the proper distance $l$ between the inner shell and the horizon.
 \begin{eqnarray}
 	l & = & \int^{r_1}_{2M} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}} dr	\nonumber	\\
-	& = & \sqrt{(r_1 - 2M)r_1} + M \log \left( \frac{ r_1 - M + \sqrt{(r_1 - 2M)r_1}}{M} \right)	\label{l-r}
+	& = & \sqrt{(r_1 - 2M)r_1} + M \log \left( \frac{ r_1 - M + \sqrt{(r_1 - 2M)r_1}}{M} \right)	~.
+	\label{l-r}
 \end{eqnarray}
-
-We will be interested in three limits of $M=0$, $M \ll l$ and $M \gg l$ and the value of $l$ in these three limits is
-
+We will be interested in two extreme cases: $M \ll l$ and $M \gg l$. The value of $l$ in these cases are given by
 \begin{equation}
-l \begin{cases}
-= r_1	 &\ \ \ \ \ (M = 0)\\
-\approx r_1 - 2M & \ \ \ \ \ (M \ll l)	\\
-\approx \sqrt{8M(r_1 - 2M)} & \ \ \ \ \ (M \gg l).
+l \approx \begin{cases}
+ r_1 - 2M & \ \ \ \ \ (M \ll l)~,	\\
+ \sqrt{8M(r_1 - 2M)} & \ \ \ \ \ (M \gg l)~.
 \end{cases}	
 \end{equation}
+This allows us to evaluate Eq.~(\ref{eq-inv}) and get Eq.~(\ref{fin-result})
 

### 2016-11-04 Draft_BH_shells.tex
grammar check

@@
 We establish an analogy to Feynman's analysis of a double-slit experiment. 
-Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen to project the interference pattern goes to infinitely far away.
+Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen the interference pattern is projected onto goes to infinitely far away.
 We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
@@
 \end{itemize}
-Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, therefore carrying the same qubit of information. 
+Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, and therefore carries the same qubit of information. 
 However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
@@
 firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
-various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
+various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it to compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
 
@@
 Basically, the near horizon mode is thermal as demanded by Statement Two.
-But it propagates out in a non-unitary process, gaining the appropriate information to restore a unitary $S$-matrix as demanded by Statement One. 
-For such abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
+However, it propagates out in a non-unitary process, gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
+For this abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
 Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
@@
 If we treat the superposition of different classical geometries as a quantum system, it may qualify as the hidden system that is responsible for the non-unitary propagation of Hawking quanta. 
-Unfortunately, the early version of such proposal can be defeated by counting entropy.
+Unfortunately, the early version of this proposal can be defeated by counting entropy.
 In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the amount of microscopic information carried by the black hole.
@@
 The recent development on black-hole-soft-hairs \cite{HawPer16} hinted a way to revive this idea.
-Basically, it was realized that two isometric (regions of) geometries should not always be considered as the same state.
+Essentially, it was realized that two isometric (regions of) geometries should not always be considered as the same state.
 If one maps the geometries with congruences of geodesics, two isometric regions with different maps are actually different states.
@@
 
-In this paper, we will take another step that is complementary to the above progress. It is exciting to know that modifying Statement Three can in-principle resolve the paradox. 
-However, it remains a great mystery of why should local QFT break down in low curvature regions. 
+In this paper, we will take another step that is complementary to the above progress.
+It is exciting to know that modifying Statement Three can, in-principle, resolve the paradox, yet it remains a great mystery why local QFT should break down in low curvature regions.
 If we just demand that it breaks down in order to resolve the information paradox, then there is no reason why this solution is preferred over modifying Statement One or Two. 
@@
 Applying such self-consistency check, we can show that a unitary propagation from a near horizon mode to an asymptotic Hawking quantum is already self-inconsistent. 
-Thus it is only natural to modify Statement Three.
+Thus, it is only natural to modify Statement Three.
 
@@
 Namely, we assume that the full system can be separated into a ``classical background'' and a ``quantum subsystem''. 
-After such artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
+After this artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
 However, such unitarity should not be taken as a physical fact unless one specifically checks the nature of interactions with the background.
@@
 We show that with a fixed geometric uncertainty, a classical wave suffers an {\it arbitrarily large} correction in the large black hole limit.
-By analogy to Feynman's analysis, this is strong evidence that the apparent unitarity of QFT in this case is not a valid assumption.
+By analogy to Feynman's analysis, this is strong evidence that the apparent unitarity of QFT is, in this case, not a valid assumption.
 
@@
 Namely, its value should be fixed if we move the screen further away. Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition. 
-Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible, thus the subsystem unitarity is valid.
+Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible and subsystem unitarity is valid.
 
@@
 
-The double-slit interference is an example that both the classical coherence and quantum unitarity can be calculated explicitly and show that they follow the same condition.
+The double-slit experiment is an example where both the classical coherence and quantum unitarity can be calculated explicitly and shown to follow the same condition.
 Here, we advocate that such a relation is actually a general rule.
@@
 
-For quantum field theory in a curved spacetime, we always assume that the quantum field is a subsystem that never entangles with the geometry, thus remains unitary.
+For quantum field theory in a curved spacetime, we always assume that the quantum field is a subsystem that never entangles with the geometry, and so remains unitary.
 Since we do not know quantum gravity/geometry, we cannot directly check this assumption by an actual calculation of entanglement.
-However, we can always check classical coherence, and by this rule we advocate, the answer directly proves/disproves subsystem unitarity.
+However, we can always check classical coherence and, by this rule we advocate, the answer directly proves/disproves subsystem unitarity.
 
@@
 At this moment, we do not have a general formalism to setup such self-consistency check that can be applied to any general geometry. 
-In Sec.\ref{sec-BlackHole}, we propose a specific way to apply such self-consistency check to the propagation of Hawking quanta.
-In addition to gaining insights into the information paradox, we hope to learn some lessons to inspire a more general formalism of such self-consistency check.
+In Sec.\ref{sec-BlackHole}, we propose a specific way to apply such a self-consistency check to the propagation of Hawking quanta.
+In addition to gaining insights into the information paradox, we hope to learn some lessons to inspire a more general formalism of such self-consistency checks.
 
@@
 Then a standard QFT calculation of scattering with this new field (graviton) should capture all interactions with the geometry, and a small scattering amplitude should guarantee that the interaction is suppressed.
-The concern for such method is that IR issues for these scattering calculations cannot be unambiguously regulated like in global Minkowski space.
+The concern for this method is that IR issues for these scattering calculations cannot be unambiguously regulated as in global Minkowski space.
 Since soft gravitons lead to real physical changes in the geometry that can be seen in memory effects \cite{Wei65,HeLys14}, an IR ambiguity signals our ignorance on how these geometric changes enter QFT.
@@
 
-The usual treatment of how a near-horizon mode becomes an asymptotic Hawking quantum is also following a fixed-background assumption.
+The usual treatment of how a near-horizon mode becomes an asymptotic Hawking quantum also uses a fixed-background assumption.
 The background is the Schwarzschild geometry.
@@
 \begin{itemize}
-\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field basically has its peaks and nodes following null geodesics.
+\item {\bf Classical coherence by tracking geodesics.} The classical mode of a massless field has its peaks and nodes following null geodesics.
 Thus, instead of actually solving the mode function, we can perform a much simpler calculation to track geodesics.
@@
 A classical uncertainty can be expressed as deviation from such metric, $\Delta g_{\mu\nu}$. 
-There are two major challenges here.
+There are two major challenges here:
 \begin{enumerate}
@@
 We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
-As explained in Sec.\ref{sec-BlackHole}, the consistency requires us to parametrize the uncertainty in the classical geometry.
+As explained in Sec.\ref{sec-BlackHole}, checking for consistency requires us to parametrize the uncertainty in the classical geometry.
 We have chosen a particular form of uncertainty in our explicit calculation.
@@
 
-In the hindsight, the physical meaning of our effect, Eq.~(\ref{eq-inv}), is quite clear.
-The geometric uncertainty, parametrized by $(\sigma\Delta l)$, leads to a fixed physical change locally where it is.
-When there is a large gravitational redshift, such effect is amplified.
+In hindsight, the physical meaning of our effect, Eq.~(\ref{eq-inv}), is quite clear.
+The geometric uncertainty, parametrized by $(\sigma\Delta l)$, leads to a fixed physical change locally.
+When there is a large gravitational redshift, the effect is amplified.
 In the large black hole limit, starting from a fixed physical distance from the horizon, the redshift gets arbitrarily large, so the effect gets amplified by an arbitrarily large factor.
@@
 While formulating the information paradox, it is customary to take the large black hole limit.
-Such limit allows us to identify near-horizon modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
+Such a limit allows us to identify near-horizon modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
 For these modes, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
@@
 Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.
-We think such competing nature is a good sign and will take us closer to the solution of information paradox.
+We think such competition is a good sign and will take us closer to the solution of information paradox.
 
@@
 \begin{equation}
-	ds^2 = - \left( 1 - \frac{2M'}{r} \right) d t'^2 + \left( 1 - \frac{2M'}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2~.	\label{2}
+	ds^2_{\rm region \ II} = - \left( 1 - \frac{2M'}{r} \right) d t'^2 + \left( 1 - \frac{2M'}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2~.	\label{2}
 \end{equation}
@@
 \begin{eqnarray}
-	\sigma  =  \frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
+	\sigma  =  \frac{-1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
 	 =  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}

### 2016-11-05 Draft_BH_shells.tex
Grammar check and updated fig 3

@@
 The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
-Instead of invoking conjectural quantum-gravity effects to modify such assumption, we propose a self-consistency check.
+Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
 We establish an analogy to Feynman's analysis of a double-slit experiment. 
-Feynman showed that a unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen the interference pattern is projected onto goes to infinitely far away.
+Feynman showed that unitary propagation of the interfering particles, namely ignoring the entanglement with the double-slit, becomes an arbitrarily reliable assumption when the screen upon which the interference pattern is projected is infinitely far away.
 We argue for an analogous self-consistency check for quantum field theory in curved spacetime.
@@
 However, it propagates out in a non-unitary process, gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
-For this abstract model to work in practice, this non-unitary propagation should be understood as interaction with a hidden system.
+For this abstract model to work in practice, this non-unitary propagation should be understood as an interaction with a hidden system.
 Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
@@
 Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
-The regions $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$.}
+The region $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$.
+The proper distance from the position where the photon is emitted to the position of the first shell is given by $l$ and the proper distance between the shells is given by $\Delta l$.
+}
 \label{fig-setup}
@@
 \item \textbf{Far from horizon ($M \ll l$)}: 
-If we send signals from the Earth surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
+If we send signals from the Earths' surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
 It starts to show a small deviation from the Minkowski result, but in the $M \ll r_1$ limit, it is almost indistinguishable.

### 2016-11-05 Draft_BH_shells.tex
minor changes

@@
 Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, and therefore carries the same qubit of information. 
-However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
+However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy \cite{Bou13}. 
 This conflict has inspired many different proposals to modify one of the above three statements. 
 For example, information loss or remnant \cite{Bek94} modifies Statement One; 
-firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
+firewall \cite{BraPir09,AMPS}, ER=EPR \cite{MalSus13}, pre-Hawking radiation \cite{KawMat13,Ho16}, or some version of the fuzzball \cite{Mat15} modifies Statement Two;
 various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it to compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}

### 2016-11-07 Draft_BH_shells.tex

@@
 \begin{itemize}
-\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer by a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
+\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer as a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
 \item {\bf General relativity:} The collapse-Schwarzschild geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
@@
 For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
+The back-reaction of such effect is no more than a Schwarzschild metric with a very slowly changing mass.
 \end{itemize}
@@
 Namely, we assume that the full system can be separated into a ``classical background'' and a ``quantum subsystem''. 
-After this artificial separation, since we only use quantum mechanics to describe the quantum subsystem, it always appears to be unitary.
+After this artificial separation, since the quantum subsystem is the only thing we describe by quantum mechanics, it always appears to be unitary.
 However, such unitarity should not be taken as a physical fact unless one specifically checks the nature of interactions with the background.
@@
 
-The fundamental principle behind Feynman's trick is that ``classical wave coherence'' should be taken as the prerequisite of ``quantum unitarity''. 
+The fundamental principle behind Feynman's trick is that ``classical wave coherence'', in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''.
 In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
-We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from perturbative calculations of gravitons.
+We provide a natural generalization to local QFT in curved spacetime, and we discuss why such self-consistency check is different from perturbative calculations of graviton-scattering.
 

### 2016-11-28 Draft_BH_shells.tex

@@
 \begin{abstract}
-The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from near-horizon modes to asymptotic Hawking quanta. 
+The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from a near-horizon mode to an asymptotic Hawking quantum. 
 Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
@@
 \item {\bf Quantum field theory in curved spacetime:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
-For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
+For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
 The back-reaction of such effect is no more than a Schwarzschild metric with a very slowly changing mass.
 \end{itemize}
-Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, and therefore carries the same qubit of information. 
-However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy \cite{Bou13}. 
+Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quantum by a unitary transformation, and therefore carries the same qubit of information. 
+However, Statement One and Two demand this unique qubit to be purified by two distinct objects, violating monogamy \cite{Bou13}. 
 This conflict has inspired many different proposals to modify one of the above three statements. 
@@
 In fact, we will argue that it is already problematic on its own. 
-In other words, {\bf the application of local QFT to unitary propagation of Hawking quanta is not self-consistent. }
+In other words, {\bf the application of local QFT to unitary propagation of individual Hawking quantum is not self-consistent. }
 
@@
 The recent paper by Osuga and Page \cite{OsuPag16} provides an abstract framework of how modifying Statement Three resolves the paradox.
-Basically, the near horizon mode is thermal as demanded by Statement Two.
-However, it propagates out in a non-unitary process, gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
-For this abstract model to work in practice, this non-unitary propagation should be understood as an interaction with a hidden system.
+Basically, the near horizon mode is purified by its interior partner as demanded by Statement Two.
+However, it propagates out in a non-unitary process, losing its original state and gaining the appropriate information to restore the unitary $S$-matrix demanded by Statement One. 
+For this abstract model to work in practice, this non-unitary propagation should be understood as an interaction with a hidden system, which actually exchanges the information within the out-going quantum with a qubit of information in the hidden system.
 Here hidden simply means something that a na\"ive application of local QFT is ignorant to.
@@
 In order for such non-unitary process to restore the asymptotic $S$-matrix, the hidden system must store the required information, which is comparable to the amount of microscopic information carried by the black hole.
-However, the black-hole-no-hair theorem states that two black holes with identical macroscopic parameters (mass, momentum, angular momentum, charge) are isometric to each other. 
+However, the black-hole-no-hair theorem states that two black-hole geometries with identical macroscopic parameters (mass, momentum, angular momentum, charge) are isometric to each other. 
 This limits the number of different classical geometries to be parametrized by macroscopic parameters only.
 As a result, the Hilbert space of superposed classical geometries has far fewer dimensions than what is necessary to carry the required amount of information.\footnote{We thank Raphael Bousso for private communication.}
-Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix; therefore such modification of Statement Three alone is insufficient to resolve the paradox.
+Thus, even if a propagating Hawking quantum does interact with this hidden system, it cannot reproduce a unitary $S$-matrix.
+Therefore such modification of Statement Three alone is insufficient to resolve the paradox.
 
@@
 Essentially, it was realized that two isometric (regions of) geometries should not always be considered as the same state.
-If one maps the geometries with congruences of geodesics, two isometric regions with different maps are actually different states.
-That is because changes in the mapping geodesics are measurable memory effects, and a consistent physical theory must be able to distinguish them.
+If one maps the geometries with congruences of geodesics, then two initially identical geometries with identical mappings may evolve into two late-time isometric geometries with different mappings. 
+Since changes in the mapping geodesics are measurable memory effects, a consistent physical theory must be able to distinguish them.
+Thus isometric regions with different maps should be described as different states.
 This realization may dramatically increase the number of different states encoded in classical geometries.
@@
 
-In this paper, we will take another step that is complementary to the above progress.
-It is exciting to know that modifying Statement Three can, in-principle, resolve the paradox, yet it remains a great mystery why local QFT should break down in low curvature regions.
+In this paper, we will take another step that is complementary to the above progress. It is exciting to know that modifying Statement Three can, in-principle, resolve the paradox.
+However, it remains a great mystery why local QFT should break down in low curvature regions. 
 If we just demand that it breaks down in order to resolve the information paradox, then there is no reason why this solution is preferred over modifying Statement One or Two. 
@@
 He showed that we can ignore the quantum details of the double-slit and summarize that as an uncertainty in its position, which is a classical quantity.
+\footnote{Here we mean that an uncertainty in position is a quantity that one can directly plug into the framework/equations of a classical theory, as oppose to states or operators which can only be understood by a quantum theory.}
 When such uncertainty is fixed, a classical calculation can show that the interference pattern is always visible as long as we put the final projection screen to be infinitely far away. 
@@
 
-The fundamental principle behind Feynman's trick is that ``classical wave coherence'', in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''.
+The fundamental principle behind Feynman's trick is that ``classical wave coherence'',
+\footnote{We remind the readers that ``coherence'' has a classical (likely original) meaning as superpositions of waves of stably similar phases.}
+ in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''. 
 In Sec.\ref{sec-QFT}, we argue that this principle enables a general self-consistency check of the classical background assumption. 
@@
 When they pass through slit 2 only, they reach the final screen as a probability distribution $P_2(y)$.
-When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$,
-instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
+When both slits are open, the probability distribution we find on the final screen is not a simple sum; $P_{12}(y) \neq P_1(y) + P_2(y)$.
+Instead, the final screen shows an interference pattern which can only be explained by wavefunctions.
 $P_i = \langle \phi_i | \phi_i \rangle$ and $P_{12} = (\langle \phi_1|+\langle \phi_2| ) (|\phi_1\rangle + | \phi_2 \rangle)=P_1 + P_2 + 2{\rm Re}\langle\phi_1|\phi_2\rangle$.
@@
 
-This standard explanation works because we assume the particle is the only quantum-mechanical system here, and it can be describe by a pure state, $|\phi\rangle_{\rm particle} = |\phi_1\rangle + |\phi_2\rangle$.
+This standard explanation assumes the particle is the only quantum-mechanical system here, and it can be describe by a pure state, $|\phi\rangle_{\rm particle} = |\phi_1\rangle + |\phi_2\rangle$.
 But if quantum mechanics is correct, this particle is not the only thing to be described by a wavefunction. 
@@
 \includegraphics[scale = 0.5]{bh_coherence.pdf}
-\caption{Schematic showing the rule we advocate; as classical coherence fails, we loose quantum unitarity.}
+\caption{Schematic showing the self-consistency check we advocate. 
+If there is a large enough uncertainty in the classical geometry, a classical mode function can have a significant uncertainty in its phases.
+If this happens, classical waves lose coherence, and the evolution of their quantum states lose unitarity.}
 \label{fig-QFT}
@@
 
-QFT theorists might think that a more direct self-consistency check is feasible.
+QFT theorists might think that the more direct self-consistency check is feasible.
 Instead of parametrizing a classical geometric uncertainty, one can treat deviations from the background geometry as a field and quantize it as any other fields.
@@
 \end{equation}
-When one applies local quantum field theory to describe a field on this fixed background, the result is by-definition unitary, but that is not necessary a physical fact. 
+When one applies local quantum field theory to describe a field on this fixed background, the results always appear to be unitary, but that is not necessary a physical fact. 
 Given how little we understand quantum gravity, a classical self-consistency check as we described in the previous section is a reasonable thing to do.

### 2016-11-28 Draft_BH_shells.tex
1 change

@@
 The fundamental principle behind Feynman's trick is that ``classical wave coherence'',
-\footnote{We remind the readers that ``coherence'' has a classical (likely original) meaning as superpositions of waves of stably similar phases.}
+\footnote{We remind the readers that ``coherence'' has a classical (likely original) meaning as superpositions of waves with stably similar phases.}
  in his case the observability of the interference pattern, should be taken as the prerequisite of ``quantum unitarity''. 

### 2016-11-30 Draft_BH_shells.tex
Updated appendix B

@@
 \begin{equation}
-	S^a_b = [K^a_b] - [K]h^a_b~.
+	8 \pi S^a_b = [K^a_b] - [K]h^a_b~.	\label{IJC}
 \end{equation}	
@@
 \begin{equation}
-	ds_{\rm induced, \ region \ I}^2 = - \left( 1 - \frac{2M}{r} \right)^{-1} dt^2 + r^2 d \Omega_2^2.	\label{13}
+	ds_{\rm induced, \ region \ I}^2 = h_{ab} dy^a dy^b \equiv - \left( 1 - \frac{2M}{r} \right) dt^2 + r^2 d \Omega_2^2.	\label{13}
 \end{equation}
-The extrinsic curvature from this side will simply be the $r$ derivative.
+
 Analogously we have the same induced metric written in the coordinate of region $II$,
 \begin{equation}
-	ds_{\rm induced, \ region \ II}^2 = - \left( 1 - \frac{2M'}{r} \right)^{-1} dt'^2 + r^2 d \Omega_2^2.	\label{14}
+	ds_{\rm induced, \ region \ II}^2 = h'_{ab} dy'^a dy'^b \equiv - \left( 1 - \frac{2M'}{r} \right) dt'^2 + r^2 d \Omega_2^2.	\label{14}
 \end{equation}
-Similarly taking the $r$ derivative here leads to the extrinsic curvature from this side.
-Combine with the continuity condition that relates $t$ to $t'$, 
+
+Matching the induced metrics at a fixed radius $r_1$ imposes the following condition.
+
 \begin{equation}
-	dt'^2 = \left( \frac{1 - \frac{2M'}{r_1}}{ 1- \frac{2M}{r_1}} \right) dt^2~,
+	dt'^2 = \left( \frac{1 - \frac{2M}{r_1}}{ 1- \frac{2M'}{r_1}} \right) dt^2~,
 \end{equation}
-we can calculate the extrinsic curvature components.
+
+We can explicitly calculate the extrinsic curvature components.
+
+\begin{equation}
+	K_{ab} = \frac{1}{2} (\mathcal{L}_n g_{\alpha \beta}) e^\alpha_a e^\beta_b, \hspace{5mm} e^\alpha_a \equiv \frac{\partial x^\alpha}{\partial y^a},
+\end{equation}
+where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{-\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{-\frac{1}{2}}, 0 , 0)$.
+Lets look at the Lie derivative first
+
 \begin{eqnarray}
-	(K^t_t)^{I} & = & \frac{M}{r_1^2} \left( 1 - \frac{2M}{r_1} \right)^{-\frac{1}{2}} ~.	\nonumber	\\
-	(K^\theta_\theta)^{I} & = & \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} 
-	= (K^\phi_\phi)^{I}~.	\label{16}
+	L_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
+	& = & n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}	
 \end{eqnarray}
-It is obvious that for region II, we simply replace $M$ by $M'$.
 
-The time component $S^0_0$ is the surface energy density.
+Now the components of the extrinsic curvature are
+
 \begin{equation}
-	\sigma = S^0_0 = \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2(M+\Delta M)}{r_1} \right)^\frac{1}{2} \right).
+	K_{ab} = \frac{1}{2} (n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}) e^\alpha_a e^\beta_b	\label{Ecuv}
 \end{equation}
+
+Notice that the since the only variable in the above equation is $r$ only the $\partial_r$ terms will contribute.
+Since the $a,b$ indices do not run over $r$ only the first term in the expression above will remain.
+Using this we can calculate the components of the extrinsic curvature.
+
+\begin{eqnarray}
+	K_{tt} & = & \frac{1}{2} (n^r \partial_r g_{tt}) 	\nonumber	\\
+	& = & \frac{1}{2} \left( 1 - \frac{2M}{r} \right)^\frac{1}{2}  \left( \frac{2M}{r^2} \right)
+\end{eqnarray}
+and we know $(K^t_t)^{I} = g^{tt}K_{tt} = \frac{M}{r^2} \left( 1 - \frac{2M}{r} \right)^{-\frac{1}{2}}$, the $I$ index represents a quantity evaluated in the metric $I$ and similarly for $II$.
+The other components are
+
+\begin{equation}
+	(K^\theta_\theta)^{I} = \frac{1}{r_1} \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} = (K^\phi_\phi)^{I}.
+\end{equation}
+For the extrinsic curvatures in region II, we simply replace $M$ by $M'$.
+\\
+\\
+The time component $S^t_t$ is the surface energy density can be calculated using Eq (\ref{IJC}).
+
+\begin{eqnarray}
+	\sigma = S^t_t & = & \frac{1}{8 \pi} ((K^\theta_\theta)^{I} + (K^\phi_{\phi})^{I} - (K^\phi_\phi)^{II} - (K^\theta_\theta)^{II})	\nonumber	\\
+	& = & \frac{1}{4 \pi r_1} \left( \left( 1 - \frac{2M}{r_1} \right)^\frac{1}{2} - \left( 1 - \frac{2M'}{r_1} \right)^\frac{1}{2} \right).
+\end{eqnarray}
+
 When $2\Delta M \ll (r_1-2M)$, this is approximately given by 
 \begin{eqnarray}
-	\sigma  =  \frac{-1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
+	\sigma  =  -\frac{1}{4 \pi r_1} \left[ \partial_X \left( 1 - \frac{2X}{r_1} \right)^\frac{1}{2} \right]_{X = M} \Delta M
 	 =  \frac{\Delta M}{4 \pi r_1^2} g_{tt}^{-\frac{1}{2}}	\label{sig-Dm}
@@
 These equations allow us to replacing $\Delta M$ by $\sigma$ and $\Delta r$ by $\Delta l$ in Eq.~(\ref{eq-result}) to get Eq.~(\ref{eq-inv}).
-
 Finally, Eq.~(\ref{Dl-Dr}) can be integrated to give the proper distance $l$ between the inner shell and the horizon.

### 2016-12-01 Draft_BH_shells.tex
caption and footnote

@@
 The bottom part is a general case of two Hawking photons coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
-The top part shows two Hawking photons coming from the same distance $r_e$ from a black hole of mass $M$.
+The top part shows two Hawking photons coming from the same place very close to the horizon, $r_e\approx2M$, from a black hole of mass $M$.
 Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
-The region $I$ represent a metric with mass $M$ and region $II$ represents a metric with mass $M+\Delta M$.
-The proper distance from the position where the photon is emitted to the position of the first shell is given by $l$ and the proper distance between the shells is given by $\Delta l$.
+The two regions marked by $I$ is described a metric with mass $M$.
+The region $II$ between the two shells is described by a metric with mass $M+\Delta M$.
+The proper distance from the shells to the horizon is $l$, and the proper distance between the shells is given by $\Delta l$.
 }
@@
 Also, the combination $(\sigma\Delta l)$ is invariant under radial boosts, thus Eq.~(\ref{eq-inv}) does not care about whether the shells are actually at rest, nor in which frame we calculate it.
+\footnote{When the shells are moving, we will reach the same gauge-invariant answer by the following process.
+First we picking an (arbitrary) frame.
+$\Delta l$ is the proper distance between the two shells at the time of the first crossing in this frame.
+$\sigma$ is the energy density measured in this frame.
+The combination $(\sigma\Delta l)$ is again invariant.
+Interesting, if the two shells are not moving in the same velocity, the result will depend on their relative velocity, and we cannot appreciate the physical meaning yet.
+A more general framework to quantify the geometric uncertainty is a goal in future works.
+}
 
@@
 
-We thank XXX for discussions. We are supported by XXX.
+We thank Raphael Bousso, Pei-Ming Ho and Robert Jefferson for discussions. 
+This work is supported by the Canadian Government through the Canadian Institute for Advance Research and Industry Canada, 
+and by Province of Ontario through the Ministry of Research and Innovation. 
+The Dunlap Institute is funded through an endowment established by the David Dunlap family and the University of Toronto.
 

### 2016-12-05 Draft_BH_shells.tex
improving captions

@@
 \begin{abstract}
-The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagations from a near-horizon mode to an asymptotic Hawking quantum. 
+The black hole information paradox presumes that quantum field theory in curved spacetime can provide unitary propagation from a near-horizon mode to an asymptotic Hawking quantum. 
 Instead of invoking conjectural quantum-gravity effects to modify such an assumption, we propose a self-consistency check.
@@
 The reason why local geometry carries the appropriate information to give in the first place may be related to the soft-hair proposal \cite{HawPer16}. 
+Exactly how such exchange of information happens is a topic for future works.
 
@@
 Screen one shows the signal that one would see in each scenario (i.e classical particles or waves) if only one slit was open. 
-If slit 1 was open we would see $P_1$ and so on.
-Screen 2 shows the signal we see if both the silts are open in each scenario.}
+If slit 1 was open we would see $P_1$ and so on. Screen 2 shows the signal we see if both the silts are open in each scenario.}
 \label{fig-doubleslit}
@@
 The uncertainty principle sets a limit on how well we can measure this difference. 
-Namely, we need a large uncertainty in the position to measure a small change in momentum.
+Namely, we need a large uncertainty in position to measure a small change in momentum. 
 Setting $\hbar$ to 1, we can say that when the momentum difference is too small to be measured,

### 2016-12-05 Draft_BH_shells.tex
discssion
improving the discussion about uncertainty principle

@@
 While formulating the information paradox, it is customary to take the large black hole limit.
-Such a limit allows us to identify near-horizon modes with wavelength much shorter than the curvature scale, but much longer than the UV cut-off scale.
-For these modes, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
-This large black hole limit, which is effectively a near-Minkowski limit of a near horizon region, is the key argument to eliminate many na\"ive solutions to the information paradox.
+Technically, it means that we first select a fixed length scale $l$ that is much longer than the UV-cutoff scale of the theory, and study a near-horizon region of this size.
+Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effect is suppressed by $(l/M)$.
+If we make the black hole arbitrarily large, $(l/M)$ goes to zero, the for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
+This large black hole limit is the key argument to eliminate many na\"ive solutions to the information paradox.
 
 The main result in this paper shows that there is a competing effect which stops us from taking this convenient limit.
-The geometric uncertainty at distance $l$ from the horizon will only affect near-horizon modes of wavelength shorter than $l$.
-If we fix the wavelength of the relevant near-horizon modes and increase the black hole size, our result shows that the unitary propagation to asymptotic Hawking radiation becomes less and less trustworthy.
+In order for field theory modes from the above region to propagate out and become asymptotic quanta, they must go through geometric uncertainties, like the double-shells in our example, at the distance scale $l$ from the horizon.
+If we again fix $l$ and increase $M$, our result in Eq.~(\ref{fin-result}) shows that the unitary propagation to asymptotic Hawking quanta becomes less and less trustworthy. 
 Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.

### 2016-12-08 Draft_BH_shells.tex
footnote
in discussion, regarding the the value of geometric uncertainty and
sourcing it from Hawking radiation itself.

@@
 We have chosen a particular form of uncertainty in our explicit calculation.
-Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty to make our approach even more general.
+Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty.
 
@@
 We think such competition is a good sign and will take us closer to the solution of information paradox.
+
+Note that our argument will fail if the combination $(\sigma\Delta l)$ is exactly zero instead of a fixed finite number.
+Namely, if there is absolutely no geometric uncertainty, then the geometry is indeed a completely classical system that does not entangle with the quantum field.
+We would like to argue that in the context of QFT in curved spacetime, enforcing $\Delta g_{\mu\nu}=0$ is quite unreasonable.
+After all, we are feeding the expectation value of the stress-tensor-operator, $\langle T_{\mu\nu}\rangle$, to the Einstein equation. 
+As long as we are not in an energy eigenstate of the quantum field, $\langle\Delta T_{\mu\nu}\rangle$ will be nonzero, and there is no reason why this does not lead to an uncertainty in the geometry.
+One can even use the uncertainty in the energy flux of Hawking radiation itself to argue that there has to be an uncertainty in geometry.
+\footnote{Although, if one simply blue shifts the actual out-going Hawking radiation back to the hear-horizon zone, one gets a contribution of $(\sigma\Delta l)$ that depends on $M$.
+That is because the QFT modes escaping the angular-momentum barrier are mostly in $S$-waves.
+This $S$-wave energy flux gets diluted by area, resulting $(\sigma\Delta l)\propto M^{-2}$.
+If this is the only contribution to $(\sigma\Delta l)$, such dependence exactly stops Eq.~(\ref{fin-result}) from diverging in the large black hole limit, which undermines our main argument in this paper.
+Nevertheless, it violates equivalence principle for the local property $(\sigma\Delta l)$ to depend on the size of the black hole.
+It will be interesting to explicitly compute $\langle\Delta T_{\mu\nu}\rangle$ for the actual states of near-horizon QFT modes to see whether they uphold equivalence principle.
+Note that higher angular modes are all excited near the horizon.
+They are trapped by the angular momentum barrier thus do not contribute to the asymptotic flux, but they should still contribute to local quantities.
+That is why the $S$-wave contribution might be a dramatic underestimation, and the actual $(\sigma\Delta l)$ can still respect equivalence principle.
+If that is true, our arguments will hold.
+We will leave that particularly involved QFT calculation to future works.
+ }
 

### 2016-12-08 Draft_BH_shells.tex
typo

@@
 After all, we are feeding the expectation value of the stress-tensor-operator, $\langle T_{\mu\nu}\rangle$, to the Einstein equation. 
-As long as we are not in an energy eigenstate of the quantum field, $\langle\Delta T_{\mu\nu}\rangle$ will be nonzero, and there is no reason why this does not lead to an uncertainty in the geometry.
+As long as we are not in an eigenstate of the local stress density, $\langle\Delta T_{\mu\nu}\rangle$ will be nonzero, and there is no reason why this does not lead to an uncertainty in the geometry.
 One can even use the uncertainty in the energy flux of Hawking radiation itself to argue that there has to be an uncertainty in geometry.

### 2016-12-10 Draft_BH_shells.tex
typo

@@
 \end{equation}
-where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{-\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{-\frac{1}{2}}, 0 , 0)$.
+where $a,b \in \{t,\theta, \phi \}$ and $\mathcal{L}_n$ is the Lie derivative w.r.t to the normal vector $n_\alpha = g_{rr}^{\frac{1}{2}} \partial_\alpha r = (0, g_{rr}^{\frac{1}{2}}, 0 , 0)$.
 Lets look at the Lie derivative first
@@
 \begin{eqnarray}
-	L_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
+	\mathcal{L}_n g_{\alpha \beta} & = & n^\mu \partial_\mu g_{\alpha \beta} + \partial_\alpha n^\mu g_{\mu \beta} + \partial_\beta n^\mu g_{\alpha \mu}	\nonumber	\\
 	& = & n^r \partial_r g_{\alpha \beta} + \partial_\alpha n^r g_{r \beta} + \partial_\beta n^r g_{\alpha r}	

### 2016-12-18 Draft_BH_shells.tex

@@
 Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effect is suppressed by $(l/M)$.
-If we make the black hole arbitrarily large, $(l/M)$ goes to zero, the for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
+If we make the black hole arbitrarily large, $(l/M)$ goes to zero, then for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
 This large black hole limit is the key argument to eliminate many na\"ive solutions to the information paradox.
@@
 The main result in this paper shows that there is a competing effect which stops us from taking this convenient limit.
-In order for field theory modes from the above region to propagate out and become asymptotic quanta, they must go through geometric uncertainties, like the double-shells in our example, at the distance scale $l$ from the horizon.
+In order for field theory modes from the above region to propagate out and become asymptotic quanta, they must go through geometric uncertainties.
+These geometric uncertainties are like the double-shells in our example, and we only care about those that an out-going quantum has to pass through---those at distance scales larger than $l$ from the horizon.
 If we again fix $l$ and increase $M$, our result in Eq.~(\ref{fin-result}) shows that the unitary propagation to asymptotic Hawking quanta becomes less and less trustworthy.
-Since the dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling both effects, there seems to be no middle-ground that can make both unitarity and local-Minkowski-ness arbitrarily reliable.
+
+The dimensionless ratio $(l/M)$ is the only relevant physical parameter that comes into the scaling of both of the above effects.
+The suppressing of curvature effects prefers this ratio to be large, but the validity of unitary propagation prefers this to be small.
+Therefore, we cannot make both unitarity and local-Minkowski-ness arbitrarily reliable.
 We think such competition is a good sign and will take us closer to the solution of information paradox.
 
-Note that our argument will fail if the combination $(\sigma\Delta l)$ is exactly zero instead of a fixed finite number.
-Namely, if there is absolutely no geometric uncertainty, then the geometry is indeed a completely classical system that does not entangle with the quantum field.
+Our argument will fail if the geometric uncertainty is exactly zero instead of a fixed finite number.
+With an exactly zero uncertainty, the geometry is indeed a completely classical system that does not entangle with the quantum field
+\footnote{Alternatively, if $(\sigma\Delta l)$ is really small, there might be an intermediate value of $(l/M)$ that makes both the curvature effects small and a unitarity propagation sufficiently trustworthy.
+A more involved discussion is required for such possibility and we postpone that to future work.}.
 We would like to argue that in the context of QFT in curved spacetime, enforcing $\Delta g_{\mu\nu}=0$ is quite unreasonable.
@@
 One can even use the uncertainty in the energy flux of Hawking radiation itself to argue that there has to be an uncertainty in geometry.
-\footnote{Although, if one simply blue shifts the actual out-going Hawking radiation back to the hear-horizon zone, one gets a contribution of $(\sigma\Delta l)$ that depends on $M$.
-That is because the QFT modes escaping the angular-momentum barrier are mostly in $S$-waves.
-This $S$-wave energy flux gets diluted by area, resulting $(\sigma\Delta l)\propto M^{-2}$.
-If this is the only contribution to $(\sigma\Delta l)$, such dependence exactly stops Eq.~(\ref{fin-result}) from diverging in the large black hole limit, which undermines our main argument in this paper.
-Nevertheless, it violates equivalence principle for the local property $(\sigma\Delta l)$ to depend on the size of the black hole.
-It will be interesting to explicitly compute $\langle\Delta T_{\mu\nu}\rangle$ for the actual states of near-horizon QFT modes to see whether they uphold equivalence principle.
-Note that higher angular modes are all excited near the horizon.
-They are trapped by the angular momentum barrier thus do not contribute to the asymptotic flux, but they should still contribute to local quantities.
-That is why the $S$-wave contribution might be a dramatic underestimation, and the actual $(\sigma\Delta l)$ can still respect equivalence principle.
-If that is true, our arguments will hold.
-We will leave that particularly involved QFT calculation to future works.
- }
+
+If one simply blue-shifts the actual out-going Hawking radiation energy flux back to the hear-horizon zone, one gets a contribution of $(\sigma\Delta l)\propto M^{-2}$.
+This would have nullified our argument since Eq.~(\ref{fin-result}) will no longer depend on $M$
+\footnote{One can still take the face value of Eq.~(\ref{fin-result}) and claim that a propagation from the Planckian, near-horizon region loses unitarity.
+This means solving the information problem with something similar to a firewall \cite{AMPS}:  a near-horizon observer can see violation of equivalence principle in scales arbitrarily smaller than the Schwarzschild radius.}.
+However, such an $M$-dependent value of geometric uncertainty explicitly violates the equivalence principle.
+Using such value in our analysis would be a technical mistake.
+The value of energy flux that can escape the angular momentum barrier are mostly in $S$-waves and it depends explicitly on $M$.
+However, the geometric uncertainty near the horizon are also affected by all those modes trapped inside the angular momentum barrier.
+Inferring a near-horizon geometric uncertainty solely from the asymptotic flux is a dramatic underestimation.
+In fact, instead of using the Rindler basis which is natural for out-going modes to calculate the energy flux, one can use the locally Minkowski mode basis to calculate the local stress tensor.
+It should then be obvious that $\langle\Delta T_{\mu\nu}\rangle$ upholds equivalence principle, which demands an $M$-independent geometric uncertainty
+\footnote{Although, we are not advocating that such calculation directly gives us the value of $(\sigma\Delta l)$.
+That is because using the expectation value of $T_{\mu\nu}$ in the Einstein equation is itself an assumption.
+The actual value one can use is related to the decoherence problem which we would like to circumvent for now.
+Our argument is valid as long as the geometric uncertainty is nonzero and obeys equivalence principle.}.
 

### 2017-01-16 Draft_BH_shells.tex

--- 2016-12-10 Draft_BH_shells.tex
@@
 We think such competition is a good sign and will take us closer to the solution of information paradox.
-
-Note that our argument will fail if the combination $(\sigma\Delta l)$ is exactly zero instead of a fixed finite number.
-Namely, if there is absolutely no geometric uncertainty, then the geometry is indeed a completely classical system that does not entangle with the quantum field.
-We would like to argue that in the context of QFT in curved spacetime, enforcing $\Delta g_{\mu\nu}=0$ is quite unreasonable.
-After all, we are feeding the expectation value of the stress-tensor-operator, $\langle T_{\mu\nu}\rangle$, to the Einstein equation. 
-As long as we are not in an eigenstate of the local stress density, $\langle\Delta T_{\mu\nu}\rangle$ will be nonzero, and there is no reason why this does not lead to an uncertainty in the geometry.
-One can even use the uncertainty in the energy flux of Hawking radiation itself to argue that there has to be an uncertainty in geometry.
-\footnote{Although, if one simply blue shifts the actual out-going Hawking radiation back to the hear-horizon zone, one gets a contribution of $(\sigma\Delta l)$ that depends on $M$.
-That is because the QFT modes escaping the angular-momentum barrier are mostly in $S$-waves.
-This $S$-wave energy flux gets diluted by area, resulting $(\sigma\Delta l)\propto M^{-2}$.
-If this is the only contribution to $(\sigma\Delta l)$, such dependence exactly stops Eq.~(\ref{fin-result}) from diverging in the large black hole limit, which undermines our main argument in this paper.
-Nevertheless, it violates equivalence principle for the local property $(\sigma\Delta l)$ to depend on the size of the black hole.
-It will be interesting to explicitly compute $\langle\Delta T_{\mu\nu}\rangle$ for the actual states of near-horizon QFT modes to see whether they uphold equivalence principle.
-Note that higher angular modes are all excited near the horizon.
-They are trapped by the angular momentum barrier thus do not contribute to the asymptotic flux, but they should still contribute to local quantities.
-That is why the $S$-wave contribution might be a dramatic underestimation, and the actual $(\sigma\Delta l)$ can still respect equivalence principle.
-If that is true, our arguments will hold.
-We will leave that particularly involved QFT calculation to future works.
- }
 

### 2017-01-16 Draft_BH_shells.tex

@@
 Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effect is suppressed by $(l/M)$.
-If we make the black hole arbitrarily large, $(l/M)$ goes to zero, then for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
+If we make the black hole arbitrarily large, $(l/M)$ goes to zero, the for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
 This large black hole limit is the key argument to eliminate many na\"ive solutions to the information paradox.

### 2017-01-17 Draft_BH_shells.tex
Typos corrected - arXiv version

--- 2017-01-16 Draft_BH_shells.tex
@@
 For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quantum.
-The back-reaction of such effect is no more than a Schwarzschild metric with a very slowly changing mass.
+The back-reaction of such an effect is no more than a Schwarzschild metric with a very slowly changing mass.
 \end{itemize}
@@
 
-Whether the double-slit states are given by Eq.~(\ref{eq-pure}) or (\ref{eq-mixed}) seems to require the knowledge about the actual quantum-mechanical interacton between the particles and the double-slit, which is unavailable in practice.
-Feynman pushed the above analysis further to overcome such problem.
+Whether the double-slit states are given by Eq.~(\ref{eq-pure}) or (\ref{eq-mixed}) seems to require the knowledge about the actual quantum-mechanical interaction between the particles and the double-slit, which is unavailable in practice.
+Feynman pushed the above analysis further to overcome such a problem.
 He pointed out that even if we try to keep the interaction minimal, there will be one inevitable interaction that makes $|\psi_1\rangle$ and $|\psi_2\rangle$ different.
@@
 We can treat both the position uncertainty $\Delta y^{\rm ds}$ and the interference fringe width $w$ as classical quantities.
-Eq.~(\ref{eq-stdcls}) is then a purely classical calculation to compare these two quantities, which tells us whether a classical wave pattern (the intereference pattern) loses coherence.
+Eq.~(\ref{eq-stdcls}) is then a purely classical calculation to compare these two quantities, which tells us whether a classical wave pattern (the interference pattern) loses coherence.
 If we only take its face value, it seems to be only a practical obstacle of measuring the interference pattern. 
@@
 We start with two out-going null geodesics with the separation of one period of such mode near the horizon, and then we calculate the change in their separations at spatial infinity.
-As this change increases, one should gradually lose faith in the unitary propagation of such mode, since it becomes increasingly difficult to experimentally verify.
+As this change increases, one should gradually lose faith in the unitary propagation of such a mode, since it becomes increasingly difficult to experimentally verify.
 \item {\bf The background and the uncertainty.} The classical background in this case is the Schwarzschild geometry, which can be written as the metric $g_{\mu\nu}$ in Eq.~(\ref{eq-metric}). 
@@
 Near the horizon, at $r_e$ with $(r_e-2M)\ll 2M$, the same two null rays will have the same coordinate time separation, but a much smaller proper time separation.
-This represent a near-horizon mode.
+This represents a near-horizon mode.
 
@@
 The trajectory of the observer and the position from which the photons are emitted are represented by solid blue lines.
-The bottom part is a general case of two Hawking photons coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
+The bottom part is a general case of two Hawking quanta coming from a distance $r_e$ from the black hole of mass $M$ and arriving at an observer who is at a distance of $r_0$.
 The top part shows two Hawking photons coming from the same place very close to the horizon, $r_e\approx2M$, from a black hole of mass $M$.
 Instead of the photons freely propagating through to an observer at $r_0$, they have to cross two shells, represented by blue dotted line, of equal and opposite mass $\Delta M, -\Delta M$ at $r_{1}, r_{2}$ respectively.
-The two regions marked by $I$ is described a metric with mass $M$.
+The two regions marked by $I$ are described a metric with mass $M$.
 The region $II$ between the two shells is described by a metric with mass $M+\Delta M$.
@@
 \footnote{When the shells are moving, we will reach the same gauge-invariant answer by the following process.
-First we picking an (arbitrary) frame.
+First we pick an (arbitrary) frame.
 $\Delta l$ is the proper distance between the two shells at the time of the first crossing in this frame.
@@
 Geometric uncertainty creates a fixed-size uncertainty in the local proper time where it occurs.
-If it happens in the region which the wavelength of a mode is blue-shifted, then it gets magnified to be relatively larger.
+If it happens in a region where the wavelength of a mode is blue-shifted, then it gets magnified to be relatively larger.
 To be more precise, we evaluate Eq.~(\ref{eq-inv}) in three regimes; 
@@
 One can imagine a simple subtraction by a counter term.
-Or alternatively, since the actual value of $(\sigma\Delta r)$ is unknown, we assume that it is small enough to not cause any concern.
+Or alternatively, since the actual value of $(\sigma \Delta l)$ is unknown, we assume that it is small enough to not cause any concern.
 
 \item \textbf{Far from horizon ($M \ll l$)}: 
-If we send signals from the Earths' surface to somewhere far in the space, this result tell us how much can we trust a unitary QFT description.
-It starts to show a small deviation from the Minkowski result, but in the $M \ll r_1$ limit, it is almost indistinguishable.
+If we send signals from the Earths' surface to somewhere far in the space, this result tells us how much we can trust a unitary QFT description.
+It starts to show a small deviation from the Minkowski result, but in the $M \ll l$ limit, it is almost indistinguishable.
 
@@
 In this paper, we proposed a self-consistency check of QFT in curved spacetime geometries.
-We have shown that propagation from the near-horizon region of a large black hole seems to fail such check.
+We have shown that propagation from the near-horizon region of a large black hole seems to fail such a check.
 As explained in Sec.\ref{sec-BlackHole}, checking for consistency requires us to parametrize the uncertainty in the classical geometry.
 We have chosen a particular form of uncertainty in our explicit calculation.
-Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such uncertainty.
+Our result is gauge invariant and makes physical sense, but there might be a more general way to parametrize such an uncertainty.
 
@@
 Technically, it means that we first select a fixed length scale $l$ that is much longer than the UV-cutoff scale of the theory, and study a near-horizon region of this size.
-Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effect is suppressed by $(l/M)$.
+Such a region will be almost identical to a region of the same size in global Minkowski space, since all locally measurable curvature effects are suppressed by $(l/M)$.
 If we make the black hole arbitrarily large, $(l/M)$ goes to zero, then for all the field theory modes within this region, we are confident that they start in local vacuum states of QFT as if they live in Minkowski space.
@@
 In order for local geometry to give this information to the Hawking quanta, it must first carry such information.
-If was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
+It was first suggested that superpositions of different classical geometries can store such information \cite{NomVar12}.
 In the conventional picture, classical geometries are determined by only a few parameters such as the location and size of the black hole.
 Thus the major objection to such picture is that the superpositions of classical geometries do not form a large enough Hilbert space to hold the required information.
-Recently, it was realized that there are actually a much larger number of classical geometries differed by their soft hairs \cite{HawPer16}.
+Recently, it was realized that there are actually a much larger number of classical geometries that differ by their soft hairs \cite{HawPer16}.
 A simple counting suggested that the size of Hilbert space seems no longer the problem, so one should pursue this line of thoughts even further.
 
-Classically, soft hairs manifest as memory effects that alter the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
+Classically, soft hairs manifest themselves as memory effects that alter the distances between geodesics, which is very similar to the effect of geometric uncertainty as we showed in this paper.
 Two neighbouring null rays simply ``remember'' the geometric uncertainty they passed through.
@@
 \end{equation}
-Clearly, they have the same coordinate time separation $\Delta t = T$ everywhere, and we illustrate in the lower part of Figure \ref{fig-setup}.
+Clearly, they have the same coordinate time separation $\Delta t = T$ everywhere, as we illustrate in the lower part of Figure \ref{fig-setup}.
 
@@
 \\
-The time component $S^t_t$ is the surface energy density can be calculated using Eq (\ref{IJC}).
+The time component $S^t_t$ is the surface energy density and can be calculated using Eq (\ref{IJC}).
 

### 2017-03-01 Draft_BH_shells.tex

@@
 In our case, we will see that even in Minkowski space, geometric uncertainty already leads to a finite change between the two null geodesics.
-We will simply ``renormalize'' that away by saying that if the black hole case leads to a similar change, it should not be taken as a serious problem.
+We will assume that this is small and it should not be taken as a serious problem.
 Our surprising result is that in the black hole case, we get an infinitely larger change, which is difficult to blame on the usual divergence of QFT.
@@
 1) The Minkowski limit: $M=0$; 
-2) Small black holes / far from horizon: $M \ll r_1$; 
-3) Large black holes / near horizon: $r_1\gg M$. 
+2) Small black holes / far from horizon: $M \ll l$; 
+3) Large black holes / near horizon: $M\gg l $. 
 Instead of using the coordinate $r_1$, we will express the answer with the physical distance $l$ between the horizon and the shells. 
@@
 The na\"ive interpretation of the $M=0$ result is that even in Minkowski space, geometric uncertainty can potentially decohere classical mode functions.
-By our definition, that poses some threat to QFT in Minkowski space.
-We are going to assume that unitarity in QFT is fine in Minkowski space, effectively ``renormalize away'' the effect at $M=0$.
-One can imagine a simple subtraction by a counter term.
-Or alternatively, since the actual value of $(\sigma \Delta l)$ is unknown, we assume that it is small enough to not cause any concern.
+However, since the actual value of $(\sigma \Delta l)$ is unknown, we assume that it is small enough to not cause any concern.
 

### 2017-03-01 Draft_BH_shells.tex

@@
 
+In other words, we have proven the following statement:
+{\it If we do not see an interference pattern because the quantum uncertainty of the double-slit position is too large and it makes the pattern blurry, then the evolution for the particle alone is not unitarity, because it becomes entangled with the double-slit.}
+
 One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit.
+Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether $\Delta y^{\rm ds}$ is the true reason that erases the interference pattern.
 This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
-Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit. 
-Namely, its value should be fixed if we move the screen further away. Eq.~(\ref{eq-stdcls}) shows that with a fixed $\Delta y^{\rm ds}$, we can always make $L$ large enough to satisfy this condition. 
-Thus, at least at the level of gedanken experiment, one can always arrange a situation that the interference pattern is visible and subsystem unitarity is valid.
+Indeed we do not know the value of $\Delta y^{\rm ds}$ just from classical physics, but it is very reasonable to assume that it is intrinsic to the double-slit and has a finite value.
+Namely, its value should be fixed if we move the screen.
+Therefore, there will be a distance too close, such that Eq.~(\ref{eq-stdcls}) is not satisfied, and unitarity of the particle is lost.
+There will also be a distance far enough, such that Eq.~(\ref{eq-stdcls}) is satisfied, and the subsystem unitarity for the particle is valid.
+At the level of gedanken experiment, we would always want to make sure that the second case is true.
 
@@
 
-We thank Raphael Bousso, Pei-Ming Ho and Robert Jefferson for discussions. 
+We thank Raphael Bousso, Steffen Gielen, Pei-Ming Ho and Robert Jefferson for discussions. 
 This work is supported by the Canadian Government through the Canadian Institute for Advance Research and Industry Canada, 

### 2017-03-03 Draft_BH_shells.tex
for PRD

@@
 Namely, we need a large uncertainty in position to measure a small change in momentum.
-Setting $\hbar$ to 1, we can say that when the momentum difference is too small to be measured,
+If the double-slit is well-localized in the position space, with an uncertainty $\Delta y^{\rm ds}$ that only comes from quantum mechanics, then it saturates the uncertainty principle and provide a momentum resolution of $(1/\Delta y^{\rm ds})$.
+Thus, when when the momentum difference is too small to be measured,
 \begin{equation}

### 2017-03-06 Draft_BH_shells.tex

@@
 In other words, we have proven the following statement:
-{\it If we do not see an interference pattern because the quantum uncertainty of the double-slit position is too large and it makes the pattern blurry, then the evolution for the particle alone is not unitarity, because it becomes entangled with the double-slit.}
+The quantum uncertainty of the double-slit position is too large and makes the interference pattern blurry {\bf if and only if} the evolution for the particle alone is not unitarity due to entanglement with the double-slit.
 
 One might object that the Eq.~(\ref{eq-stdcls}) is not entirely classical, since the value of $\Delta y^{\rm ds}$ has to originate from the unknown quantum mechanics of the double-slit.
-Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether $\Delta y^{\rm ds}$ is the true reason that erases the interference pattern.
+Thus, within a classical theory, even if we do not see an interference pattern, we can never know whether the quantum uncertainty, $\Delta y^{\rm ds}$, is the true reason that erases the interference pattern.
 This is a valid concern, and it actually shows another strength of Eq.~(\ref{eq-stdcls}). 
@@
 Thus when classical coherence fails, not only have we no practical measurements to confirm the purity of the subsystem wavefunction, such wavefunctions {\it actually did not evolve unitarily.}
-Whatever effect responsible for a classical uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem quantum-mechanically and became entangled with it.
+Whatever effect responsible for a quantum uncertainty large enough to disrupt classical coherence must have also interacted with the subsystem and became entangled with it.
 
